---
title: "VR - Supplementary Analyses - Reaching"
author: "Joshua Bell"
format:
  html:
    toc: true
    toc-depth: 3
    toc-float: true
    toc-placement: left
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      cache = TRUE, 
                      fig.width = 12, 
                      fig.height = 8)
pkgs <- c("dplyr", "readr", "magrittr", "data.table", "patchwork", "here", "brms", "cmdstanr", "datawizard", "bayestestR", "flextable", "ggplot2", "tidybayes")
for(i in pkgs){
  if(!i %in% rownames(installed.packages())){ 
    install.packages(i) 
    library(i, character.only = TRUE)
  }
  else(library(i, character.only = TRUE))
}

options("mc.cores" = parallel::detectCores(), "brms.backend" = "cmdstan")
control_list = list(adapt_delta = .998, max_treedepth = 18)

b = 4000/parallel::detectCores()
i = 48000/parallel::detectCores()
ch = parallel::detectCores()
co = parallel::detectCores()
```

```{r import-standardize, include=FALSE}

ppt_m <- read_csv(
  here::here("data", "study_one", "ppt_manual.csv")
) %>%
  as.data.table() %>%
  mutate(time = factor(
    x = time,
    levels = c("pre", "post"), labels = c("Pre", "Post"),
  ),
  order = fcase(block_num < 3, "Pre",
                block_num == 4, "First",
                block_num == 5, "Second"))

ppt_m_std <- ppt_m %>% 
  mutate(vel_m_filt_std = standardize(vel_m_filt),
          dec_m_filtfilt_std = standardize(dec_m_filtfilt)) %>%
  as.data.table()

ppt_acc_std <- ppt_m %>%
    dplyr::filter(!ppid %in% c("d1-001")) %>%
  mutate(acc_m_filtfilt_std = standardize(acc_m_filtfilt)) %>%
  as.data.table()
          
ppt_l_std <- ppt_m %>%
    mutate(vel_lat_filt_std = standardize(vel_lat_filt),
          acc_lat_filtfilt_std = standardize(acc_lat_filtfilt),
          dec_lat_filtfilt_std = standardize(dec_lat_filtfilt)
          ) %>%
  as.data.table()

ppt_acc_l_std <- ppt_m %>%
    dplyr::filter(ppid %in% c("d1-001")) %>%
  mutate(acc_lat_filtfilt_std = standardize(acc_lat_filtfilt)) %>%
  as.data.table()

ppt_tool <- read_csv(here::here("data", "study_one", "ppt_tool.csv")) %>%
  as.data.table()

landmark <- read_csv(here::here("data", "study_one", "landmark.csv")) %>%
    mutate(
        error_std = standardize(lapse_fix_error),
        target = factor(lapse_fix_target,
            levels = c("Elbow", "Forearm", "Wrist")
        ),
        error_cm = lapse_fix_error * 100,
        forearmlength = forearmlength * 100,
        forearmlength_std = standardize(forearmlength),
        time = factor(time,
            levels = c("pre", "post"),
            labels = c("Pre", "Post")
        ),
        order = factor(
            x = order, levels = c("pre", "first", "second"),
            labels = c("Pre", "First", "Second")
        )
    ) %>%
    as.data.table()
```

# Supplemental Analyses

## Reaching Task

### Bongers (2010) Replication
In Bongers's (2010) study, no effect of tool-use on kinematics was observed when considering the full block of trials in the post-test. He did, however, observe an effect when comparing a subset of trials: Those immediately after the tool-use block.

```{r by-trial-plots}
ppt_combined <- ppt_m %>% bind_rows(ppt_tool) %>% as.data.table()

ppt_combined <- ppt_combined %>% 
  mutate(overall_trial = fcase(time == "Pre", trial_num_in_block,
                               time == "Tool-use", trial_num_in_block + 18,
                               time == "Post", trial_num_in_block + 66)
                               )

ppt_combined_by_trial <- ppt_combined %>%
  dplyr::filter(vel_m_filt < 2000,
              !(time == "Tool-use" & vel_m_filt > 1500)) %>%
  group_by(overall_trial, time) %>%
  dplyr::summarise(
    m_vel = mean(vel_m_filt, na.rm = TRUE),
    m_acc = mean(acc_m_filtfilt, na.rm = TRUE),
    m_dec = mean(dec_m_filtfilt, na.rm = TRUE),
    lat_vel = mean(vel_lat_filt, na.rm = TRUE),
    lat_acc = mean(acc_lat_filtfilt, na.rm = TRUE),
    lat_dec = mean(dec_lat_filtfilt, na.rm = TRUE)
  )

velocity_trials <- ppt_combined_by_trial %>%
  ggplot(aes(x = overall_trial, y = m_vel, color = time)) +
    geom_line(size = 2) +
    stat_dots(side = "both") +
    labs(title = "Peak Velocity By Trial", subtitle = "Tool-use in VR (No Avatar)", x = "Trial", y = "Peak Velocity (mm/s)") +
    theme_tidybayes()+
    scale_color_manual(breaks = c("Pre", "Tool-use", "Post"),
    values = c("#001015", "firebrick", "#09A1D7"),
    labels = c("Pre", "Tool-use", "Post")) +
    theme(text = element_text(size = 34))

saveRDS(velocity_trials, here::here("figures", "velocity_trials.rds"))

ppt_combined_by_trial %>%
  ggplot(aes(x = overall_trial, y = m_acc, color = time)) +
    geom_line(size = 2) +
    labs(title = "Peak Acceleration By Trial", subtitle = "Tool-use in VR (No Avatar)", x = "Trial", y = "Peak Acceleration (mm/s^2)") +
    theme_tidybayes()+
    scale_color_manual(breaks = c("Pre", "Tool-use", "Post"),
    values = c("#001015", "firebrick", "#09A1D7"),
    labels = c("Pre", "Tool-use", "Post")) +
    theme(text = element_text(size = 34))
  
ppt_combined_by_trial %>%
  ggplot(aes(x = overall_trial, y = m_dec, color = time)) +
    geom_line(size = 2) +
    labs(title = "Peak Deceleration By Trial", subtitle = "Tool-use in VR (No Avatar)", x = "Trial", y = "Peak Deceleration (mm/s^2)") +
    theme_tidybayes()+
    scale_color_manual(breaks = c("Pre", "Tool-use", "Post"),
    values = c("#001015", "firebrick", "#09A1D7"),
    labels = c("Pre", "Tool-use", "Post")) +
    theme(text = element_text(size = 34))

ppt_combined_by_trial %>%
  ggplot(aes(x = overall_trial, y = lat_vel, color = time)) +
    geom_line(size = 2) +
    labs(title = "Peak Velocity Latency By Trial", subtitle = "Tool-use in VR (No Avatar)", x = "Trial", y = "Latency (ms)") +
    theme_tidybayes()+
    scale_color_manual(breaks = c("Pre", "Tool-use", "Post"),
    values = c("#001015", "firebrick", "#09A1D7"),
    labels = c("Pre", "Tool-use", "Post")) +
    theme(text = element_text(size = 34))

ppt_combined_by_trial %>%
  ggplot(aes(x = overall_trial, y = lat_acc, color = time)) +
    geom_line(size = 2) +
    labs(title = "Peak Acceleration Latency By Trial", subtitle = "Tool-use in VR (No Avatar)", x = "Trial", y = "Latency (ms)") +
    theme_tidybayes()+
    scale_color_manual(breaks = c("Pre", "Tool-use", "Post"),
    values = c("#001015", "firebrick", "#09A1D7"),
    labels = c("Pre", "Tool-use", "Post")) +
    theme(text = element_text(size = 34))

ppt_combined_by_trial %>%
  ggplot(aes(x = overall_trial, y = lat_dec, color = time)) +
    geom_line(size = 2) +
    labs(title = "Peak Deceleration Latency By Trial", subtitle = "Tool-use in VR (No Avatar)", x = "Trial", y = "Latency (ms)") +
    theme_tidybayes()+
    scale_color_manual(breaks = c("Pre", "Tool-use", "Post"),
    values = c("#001015", "firebrick", "#09A1D7"),
    labels = c("Pre", "Tool-use", "Post")) +
    theme(text = element_text(size = 34))
```


#### Is this influenced by order?

```{r}
order_plot_data <- ppt_combined %>%
dplyr::filter(
  overall_trial > 66,
  order != "Pre") %>%
group_by(
  overall_trial,
  order) %>% 
dplyr::summarise(
  m_vel = mean(vel_m_filt, na.rm = TRUE), 
  m_acc = mean(acc_m_filtfilt, na.rm = TRUE), 
  m_dec = mean(dec_m_filtfilt, na.rm = TRUE),
  lat_vel = mean(vel_lat_filt, na.rm = TRUE),
  lat_acc = mean(acc_lat_filtfilt, na.rm = TRUE),
  lat_dec = mean(dec_lat_filtfilt, na.rm = TRUE)
  ) 

order_plot_data %>%
ggplot(
  aes(x = overall_trial,
  y = m_vel,
  color = order)) +
  geom_line(size = 2) +
  theme_tidybayes() +
  labs(x = "Trial", y = "Peak Velocity") +
  scale_color_manual(
    breaks = c("First", "Second"),
    values = c("#001015", "#09A1D7"),
    labels = c("First", "Second")
  )

order_plot_data %>%
ggplot(
  aes(x = overall_trial,
  y = m_acc,
  color = order)) +
  geom_line(size = 2) +
  theme_tidybayes() +
  labs(x = "Trial", y = "Peak Acceleration") +
  scale_color_manual(
    breaks = c("First", "Second"),
    values = c("#001015", "#09A1D7"),
    labels = c("First", "Second")
  )

order_plot_data %>%
ggplot(
  aes(x = overall_trial,
  y = m_dec,
  color = order)) +
  geom_line(size = 2) +
  theme_tidybayes() +
  labs(x = "Trial", y = "Peak Deceleration") +
  scale_color_manual(
    breaks = c("First", "Second"),
    values = c("#001015", "#09A1D7"),
    labels = c("First", "Second")
  )

order_plot_data %>%
ggplot(
  aes(x = overall_trial,
  y = lat_vel,
  color = order)) +
  geom_line(size = 2) +
  theme_tidybayes() +
  labs(x = "Trial", y = "Velocity Latency") +
  scale_color_manual(
    breaks = c("First", "Second"),
    values = c("#001015", "#09A1D7"),
    labels = c("First", "Second")
  )

order_plot_data %>%
ggplot(
  aes(x = overall_trial,
  y = lat_acc,
  color = order)) +
  geom_line(size = 2) +
  theme_tidybayes() +
  labs(x = "Trial", y = "Acceleration Latency") +
  scale_color_manual(
    breaks = c("First", "Second"),
    values = c("#001015", "#09A1D7"),
    labels = c("First", "Second")
  )

order_plot_data %>%
ggplot(
  aes(x = overall_trial,
  y = lat_dec,
  color = order)) +
  geom_line(size = 2) +
  theme_tidybayes() +
  labs(x = "Trial", y = "Deceleration Latency") +
  scale_color_manual(
    breaks = c("First", "Second"),
    values = c("#001015", "#09A1D7"),
    labels = c("First", "Second")
  )
```

# Six-trial Models (Bongers 2010)

```{r bongers-replication, include=FALSE}
ppt_peaks_bongers <- ppt_m_std %>%
    dplyr::filter(
        (time == "Post" & 
        trial_num_in_block %in% c(1:6)) 
        | 
        (time == "Pre" & 
        trial_num_in_block %in% c(13:18))
        )

ppt_acceleration_and_latencies_bongers <- ppt_m %>%
  mutate(acc_m_filtfilt_std = standardize(acc_m_filtfilt)) %>%
  dplyr::filter(
      ppid != "d1-001",
      (time == "Post" & 
      trial_num_in_block %in% c(1:6)) 
      | 
      (time == "Pre" & 
      trial_num_in_block %in% c(13:18))
      )

```

As in Bongers, data is filtered such that the analysis only considers the last 6 trials of the first block (Pre) and the first 6 trials of the second block (Post) of manual reaching. 

## Peaks
### Velocity
#### Prior
```{r velocity-peak-prior}
velocity_peak_priors <- brm(
  vel_m_filt_std ~ 1 + time + (1 + time | ppid), 
  data = ppt_peaks_bongers, 
  family = gaussian,
  prior = c(
    set_prior(prior = "normal(-.2, 2)", class = "b", coef = "timePost"),
    set_prior(prior = "normal(0, 2)", class = "Intercept"),
    set_prior(prior = "exponential(1)", class = "sd"), 
    set_prior(prior = "exponential(1)", class = "sigma"),
    set_prior(prior = "lkj(1)", class = "cor", group = "ppid")
  ),
  sample_prior = "only",
  seed = 1337,
  silent = TRUE, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(velocity_peak_priors)
summary(velocity_peak_priors)
```

#### Posterior

```{r velocity-peak-posterior}
velocity_peaks <- update(
  velocity_peak_priors,
  sample_prior = "no",
  refresh = 0,
  seed = 1337,
  file = here::here("scripts", "for_osf", "tooluse_in_VR", "models", "supplementary", "peakvelocity_ppt_bongers")
  )

plot(velocity_peaks)
summary(velocity_peaks)

pp_check(velocity_peaks, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Peak Velocity",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Velocity (mm/s)"
  )

velbf <- bayesfactor_pointnull(
  velocity_peaks,
  direction = "<",
  prior = velocity_peak_priors
  ) %>% as.data.table()

vel_describe <- bayestestR::describe_posterior(
  velocity_peaks,
  centrality = "map",
  ci_method="hdi"
  ) %>% 
  dplyr::filter(Parameter == "b_timePost") %>% 
  mutate("Outcome" = "Peak Velocity")

(
  vel_describe <- bind_cols(
    vel_describe,
    "BF" = exp(
        velbf[Parameter == "b_timePost",
        log_BF]
        )
        )
)
```

### Acceleration
#### Prior
```{r acceleration-peak-prior}
acceleration_peak_priors <- brm(
  acc_m_filtfilt_std ~ 1 + time + (1 + time | ppid), 
  data = ppt_acceleration_and_latencies_bongers, 
  family = gaussian,
  prior = c(
    set_prior(prior = "normal(-.2, 2)", class = "b", coef = "timePost"),
    set_prior(prior = "normal(0, 2)", class = "Intercept"),
    set_prior(prior = "exponential(1)", class = "sd"), 
    set_prior(prior = "exponential(1)", class = "sigma"),
    set_prior(prior = "lkj(1)", class = "cor", group = "ppid")
    ),
  sample_prior = "only",
  seed = 1337,
  silent = TRUE, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(acceleration_peak_priors)
summary(acceleration_peak_priors)
```

#### Posterior

```{r acceleration-peak-posterior}
acceleration_peaks <- update(
  acceleration_peak_priors,
  sample_prior = "no",
  refresh = 0,
  seed = 1337,
  file = here::here("scripts", "for_osf", "tooluse_in_VR", "models", "supplementary", "peakacceleration_ppt_bongers")
  )

plot(acceleration_peaks)
summary(acceleration_peaks)

pp_check(acceleration_peaks, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Acceleration Peak",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Acceleration (mm/s^2)"
  )

accbf <- bayesfactor_pointnull(
  acceleration_peaks,
  direction = "<",
  prior = acceleration_peak_priors
  ) %>% as.data.table()

acc_describe <- bayestestR::describe_posterior(
  acceleration_peaks,
  centrality = "map",
  ci_method="hdi"
  ) %>% dplyr::filter(
    Parameter == "b_timePost"
  ) %>% 
  mutate("Outcome" = "Peak Acceleration")

(
  acc_describe <- bind_cols(
    acc_describe,
    "BF" = exp(
        accbf[Parameter == "b_timePost",
        log_BF]
        )
    )
  )

```

### Deceleration
#### Prior
```{r deceleration-peak-prior}
deceleration_peak_priors <- brm(
  dec_m_filtfilt_std ~ 1 + time + (1 + time | ppid), 
  data = ppt_peaks_bongers, 
  family = gaussian,
  prior = c(
    set_prior(prior = "normal(.2, 2)", class = "b", coef = "timePost"),
    set_prior(prior = "normal(0, 2)", class = "Intercept"),
    set_prior(prior = "exponential(1)", class = "sd"), 
    set_prior(prior = "exponential(1)", class = "sigma"),
    set_prior(prior = "lkj(1)", class = "cor", group = "ppid")
            ),
  sample_prior = "only",
  seed = 1337,
  silent = TRUE, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(deceleration_peak_priors)
summary(deceleration_peak_priors)
```

#### Posterior
```{r deceleration-peak-posterior}

deceleration_peaks <- update(
  deceleration_peak_priors,
  sample_prior = "no",
  seed = 1337,
  refresh = 0,
  file = here::here("scripts", "for_osf", "tooluse_in_VR", "models", "supplementary", "peakdeceleration_ppt_bongers")
  )

plot(deceleration_peaks)
summary(deceleration_peaks)

pp_check(deceleration_peaks, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Deceleration Peak",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Deceleration (mm/s^2)"
  )

dec_describe <- bayestestR::describe_posterior(
  deceleration_peaks,
  centrality = "map",
  ci_method="hdi"
  ) %>% dplyr::filter(
    Parameter == "b_timePost"
  ) %>% 
  mutate("Outcome" = "Peak Deceleration")

decbf <- bayesfactor_pointnull(
  deceleration_peaks,
  direction = ">",
  prior = deceleration_peak_priors
  ) %>% as.data.table()

(
  dec_describe <- bind_cols(
    dec_describe,
    "BF" = exp(
        decbf[Parameter == "b_timePost",
        log_BF]
        )
    )
    )

```

## Peak Latencies
### Preregistration changes
Changes from preregistration:  
- Lognormal distribution over gaussian due to better posterior fit  
- Unstandardized due to lognormal, and negative parameter estimates from standardization  
- Intercepts centered at empirical mean, with an SD equal to empirical SD * 2.5  
- Time effect centered at empirical SD / 5, with spread of empirical SD * 2.5  
- These changes do not change the interpretable results of the models, but do improve the fit of the models  

### Velocity

#### Prior

```{r velocity-latency-prior}

velocity_latency_priors <- brm(
  vel_lat_filt ~ 1 + time + (1 + time | ppid), 
  data = ppt_acceleration_and_latencies_bongers, 
  family = lognormal,
  prior = c(
     prior_string(
       prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(vel_lat_filt)] / 5
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(vel_lat_filt)] * 2.5
         ), 2), ")"
       ),
       class = "b"),
    # Use rstanarm approach to set Intercept prior
    # Use normal with mean of response, and sd of response * 2.5
    prior_string(
      prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_bongers[,mean(vel_lat_filt)]
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(vel_lat_filt)] * 2.5
         ), 2), ")"
       ),
      class = "Intercept"),
    prior(prior = "exponential(1)", class = "sd"),
    prior(prior = "exponential(1)", class = "sigma"),
    prior(prior = "lkj(1)", class = "cor", group = "ppid")
            ),
  sample_prior = "only",
  seed = 1337,
  silent = 2, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(velocity_latency_priors)
summary(velocity_latency_priors)
```

#### Posterior
```{r velocity-latency-posterior}

velocity_latencies <- update(
  velocity_latency_priors,
  sample_prior = "no",
  refresh = 0,
  seed = 1337,
  file = here::here("scripts", "for_osf", "tooluse_in_VR", "models", "supplementary", "velocity_latency_ppt_bongers")
  )

plot(velocity_latencies)
summary(velocity_latencies)

pp_check(velocity_latencies, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Velocity Latency",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Time (ms)"
  )

velocity_latencies_describe <- bayestestR::describe_posterior(
  velocity_latencies,
  centrality = "map",
  ci_method="hdi"
  ) %>% 
  dplyr::filter(
  Parameter == "b_timePost"
  ) %>% 
  mutate("Outcome" = "Velocity Latency")

vellatbf <- bayesfactor_pointnull(
  velocity_latencies,
  direction = ">",
  prior = velocity_latency_priors
  ) %>% as.data.table()

vel_lat_describe <- bind_cols(
    velocity_latencies_describe,
    "BF" = exp(
        vellatbf[Parameter == "b_timePost",
        log_BF]
        )
    )
```

### Acceleration
#### Prior
```{r acceleration-latency-prior}

# Acceleration Latency -------------

acceleration_latency_priors <- brm(
  acc_lat_filtfilt ~ 1 + time + (1 + time | ppid), 
  data = ppt_acceleration_and_latencies_bongers, 
  family = lognormal(link = "identity"),
  prior = c(
     prior_string(
       prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(acc_lat_filtfilt)] / 5
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(acc_lat_filtfilt)] * 2.5
         ), 2), ")"
       ),
       class = "b"),
    # Use rstanarm approach to set Intercept prior
    # Use normal with mean of response, and sd of response * 2.5
    prior_string(
      prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_bongers[,mean(acc_lat_filtfilt)]
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(acc_lat_filtfilt)] * 2.5
         ), 2), ")"
       ),
      class = "Intercept"),
    prior(prior = "exponential(1)", class = "sd"),
    prior(prior = "exponential(1)", class = "sigma"),
    prior(prior = "lkj(1)", class = "cor", group = "ppid")
            ),
  sample_prior = "only",
  seed = 1337,
  silent = 2, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(acceleration_latency_priors) 

```

#### Posterior
```{r acceleration-latency-posterior}

acceleration_latencies <- update(
  acceleration_latency_priors,
  sample_prior = "no",
  refresh = 0,
  seed = 1337,
  file = here::here("scripts", "for_osf", "tooluse_in_VR", "models", "supplementary", "acceleration_latency_ppt_bongers")
  )

plot(acceleration_latencies)
summary(acceleration_latencies)

pp_check(acceleration_latencies, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Acceleration Latency",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Time (ms)"
  )

acc_lat_describe <- bayestestR::describe_posterior(
  acceleration_latencies, centrality = "map",
  ci_method="hdi"
  ) %>% 
  dplyr::filter(
    Parameter == "b_timePost"
  ) %>% 
  mutate("Outcome" = "Acceleration Latency")

acclatbf <- bayesfactor_pointnull(
  acceleration_latencies,
  direction = ">",
  prior = acceleration_latency_priors
  ) %>% as.data.table()

(
  acc_lat_describe <- bind_cols(
    acc_lat_describe,
    "BF" = exp(
        acclatbf[
          Parameter == "b_timePost",
          log_BF
          ]
        )
    )
    )
```

### Deceleration
#### Prior
```{r deceleration-latency-prior}

deceleration_latency_priors <- brm(dec_lat_filtfilt ~ 1 + time + (1 + time | ppid), 
  data = ppt_acceleration_and_latencies_bongers, 
  family = lognormal(link = "identity"),
  prior = c(
     prior_string(
       prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(dec_lat_filtfilt)] / 5
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(dec_lat_filtfilt)] * 2.5
         ), 2), ")"
       ),
       class = "b"),
    # Use rstanarm approach to set Intercept prior
    # Use normal with mean of response, and sd of response * 2.5
    prior_string(
      prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_bongers[,mean(dec_lat_filtfilt)]
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(dec_lat_filtfilt)] * 2.5
         ), 2), ")"
       ),
      class = "Intercept"),
    prior(prior = "exponential(1)", class = "sd"),
    prior(prior = "exponential(1)", class = "sigma"),
    prior(prior = "lkj(1)", class = "cor", group = "ppid")
            ),
  sample_prior = "only",
  seed = 1337,
  silent = 2, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(deceleration_latency_priors)
summary(deceleration_latency_priors)
```

#### Posterior

```{r deceleration-latency-posterior}

deceleration_latencies <- update(
  deceleration_latency_priors,
  sample_prior = "no",
  seed = 1337,
  refresh = 0,
  file = here::here("scripts", "for_osf", "tooluse_in_VR", "models", "supplementary", "deceleration_latency_ppt_bongers")
  )

plot(deceleration_latencies)
summary(deceleration_latencies)

pp_check(deceleration_latencies, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Deceleration Latency",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Time (ms)"
  )

deceleration_latencies_describe <- bayestestR::describe_posterior(
  deceleration_latencies,
  centrality = "map",
  ci_method="hdi"
  ) %>% 
  dplyr::filter(
    Parameter == "b_timePost"
    ) %>% 
  mutate("Outcome" = "Deceleration Latency")

declatbf <- bayesfactor_pointnull(
  deceleration_latencies,
  direction = ">",
  prior = deceleration_latency_priors
  ) %>% as.data.table()

(
  dec_lat_describe <- bind_cols(
    deceleration_latencies_describe,
    "BF" = exp(
        declatbf[Parameter == "b_timePost",
        log_BF]
        )
    )
    )
```

# Summary Table

```{r table_one, results='asis'}
#| tbl-cap: Bongers Model Summary Table
model_params <- bind_rows(
  vel_describe,
  acc_describe,
  dec_describe,
  vel_lat_describe,
  acc_lat_describe,
  dec_lat_describe
) %>% dplyr::select(
  Outcome,
  BF,
  MAP,
  CI_low,
  CI_high
) %>% rename("Lower" = CI_low,
             "Upper" = CI_high,
             "Mode" = MAP)

fwrite(model_params, here::here("scripts", "for_osf", "tooluse_in_vr", "tables", "supplementary", "model_params_bongers.csv"))

model_table <- flextable::qflextable(model_params) %>%
  add_header_row(T, 
                 c(" ", "95% Highest Density Interval"), 
                 colwidths = c(3, 2)) %>% 
  add_header_lines("Table 1. Parameters of Kinematic Models") %>%
  border_outer(border = officer::fp_border(style = "none", 
                                           width = 0), 
               part = "header") %>%
  hline(i = 1, 
        border = officer::fp_border(style = "solid", 
                                    width = 1.5), 
        part = "header") %>%
  hline(i = 2, j= c(1:3), 
        border = officer::fp_border(style = "none", 
                                    width = 0), 
        part = "header") %>%
  hline(i = 2, j= c(4, 5), 
        border = officer::fp_border(style = "solid", 
                                    width = 1), 
        part = "header") %>%
  hline(i = 3, 
        border = officer::fp_border(style = "solid", 
                                    width = 1), 
        part = "header") %>%
  hline(i = 6, 
        border = officer::fp_border(style = "solid", 
                                    width = 1.5), 
        part = "body") %>%
  flextable::footnote(i = 3, j=c(1:2),
           value = as_paragraph(
             c(
               "Parameters given as standardized values, and represent the effect of time (tool-use).", 
               "Bayes Factors represent multiplicative evidence in favor of effect (Savage-Dickey Ratios).")
             ), 
           ref_symbols = c("a", "b"),
           part = "header"
          ) %>%
  font(fontname = "Times New Roman",
       part = "all") %>%
  fontsize(size = 9, part = "footer") %>%
  flextable::colformat_double(i=c(1:6), j = 3:5, digits = 3) %>%
  flextable::colformat_double(i=c(1:6), j = 2, digits = 2)
  

model_table

saveRDS(model_table, here::here("scripts", "for_osf", "tooluse_in_vr", "tables", "supplementary", "kinematic_table_bongers.rds"))

```


# Twelve-trial Models (Cardinali 2009)

Cardinali (2009) only had 12 trials in each of the two reaching blocks. This analysis only considers the last 12 of the pre-tool-use block, and first 12 of the post-tool-use block.

```{r cardinali-replication, include=FALSE}
ppt_peaks_cardinali <- ppt_m_std %>%
    dplyr::filter(
        (time == "Post" & 
        trial_num_in_block %in% c(1:12)) 
        | 
        (time == "Pre" & 
        trial_num_in_block %in% c(7:18))
        )

ppt_acceleration_and_latencies_cardinali <- ppt_m %>%
  mutate(acc_m_filtfilt_std = standardize(acc_m_filtfilt)) %>%
  dplyr::filter(
      ppid != "d1-001",
      (time == "Post" & 
      trial_num_in_block %in% c(1:12)) 
      | 
      (time == "Pre" & 
      trial_num_in_block %in% c(7:18))
      )

```

## Peaks
### Velocity
#### Prior
```{r velocity-peak-prior-cardinali}
velocity_peak_priors <- brm(
  vel_m_filt_std ~ 1 + time + (1 + time | ppid), 
  data = ppt_peaks_bongers, 
  family = gaussian,
  prior = c(
    set_prior(prior = "normal(-.2, 2)", class = "b", coef = "timePost"),
    set_prior(prior = "normal(0, 2)", class = "Intercept"),
    set_prior(prior = "exponential(1)", class = "sd"), 
    set_prior(prior = "exponential(1)", class = "sigma"),
    set_prior(prior = "lkj(1)", class = "cor", group = "ppid")
  ),
  sample_prior = "only",
  seed = 1337,
  silent = TRUE, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(velocity_peak_priors)
summary(velocity_peak_priors)
```

#### Posterior

```{r velocity-peak-posterior-cardinali}
velocity_peaks <- update(
  velocity_peak_priors,
  sample_prior = "no",
  refresh = 0,
  seed = 1337,
  file = here::here("scripts", "for_osf", "tooluse_in_VR", "models", "supplementary", "peakvelocity_ppt_cardinali")
  )

plot(velocity_peaks)
summary(velocity_peaks)

pp_check(velocity_peaks, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Peak Velocity",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Velocity (mm/s)"
  )

velbf <- bayesfactor_pointnull(
  velocity_peaks,
  direction = "<",
  prior = velocity_peak_priors
  ) %>% as.data.table()

vel_describe <- bayestestR::describe_posterior(
  velocity_peaks,
  centrality = "map",
  ci_method="hdi"
  ) %>% 
  dplyr::filter(Parameter == "b_timePost") %>% 
  mutate("Outcome" = "Peak Velocity")

(
  vel_describe <- bind_cols(
    vel_describe,
    "BF" = exp(
        velbf[Parameter == "b_timePost",
        log_BF]
        )
        )
)
```

### Acceleration
#### Prior
```{r acceleration-peak-prior-cardinali}
acceleration_peak_priors <- brm(
  acc_m_filtfilt_std ~ 1 + time + (1 + time | ppid), 
  data = ppt_acceleration_and_latencies_cardinali, 
  family = gaussian,
  prior = c(
    set_prior(prior = "normal(-.2, 2)", class = "b", coef = "timePost"),
    set_prior(prior = "normal(0, 2)", class = "Intercept"),
    set_prior(prior = "exponential(1)", class = "sd"), 
    set_prior(prior = "exponential(1)", class = "sigma"),
    set_prior(prior = "lkj(1)", class = "cor", group = "ppid")
    ),
  sample_prior = "only",
  seed = 1337,
  silent = TRUE, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(acceleration_peak_priors)
summary(acceleration_peak_priors)
```

#### Posterior

```{r acceleration-peak-posterior-cardinali}
acceleration_peaks <- update(
  acceleration_peak_priors,
  sample_prior = "no",
  refresh = 0,
  seed = 1337,
  file = here::here("scripts", "for_osf", "tooluse_in_VR", "models", "supplementary", "peakacceleration_ppt_cardinali")
  )

plot(acceleration_peaks)
summary(acceleration_peaks)

pp_check(acceleration_peaks, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Acceleration Peak",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Acceleration (mm/s^2)"
  )

accbf <- bayesfactor_pointnull(
  acceleration_peaks,
  direction = "<",
  prior = acceleration_peak_priors
  ) %>% as.data.table()

acc_describe <- bayestestR::describe_posterior(
  acceleration_peaks,
  centrality = "map",
  ci_method="hdi"
  ) %>% dplyr::filter(
    Parameter == "b_timePost"
  ) %>% 
  mutate("Outcome" = "Peak Acceleration")

(
  acc_describe <- bind_cols(
    acc_describe,
    "BF" = exp(
        accbf[Parameter == "b_timePost",
        log_BF]
        )
    )
  )

```

### Deceleration
#### Prior
```{r deceleration-peak-prior-cardinali}
deceleration_peak_priors <- brm(
  dec_m_filtfilt_std ~ 1 + time + (1 + time | ppid), 
  data = ppt_peaks_cardinali, 
  family = gaussian,
  prior = c(
    set_prior(prior = "normal(.2, 2)", class = "b", coef = "timePost"),
    set_prior(prior = "normal(0, 2)", class = "Intercept"),
    set_prior(prior = "exponential(1)", class = "sd"), 
    set_prior(prior = "exponential(1)", class = "sigma"),
    set_prior(prior = "lkj(1)", class = "cor", group = "ppid")
            ),
  sample_prior = "only",
  seed = 1337,
  silent = TRUE, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(deceleration_peak_priors)
summary(deceleration_peak_priors)
```

#### Posterior
```{r deceleration-peak-posterior-cardinali}

deceleration_peaks <- update(
  deceleration_peak_priors,
  sample_prior = "no",
  seed = 1337,
  refresh = 0,
  file = here::here("scripts", "for_osf", "tooluse_in_VR", "models", "supplementary", "peakdeceleration_ppt_cardinali")
  )

plot(deceleration_peaks)
summary(deceleration_peaks)

pp_check(deceleration_peaks, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Deceleration Peak",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Deceleration (mm/s^2)"
  )

dec_describe <- bayestestR::describe_posterior(
  deceleration_peaks,
  centrality = "map",
  ci_method="hdi"
  ) %>% dplyr::filter(
    Parameter == "b_timePost"
  ) %>% 
  mutate("Outcome" = "Peak Deceleration")

decbf <- bayesfactor_pointnull(
  deceleration_peaks,
  direction = ">",
  prior = deceleration_peak_priors
  ) %>% as.data.table()

(
  dec_describe <- bind_cols(
    dec_describe,
    "BF" = exp(
        decbf[Parameter == "b_timePost",
        log_BF]
        )
    )
    )

```

## Peak Latencies
### Preregistration changes
Changes from preregistration:  
- Lognormal distribution over gaussian due to better posterior fit  
- Unstandardized due to lognormal, and negative parameter estimates from standardization  
- Intercepts centered at empirical mean, with an SD equal to empirical SD * 2.5  
- Time effect centered at empirical SD / 5, with spread of empirical SD * 2.5  
- These changes do not change the interpretable results of the models, but do improve the fit of the models  

### Velocity

#### Prior

```{r velocity-latency-prior-cardinali}

velocity_latency_priors <- brm(
  vel_lat_filt ~ 1 + time + (1 + time | ppid), 
  data = ppt_acceleration_and_latencies_cardinali, 
  family = lognormal,
  prior = c(
     prior_string(
       prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_cardinali[,sd(vel_lat_filt)] / 5
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_cardinali[,sd(vel_lat_filt)] * 2.5
         ), 2), ")"
       ),
       class = "b"),
    # Use rstanarm approach to set Intercept prior
    # Use normal with mean of response, and sd of response * 2.5
    prior_string(
      prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_cardinali[,mean(vel_lat_filt)]
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_cardinali[,sd(vel_lat_filt)] * 2.5
         ), 2), ")"
       ),
      class = "Intercept"),
    prior(prior = "exponential(1)", class = "sd"),
    prior(prior = "exponential(1)", class = "sigma"),
    prior(prior = "lkj(1)", class = "cor", group = "ppid")
            ),
  sample_prior = "only",
  seed = 1337,
  silent = 2, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(velocity_latency_priors)
summary(velocity_latency_priors)
```

#### Posterior
```{r velocity-latency-posterior-cardinali}

velocity_latencies <- update(
  velocity_latency_priors,
  sample_prior = "no",
  refresh = 0,
  seed = 1337,
  file = here::here("scripts", "for_osf", "tooluse_in_VR", "models", "supplementary", "velocity_latency_ppt_cardinali")
  )

plot(velocity_latencies)
summary(velocity_latencies)

pp_check(velocity_latencies, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Velocity Latency",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Time (ms)"
  )

velocity_latencies_describe <- bayestestR::describe_posterior(
  velocity_latencies,
  centrality = "map",
  ci_method="hdi"
  ) %>% 
  dplyr::filter(
  Parameter == "b_timePost"
  ) %>% 
  mutate("Outcome" = "Velocity Latency")

vellatbf <- bayesfactor_pointnull(
  velocity_latencies,
  direction = ">",
  prior = velocity_latency_priors
  ) %>% as.data.table()

vel_lat_describe <- bind_cols(
    velocity_latencies_describe,
    "BF" = exp(
        vellatbf[Parameter == "b_timePost",
        log_BF]
        )
    )
```

### Acceleration
#### Prior
```{r acceleration-latency-prior-cardinali}

# Acceleration Latency -------------

acceleration_latency_priors <- brm(
  acc_lat_filtfilt ~ 1 + time + (1 + time | ppid), 
  data = ppt_acceleration_and_latencies_cardinali, 
  family = lognormal(link = "identity"),
  prior = c(
     prior_string(
       prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_cardinali[,sd(acc_lat_filtfilt)] / 5
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_cardinali[,sd(acc_lat_filtfilt)] * 2.5
         ), 2), ")"
       ),
       class = "b"),
    # Use rstanarm approach to set Intercept prior
    # Use normal with mean of response, and sd of response * 2.5
    prior_string(
      prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_cardinali[,mean(acc_lat_filtfilt)]
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_cardinali[,sd(acc_lat_filtfilt)] * 2.5
         ), 2), ")"
       ),
      class = "Intercept"),
    prior(prior = "exponential(1)", class = "sd"),
    prior(prior = "exponential(1)", class = "sigma"),
    prior(prior = "lkj(1)", class = "cor", group = "ppid")
            ),
  sample_prior = "only",
  seed = 1337,
  silent = 2, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(acceleration_latency_priors) 

```

#### Posterior
```{r acceleration-latency-posterior-cardinali}

acceleration_latencies <- update(
  acceleration_latency_priors,
  sample_prior = "no",
  refresh = 0,
  seed = 1337,
  file = here::here("scripts", "for_osf", "tooluse_in_VR", "models", "supplementary", "acceleration_latency_ppt_cardinali")
  )

plot(acceleration_latencies)
summary(acceleration_latencies)

pp_check(acceleration_latencies, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Acceleration Latency",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Time (ms)"
  )

acc_lat_describe <- bayestestR::describe_posterior(
  acceleration_latencies, centrality = "map",
  ci_method="hdi"
  ) %>% 
  dplyr::filter(
    Parameter == "b_timePost"
  ) %>% 
  mutate("Outcome" = "Acceleration Latency")

acclatbf <- bayesfactor_pointnull(
  acceleration_latencies,
  direction = ">",
  prior = acceleration_latency_priors
  ) %>% as.data.table()

(
  acc_lat_describe <- bind_cols(
    acc_lat_describe,
    "BF" = exp(
        acclatbf[
          Parameter == "b_timePost",
          log_BF
          ]
        )
    )
    )
```

### Deceleration
#### Prior
```{r deceleration-latency-prior-cardinali}

deceleration_latency_priors <- brm(dec_lat_filtfilt ~ 1 + time + (1 + time | ppid), 
  data = ppt_acceleration_and_latencies_cardinali, 
  family = lognormal(link = "identity"),
  prior = c(
     prior_string(
       prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_cardinali[,sd(dec_lat_filtfilt)] / 5
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_cardinali[,sd(dec_lat_filtfilt)] * 2.5
         ), 2), ")"
       ),
       class = "b"),
    # Use rstanarm approach to set Intercept prior
    # Use normal with mean of response, and sd of response * 2.5
    prior_string(
      prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_cardinali[,mean(dec_lat_filtfilt)]
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_cardinali[,sd(dec_lat_filtfilt)] * 2.5
         ), 2), ")"
       ),
      class = "Intercept"),
    prior(prior = "exponential(1)", class = "sd"),
    prior(prior = "exponential(1)", class = "sigma"),
    prior(prior = "lkj(1)", class = "cor", group = "ppid")
            ),
  sample_prior = "only",
  seed = 1337,
  silent = 2, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(deceleration_latency_priors)
summary(deceleration_latency_priors)
```

#### Posterior

```{r deceleration-latency-posterior-cardinali}

deceleration_latencies <- update(
  deceleration_latency_priors,
  sample_prior = "no",
  seed = 1337,
  refresh = 0,
  file = here::here("scripts", "for_osf", "tooluse_in_VR", "models", "supplementary", "deceleration_latency_ppt_cardinali")
  )

plot(deceleration_latencies)
summary(deceleration_latencies)

pp_check(deceleration_latencies, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Deceleration Latency",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Time (ms)"
  )

deceleration_latencies_describe <- bayestestR::describe_posterior(
  deceleration_latencies,
  centrality = "map",
  ci_method="hdi"
  ) %>% 
  dplyr::filter(
    Parameter == "b_timePost"
    ) %>% 
  mutate("Outcome" = "Deceleration Latency")

declatbf <- bayesfactor_pointnull(
  deceleration_latencies,
  direction = ">",
  prior = deceleration_latency_priors
  ) %>% as.data.table()

(
  dec_lat_describe <- bind_cols(
    deceleration_latencies_describe,
    "BF" = exp(
        declatbf[Parameter == "b_timePost",
        log_BF]
        )
    )
    )
```

# Summary Table

```{r table_one-cardinali, results='asis'}
#| tbl-cap: Cardinali Model Summary Table
model_params <- bind_rows(
  vel_describe,
  acc_describe,
  dec_describe,
  vel_lat_describe,
  acc_lat_describe,
  dec_lat_describe
) %>% dplyr::select(
  Outcome,
  BF,
  MAP,
  CI_low,
  CI_high
) %>% rename("Lower" = CI_low,
             "Upper" = CI_high,
             "Mode" = MAP)

fwrite(model_params, here::here("scripts", "for_osf", "tooluse_in_vr", "tables", "supplementary", "model_params_cardinali.csv"))

model_table <- flextable::qflextable(model_params) %>%
  add_header_row(T, 
                 c(" ", "95% Highest Density Interval"), 
                 colwidths = c(3, 2)) %>% 
  add_header_lines("Parameters of Kinematic Models") %>%
  border_outer(border = officer::fp_border(style = "none", 
                                           width = 0), 
               part = "header") %>%
  hline(i = 1, 
        border = officer::fp_border(style = "solid", 
                                    width = 1.5), 
        part = "header") %>%
  hline(i = 2, j= c(1:3), 
        border = officer::fp_border(style = "none", 
                                    width = 0), 
        part = "header") %>%
  hline(i = 2, j= c(4, 5), 
        border = officer::fp_border(style = "solid", 
                                    width = 1), 
        part = "header") %>%
  hline(i = 3, 
        border = officer::fp_border(style = "solid", 
                                    width = 1), 
        part = "header") %>%
  hline(i = 6, 
        border = officer::fp_border(style = "solid", 
                                    width = 1.5), 
        part = "body") %>%
  flextable::footnote(i = 3, j=c(1:2),
           value = as_paragraph(
             c(
               "Parameters given as standardized values, and represent the effect of time (tool-use).", 
               "Bayes Factors represent multiplicative evidence in favor of effect (Savage-Dickey Ratios).")
             ), 
           ref_symbols = c("a", "b"),
           part = "header"
          ) %>%
  font(fontname = "Times New Roman",
       part = "all") %>%
  fontsize(size = 9, part = "footer") %>%
  flextable::colformat_double(i=c(1:6), j = 3:5, digits = 3) %>%
  flextable::colformat_double(i=c(1:6), j = 2, digits = 2)
  

model_table

saveRDS(model_table, here::here("scripts", "for_osf", "tooluse_in_vr", "tables", "supplementary", "kinematic_table_cardinali.rds"))

```

# Does Forearm Length Predict Baseline Reaching Kinematics?

```{r}
ppt_forearmlength <- landmark[, .(forearmlength = mean(forearmlength)),
    by = c("ppid")
] %>%
    merge(ppt_m, by = "ppid") %>%
    as.data.table()

t <- ppt_forearmlength[
    time == "Pre",
    `:=`(
        forearmlength_std = standardize(forearmlength),
        vel_m_filt_std = standardize(vel_m_filt),
        acc_m_filtfilt_std = standardize(acc_m_filtfilt),
        dec_m_filtfilt_std = standardize(dec_m_filtfilt),
        vel_lat_filt_std = standardize(vel_lat_filt),
        acc_lat_filtfilt_std = standardize(acc_lat_filtfilt),
        dec_lat_filtfilt_std = standardize(dec_lat_filtfilt),
        ppid = factor(ppid),
        trial_num_in_block = trial_num_in_block
    )
]

vel <- t %>%
    group_by(ppid) %>%
    dplyr::summarise(
        forearmlength = mean(forearmlength),
        vel_m_filt = mean(vel_m_filt)
    ) %>%
    ggplot(aes(x = forearmlength, y = vel_m_filt)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)

acc <- t %>%
    group_by(ppid) %>%
    dplyr::summarise(
        forearmlength = mean(forearmlength),
        acc_m_filtfilt = mean(acc_m_filtfilt)
    ) %>%
    ggplot(aes(x = forearmlength, y = acc_m_filtfilt)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)

dec <- t %>%
    group_by(ppid) %>%
    dplyr::summarise(
        forearmlength = mean(forearmlength),
        dec_m_filtfilt = mean(dec_m_filtfilt)
    ) %>%
    ggplot(aes(x = forearmlength, y = dec_m_filtfilt)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)

vel_lat <- t %>%
    group_by(ppid) %>%
    dplyr::summarise(
        forearmlength = mean(forearmlength),
        vel_lat_filt = mean(vel_lat_filt)
    ) %>%
    ggplot(aes(x = forearmlength, y = vel_lat_filt)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)

acc_lat <- t %>%
    group_by(ppid) %>%
    dplyr::summarise(
        forearmlength = mean(forearmlength),
        acc_lat_filtfilt = mean(acc_lat_filtfilt)
    ) %>%
    ggplot(aes(x = forearmlength, y = acc_lat_filtfilt)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)

dec_lat <- t %>%
    group_by(ppid) %>%
    dplyr::summarise(
        forearmlength = mean(forearmlength),
        dec_lat_filtfilt = mean(dec_lat_filtfilt)
    ) %>%
    ggplot(aes(x = forearmlength, y = dec_lat_filtfilt)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)

(vel + acc + dec) / (vel_lat + acc_lat + dec_lat) & theme_tidybayes()
```

# Fatigue Model

```{r fatigue-data, include=FALSE}
participant_info <- fread(here::here("data", "1_tooluseinvr", "participant_info.csv")) %>%
  dplyr::select(
      ppid, age, gender, fatigue, performance_hypothesis
  ) %>%
  mutate(
    fatigue = factor(fatigue, levels = c(0, 1), labels = c("No", "Yes")),
    performance_hypothesis = factor(performance_hypothesis, levels = c(0, 1), labels = c("No", "Yes"))
  ) 
  

participant_info_and_kinematics <- ppt_m %>%
      left_join(participant_info, by = "ppid") %>%
      mutate(
          overall_trial = fifelse(
              time == "Post",
              trial_num_in_block + 18,
              trial_num_in_block
          )
      )


ppt_peaks_bongers_fatigue <- participant_info_and_kinematics %>%
    dplyr::filter(
        (time == "Post" & 
        trial_num_in_block %in% c(1:6)) 
        | 
        (time == "Pre" & 
        trial_num_in_block %in% c(13:18))
        ) %>%
        mutate(
            vel_m_filt_std = standardize(vel_m_filt),
            acc_m_filtfilt_std = standardize(acc_m_filtfilt),
            dec_m_filtfilt_std = standardize(dec_m_filtfilt)
        )


cor <- ppt_forearmlength %>%
    group_by(ppid) %>%
    dplyr::summarise(
        forearmlength = mean(forearmlength),
        vel_m_filt = mean(vel_m_filt),
        acc_m_filtfilt = mean(acc_m_filtfilt),
        acc_lat_filtfilt = mean(acc_lat_filtfilt),
        dec_m_filtfilt = mean(dec_m_filtfilt),
        vel_lat_filt = mean(vel_lat_filt),
        dec_lat_filtfilt = mean(dec_lat_filtfilt,
            acc_lat_filtfilt = mean(acc_lat_filtfilt)
        )
    ) %>%
    correlation::correlation(
        method = "auto",
        bayesian = TRUE,
        partial = FALSE
    )
```

As in Bongers, data is filtered such that the analysis only considers the last 6 trials of the first block (Pre) and the first 6 trials of the second block (Post) of manual reaching. 

## Peaks
### Velocity
#### Prior
```{r fatigue-velocity-peak-prior}
velocity_peak_priors <- brm(
  vel_m_filt_std ~ 1 + time * fatigue + (1 + time * fatigue | ppid), 
  data = ppt_peaks_bongers_fatigue, 
  family = gaussian,
  prior = c(
    set_prior(prior = "normal(-.2, 2)", class = "b", coef = "timePost"),
    set_prior(prior = "normal(0, 2)", class = "b", coef = "fatigueYes"),
    set_prior(prior = "normal(0, 2)", class = "Intercept"),
    set_prior(prior = "exponential(1)", class = "sd"), 
    set_prior(prior = "exponential(1)", class = "sigma"),
    set_prior(prior = "lkj(1)", class = "cor", group = "ppid")
  ),
  sample_prior = "only",
  seed = 1337,
  silent = TRUE, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(velocity_peak_priors)
summary(velocity_peak_priors)
```

#### Posterior

```{r fatigue-velocity-peak-posterior}
velocity_peaks <- update(
  velocity_peak_priors,
  sample_prior = "no",
  refresh = 0,
  seed = 1337,
  #file = here::here("scripts", "for_osf", "cumulative_analyses", "models", "peakvelocity_ppt_fatigue_bongers")
  )

plot(velocity_peaks)
summary(velocity_peaks)

pp_check(velocity_peaks, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Peak Velocity",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Velocity (mm/s)"
  )

velbf <- bayesfactor_pointnull(
  velocity_peaks,
  direction = "<",
  prior = velocity_peak_priors
  ) %>% as.data.table()

vel_describe <- bayestestR::describe_posterior(
  velocity_peaks,
  centrality = "map",
  ci_method="hdi"
  ) %>% 
  dplyr::filter(Parameter == "b_timePost:fatigueYes") %>% 
  mutate("Outcome" = "Peak Velocity")

(
  vel_describe <- bind_cols(
    vel_describe,
    "BF" = exp(
        velbf[
          Parameter == "b_timePost:fatigueYes",
          log_BF
          ]
        )
        )
)
```

```{r}
fatigue_points <- participant_info_and_kinematics %>%
    group_by(overall_trial, ppid, fatigue) %>%
    dplyr::summarise(
        m_vel = mean(vel_m_filt),
        m_acc = mean(acc_m_filtfilt),
        m_dec = mean(dec_m_filtfilt)
    )
fatigue_lines <- participant_info_and_kinematics %>%
    group_by(overall_trial, fatigue, time) %>%
    dplyr::summarise(
        m_vel = mean(vel_m_filt),
        m_acc = mean(acc_m_filtfilt),
        m_dec = mean(dec_m_filtfilt)
    )

fatigue_plot <- fatigue_points %>%
    ggplot(
      aes(
        x = overall_trial,
        y = m_vel,
        fill = fatigue,
        color = fatigue
      )
    ) +
    geom_dots(alpha = .5) +
    geom_line(
      data = fatigue_lines,
      aes(
        x = overall_trial,
        y = m_vel,
        color = fatigue,
        group = interaction(fatigue, time)
      ),
      linewidth = 3
    ) +
    labs(
        title = "Peak Velocity By Trial",
        subtitle = "Fatigue vs. No Fatigue",
        x = "Trial",
        y = "Peak Velocity (mm/s)",
        color = "Fatigue",
        fill = "Fatigue"
    ) +
    theme_tidybayes() +
    scale_fill_manual(
        breaks = c("No", "Yes"),
        values = c("#001015", "#09A1D7"),
        labels = c("No", "Yes")
    ) +
    scale_color_manual(
        breaks = c("No", "Yes"),
        values = c("#001015", "#09A1D7"),
        labels = c("No", "Yes")
    ) +
    theme(text = element_text(size = 34))

fatigue_plot
ggsave(
    filename = here::here("scripts", "for_osf", "tooluse_in_vr", "figures", "fatigue_plot.png"),
    plot = fatigue_plot,
    width = 20,
    height = 10,
    units = "in",
    dpi = 300,
    background = "transparent"
    )
saveRDS(fatigue_plot, here::here("scripts", "for_osf", "tooluse_in_vr", "figures", "fatigue_plot.rds"))
```


```{r}
sessioninfo::package_info()
```