---
title: "Cumulative Analyses"
author: "Joshua Bell"
date: "03/10/2023"
output: html_document
format:
  html:
    toc: true
    toc-depth: 3
    toc-float: true
    toc-placement: left
---

# Imports
## Present Studies
```{r setup, include=TRUE}
pkgs <- c("dplyr", "tidyr", "readr", "flextable", "data.table", "magrittr", "ggridges", "here", "ggplot2", "patchwork", "tidybayes", "correlation", "knitr", "datawizard", "brms", "bayestestR", "RColorBrewer", "latex2exp", "showtext")
for(i in pkgs){
  if(!i %in% rownames(installed.packages())){ 
    install.packages(i) 
    library(i, character.only = TRUE)
  }
  else(library(i, character.only = TRUE))
}
# Sets stan backend to cmdstan. You will need to install the cmdstanr package and set up the toolchain.
options("mc.cores" = parallel::detectCores(), "brms.backend" = "cmdstan", tinytex.verbose = T)
showtext_auto()
b = 4800/parallel::detectCores()
i = 48000/parallel::detectCores()
ch = parallel::detectCores()
co = parallel::detectCores()
control_list <- list(adapt_delta = .995, max_treedepth = 15)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = TRUE, fig.width = 12, fig.height = 8)

ppt_m <- read_csv(here::here("data", "study_one", "ppt_manual.csv")) %>%
        bind_rows(
            read_csv(here::here("data", "study_two", "ppt_manual.csv")),
            read_csv(here::here("data", "study_three", "ppt_manual.csv"))) %>%
        as.data.table() %>%
        mutate(
        study = fcase(
            ppid %like% "d1-0", "VR (No Avatar)",
            ppid %like% "d2-0", "Real-world",
            ppid %like% "d3-0", "VR (Avatar)",
            default = NA),
        time = factor(x = time,
            levels = c("pre", "post"),
            labels = c("Pre", "Post")),
        order = fifelse(
            ppid == "d2-018" & is.na(order), "first", order
        ),
        order = factor(x = order,
            levels = c("pre", "first", "second"),
            labels = c("Pre", "First", "Second")),

        )



landmark <- read_csv(here::here("data", "study_one", "landmark.csv")) %>%
    bind_rows(
        read_csv(here::here("data", "study_two", "landmark.csv")),
        read_csv(here::here("data", "study_three", "landmark.csv"))) %>%
    mutate(
      study = fcase(
            ppid %like% "d1-0", "VR (No Avatar)",
            ppid %like% "d2-0", "Real-world",
            ppid %like% "d3-0", "VR (Avatar)",
        default = NA),
      error_std = standardize(lapse_fix_error),
         target = factor(lapse_fix_target,
            levels = c("Elbow", "Forearm", "Wrist")),
         error_cm = lapse_fix_error * 100,
         forearmlength = forearmlength * 100,
         forearmlength_std = (forearmlength - mean(forearmlength)) / sd(forearmlength),
         time = factor(time,
            levels = c("pre", "post"),
            labels= c("Pre", "Post")),
         order = factor(x = order, levels = c("pre", "first", "second"),
            labels = c("Pre", "First", "Second"))
            ) %>%
            as.data.table()

participant_info <- bind_rows(
read_csv(
    here::here("data", "1_tooluseinVR", "participant_info.csv"),
),
read_csv(
    here::here("data", "2_toolusenotinVR", "participant_info.csv"),
),
read_csv(
    here::here("data", "3_avatartooluse", "participant_info_coded.csv"),
)[, fatigue := ifelse(fatigue_yn, 1, 0)]
) %>%
    mutate(
          study = fcase(ppid %like% "d1-0", "VR (No Avatar)",
                        ppid %like% "d2-0", "Real-world",
                        ppid %like% "d3-0", "VR (Avatar)",
                        default = NA)
    ) %>%
    as.data.table()
    
    



ppt_forearmlength <- landmark[, .(forearmlength = mean(forearmlength)),
                                by = c("ppid")] %>% merge(ppt_m, by = c("ppid")) %>%
                                as.data.table()


ppt_forearm_surveys <- merge(
    ppt_forearmlength,
participant_info[,
        .(
            ppid,
            study,
            age,
            gender,
            fatigue,
            performance_hypothesis
        )
    ],
    by = c("ppid", "study")
)
```

## Change comparison across all studies

```{r}
kinematic_change <- bind_rows(
    read_csv(here::here("scripts", "for_osf", "tooluse_in_VR", "plot_data", "kinematic_draws_change.csv")) %>% mutate(study = "VR (No Avatar)"),
    read_csv(here::here("scripts", "for_osf", "tooluse_in_real", "plot_data", "kinematic_draws_change.csv")) %>% mutate(study = "Real-world"),
    read_csv(here::here("scripts", "for_osf", "tooluse_avatar", "plot_data", "kinematic_draws_change.csv")) %>% mutate(study = "VR (Avatar)")
)

kinematic_change <- kinematic_change %>%
    mutate(
        outcome = factor(Outcome,
            levels = c("Peak Acceleration","Peak Velocity", "Peak Deceleration", "Acceleration Latency", "Velocity Latency", "Deceleration Latency"),
            labels = c("Peak Acceleration", "Peak Velocity", "Peak Deceleration", "Acceleration Latency", "Velocity Latency", "Deceleration Latency")),
        change = .epred,
        study = factor(study,
            levels = c("VR (No Avatar)", "VR (Avatar)", "Real-world"),
            labels = c("VR (No Avatar)", "VR (Avatar)", "Real-world"))
    )

## Cardinali et al. (2009) values (from figure 1)
mupre <- 1243.2
se <- 25.6
mupost <- 1195.2


velchange <- mupost - mupre
velchange_ci <- se * 1.96

velchangedf <- data.frame(
    study = c(0.5, 3.5),
    change = c(velchange, velchange)
)

decchange <- 448.74
decchange_ci <- 50 * 1.96

decchangedf <- data.frame(
    study = c(0.5, 3.5),
    change = c(decchange, decchange)
)

accchange <- -480
accchange_ci <- 608 * 1.96

accchangedf <- data.frame(
    study = c(0.5, 3.5),
    change = c(accchange, accchange)
)

acclatchange <- 11.67
acclatchange_ci <- 8.75 * 1.96

acclatchangedf <- data.frame(
    study = c(0.5, 3.5),
    change = c(acclatchange, acclatchange)
)

vellatchange <- 16
vellatchange_ci <- 18.4 * 1.96

vellatchangedf <- data.frame(
    study = c(0.5, 3.5),
    change = c(vellatchange, vellatchange)
)

declatchange <- 19.2
declatchange_ci <- 14.4 * 1.96

declatchangedf <- data.frame(
    study = c(0.5, 3.5),
    change = c(declatchange, declatchange)
)

# Plot change in kinematic error for each outcome, within each study, using stat_eye
# Outcome: Peak Velocity, Peak Acceleration, Peak Deceleration, Velocity Latency, Acceleration Latency, Deceleration Latency
# Study: VR (No Avatar), Real-world, VR (Avatar)
# Create six individual plots, one for each outcome, since the scales are different for each outcome. 
# Then use patchwork to put them together

# Define a function to create each plot
create_kinematic_peak_plot <- function(df, outcome_str, ymin, ymax, ylab) {
    past_value <- fcase(
        outcome_str == "Peak Velocity", "velchange",
        outcome_str == "Peak Acceleration", "accchange",
        outcome_str == "Peak Deceleration", "decchange",
        default = NA
    )

    past_df <- get(paste0(past_value, "df"), envir = parent.frame()) %>%
    as.data.frame()

    df %>%
        dplyr::filter(outcome == outcome_str) %>%
        ggplot(aes(x = study, y = change, fill = study)) +
        geom_blank() +
        geom_ribbon(
            data = past_df %>%
                dplyr::mutate(
                    ymin = change - get(paste0(past_value, "_ci")),
                    ymax = change + get(paste0(past_value, "_ci"))
                ),
            aes(ymin = ymin, ymax = ymax, x = study, fill = "Cardinali et al. (2009)"),
            alpha = 0.6
        ) +
        stat_eye() +
        geom_hline(
            yintercept = 0,
            linetype = "dashed",
            linewidth = 1.5
            ) +
        geom_hline(
            yintercept = get(paste0(past_value)),
            linetype = "solid",
            color = "#003566",
            linewidth = 2
        ) +
        theme_tidybayes() +
        theme(
            axis.text.x = element_blank(),
            axis.title.x = element_blank(),
            axis.text.y = element_text(angle = 0, hjust = 1, color = "black", size = 14),
            axis.ticks.x = element_blank(),
            axis.ticks.y = element_line(colour = "black", linewidth = .5),
            axis.line = element_line(colour = "black", linewidth = 1),
            axis.title.y = element_text(angle = 90, size = 20),
            plot.title = element_text(size = 24, hjust = 0.5)
        ) +
        scale_x_discrete(limits = c("VR (No Avatar)", "VR (Avatar)", "Real-world"), expand = c(-.15, -.15)) +
        scale_y_continuous(limits = c(ymin, ymax)) +
        ylab(ylab) +
        xlab("Study") +
        ggtitle(stringr::str_remove(outcome_str, "Peak ")) +
        scale_fill_manual(
            guide = guide_legend(title = "Study"),
            values = c("VR (No Avatar)" = "#E69F00", "Real-world" = "#56B4E9", "VR (Avatar)" = "#009E73", "Cardinali et al. (2009)" = "#003566")
        )
}



create_kinematic_latency_plot <- function(df, outcome_str, xmin, xmax, xlab) {
    past_value <- fcase(
        outcome_str == "Velocity Latency", "vellatchange",
        outcome_str == "Acceleration Latency", "acclatchange",
        outcome_str == "Deceleration Latency", "declatchange",
        default = NA
    )

    past_df <- get(paste0(past_value, "df"), envir = parent.frame()) %>%
        as.data.frame()

    df %>%
        dplyr::filter(outcome == outcome_str) %>%
        ggplot(aes(y = study, x = change, fill = study)) +
        geom_blank() +
        geom_ribbon(
            data = past_df %>%
                dplyr::mutate(
                    xmin = change - get(paste0(past_value, "_ci")),
                    xmax = change + get(paste0(past_value, "_ci"))
                ),
            aes(xmin = xmin, xmax = xmax, y = study, fill = "Cardinali et al. (2009)"),
            alpha = 0.6
        ) +
        stat_eye() +
        geom_vline(
            xintercept = 0, 
            linetype = "dashed",
            linewidth = 1.5
            ) +
        geom_vline(
            xintercept = get(paste0(past_value)), 
            linetype = "solid",
            color = "#003566",
            linewidth = 2
        ) +

        theme_tidybayes() +
        theme(
            axis.text.x = element_text(angle = -90, color = "black", size = 14, vjust = .5, hjust = .5),
            axis.title.x = element_text(angle = 0, size = 20),
            axis.title.y = element_blank(),
            axis.text.y = element_blank(),
            axis.ticks.y = element_blank(),
            axis.ticks.x = element_line(colour = "black", linewidth = .5),
            plot.title = element_text(size = 24, hjust = 0.5)
        ) +
        scale_y_discrete(limits = c("Real-world", "VR (Avatar)", "VR (No Avatar)"), expand = c(-.25, -.25))+
        scale_x_continuous(limits = c(xmin, xmax), expand = c(0.1, 0.1)) +
        ylab("Study") +
        xlab(xlab) +
        ggtitle(stringr::str_remove(outcome_str, " Latency")) +
        scale_fill_manual(guide = guide_legend(title = "Study"),
            values = c("VR (No Avatar)" = "#E69F00", "Real-world" = "#56B4E9", "VR (Avatar)" = "#009E73", "Cardinali et al. (2009)" = "#003566"))
}




# All Studies
velocity_change_plot <- create_kinematic_peak_plot(kinematic_change, "Peak Velocity", -250, 250, " ")
acceleration_change_plot <- create_kinematic_peak_plot(kinematic_change, "Peak Acceleration", -2000, 2000, "Kinematic Peak Change (Post - Pre)")
deceleration_change_plot <- create_kinematic_peak_plot(kinematic_change, "Peak Deceleration", -2000, 2000, " ")
velocity_latency_change_plot <- create_kinematic_latency_plot(kinematic_change, "Velocity Latency", -100, 100, "Latency Change (Post - Pre)")
acceleration_latency_change_plot <- create_kinematic_latency_plot(kinematic_change, "Acceleration Latency", -100, 100, " ")
deceleration_latency_change_plot <- create_kinematic_latency_plot(kinematic_change, "Deceleration Latency", -100, 100, " ")



pw_theme <- theme(
    plot.background = element_rect(fill = "transparent", color = "transparent"),
    panel.background = element_rect(fill = "transparent", color = "transparent"),
    legend.background = element_rect(fill = "transparent", color = "transparent"),
    legend.key = element_rect(fill = "transparent", color = "transparent"),
    legend.text = element_text(color = "black", size = 16),
    legend.title = element_text(color = "black", size = 20),
    legend.position = "bottom",
    text = element_text(color = "black"),
    axis.line.x = element_line(colour = "black", linewidth = .5),
    axis.line.y = element_line(colour = "black", linewidth = .5),
)

peak_changes_plot <- acceleration_change_plot + velocity_change_plot + deceleration_change_plot + patchwork::plot_layout(guides = "collect") & pw_theme
latency_changes_plot <- acceleration_latency_change_plot + velocity_latency_change_plot + deceleration_latency_change_plot + 
patchwork::plot_layout(guides = "collect") & pw_theme

ggsave(
    peak_changes_plot,
    width = 12,
    height = 6,
    dpi = 200,
    bg = "transparent",
    filename = here::here("scripts", "for_osf", "cumulative_analyses", "figures", "kinematic_changes_all.svg")
)

ggsave(
    latency_changes_plot,
    width = 12,
    height = 6,
    dpi = 200,
    bg = "transparent",
    filename = here::here("scripts", "for_osf", "cumulative_analyses", "figures","kinematic_latency_changes_all.svg" )
)
```

```{r}
landmark_change <- bind_rows(
    fread(here::here("scripts", "for_osf", "tooluse_in_vr", "plot_data", "landmark_draws_change.csv")) %>% mutate(study = "VR (No Avatar)"),
    fread(here::here("scripts", "for_osf", "tooluse_in_real", "plot_data", "landmark_draws_change.csv")) %>% mutate(study = "Real-world"),
    fread(here::here("scripts", "for_osf", "tooluse_avatar", "plot_data", "landmark_draws_change.csv")) %>% mutate(study = "VR (Avatar)")
)

landmark_change <- landmark_change %>%
    mutate(
        target = factor(Target,
            levels = c("Elbow", "Forearm", "Wrist"),
            labels = c("Elbow", "Forearm", "Wrist")
        ),
        change = .epred,
        study = factor(study,
            levels = c("VR (No Avatar)", "VR (Avatar)", "Real-world"),
            labels = c("VR (No Avatar)", "VR (Avatar)", "Real-world")
        )
    )

create_landmark_error_plot <- function(df, target_str) {
    ylab = fifelse(
        target_str == "Elbow",
        "Change in Error (cm, Post - Pre)",
        " "
    )
    df %>%
        dplyr::filter(target == target_str) %>%
        ggplot(aes(x = study, y = change, fill = study)) +
        geom_blank() +
        stat_eye() +
        geom_hline(
            yintercept = 0,
            linetype = "dashed",
            linewidth = 1.5
        ) +
        theme_tidybayes() +
        theme(
            axis.text.x = element_blank(),
            axis.title.x = element_blank(),
            axis.text.y = element_text(angle = 0, hjust = 1, color = "black", size = 14),
            axis.ticks.x = element_blank(),
            axis.ticks.y = element_line(colour = "black", linewidth = .5),
            axis.line = element_line(colour = "black", linewidth = 1),
            axis.title.y = element_text(angle = 90, size = 20),
            plot.title = element_text(size = 24, hjust = 0.5)
        ) +
        scale_x_discrete(limits = c("VR (No Avatar)", "VR (Avatar)", "Real-world"), expand = c(-.15, -.15)) +
        scale_y_continuous(limits = c(-10, 10)) +
        ylab(ylab) +
        xlab("Study") +
        ggtitle(target_str) +
        scale_fill_manual(
            guide = guide_legend(title = "Study"),
            values = c("VR (No Avatar)" = "#E69F00", "Real-world" = "#56B4E9", "VR (Avatar)" = "#009E73", "Cardinali et al. (2009)" = "#003566")
        )
}

wrist_change_plot <- create_landmark_error_plot(landmark_change, "Wrist")
forearm_change_plot <- create_landmark_error_plot(landmark_change, "Forearm")
elbow_change_plot <- create_landmark_error_plot(landmark_change, "Elbow")

landmark_change_plot <- elbow_change_plot + forearm_change_plot + wrist_change_plot + patchwork::plot_layout(guides = "collect") & pw_theme

ggsave(
    landmark_change_plot,
    width = 12,
    height = 6,
    dpi = 200,
    bg = "transparent",
    filename = here::here("scripts", "for_osf", "cumulative_analyses", "figures", "landmark_changes_all.svg")
)
```


# Exploratory Analysis

## Follow-ups

### How many participants displayed the expected effects?
```{r}
ppt_m %>% group_by(ppid, time) %>% 
dplyr::summarise(m_vel = mean(vel_m_filt)) %>% 
as.data.table() %>% 
dcast(ppid~time) %>%
mutate(direction = fifelse(Pre > Post, 1, 0),) %>% 
dplyr::summarise(num_velocity_effect = sum(direction),
                 num_velocity_no_effect = sum(!direction),
                 percent_velocity_effect = num_velocity_effect / (num_velocity_effect + num_velocity_no_effect))

ppt_m %>% group_by(ppid, time) %>% 
dplyr::summarise(m_acc = mean(acc_m_filtfilt, na.rm = TRUE)) %>% 
as.data.table() %>% 
dcast(ppid~time) %>% 
mutate(direction = fifelse(Pre > Post, 1, 0)) %>% 
dplyr::summarise(num_accel_effect = sum(direction, na.rm = TRUE))

ppt_m %>% group_by(ppid, time) %>% 
dplyr::summarise(m_dec = mean(dec_m_filtfilt)) %>% 
as.data.table() %>% 
dcast(ppid~time) %>% 
mutate(direction = fifelse(Pre < Post, 1, 0)) %>% 
dplyr::summarise(num_decel_effect = sum(direction))

landmark %>% group_by(ppid, time, target) %>% 
dplyr::summarise(error = mean(error_std)) %>% 
as.data.table() %>% 
dcast(ppid+target~time)%>% 
mutate(direction = fifelse(Pre < Post, "Further", "Closer")) %>%
group_by(target) %>%
dplyr::summarise(num_further = sum(direction == "Further"))
```

### Does order influence the number of participants who show the tool-use effect?

#### Kinematics
```{r}
order_test_vel <- ppt_m %>%
    group_by(ppid, order) %>%
    dplyr::summarise(m_vel = mean(vel_m_filt)) %>%
    as.data.table() %>%
    dcast(ppid ~ order)

order_test_acc <- ppt_m %>%
    group_by(ppid, order) %>%
    dplyr::summarise(m_acc = mean(acc_m_filtfilt)) %>%
    as.data.table() %>%
    dcast(ppid ~ order)

order_test_dec <- ppt_m %>%
    group_by(ppid, order) %>%
    dplyr::summarise(m_dec = mean(dec_m_filtfilt)) %>%
    as.data.table() %>%
    dcast(ppid ~ order)

bind_rows(
order_test_vel %>%
    dplyr::filter(!is.na(First)) %>%
    mutate(direction = fifelse(Pre > First, 1, 0)) %>%
    dplyr::summarise(
        Outcome = "Velocity",
        order = "First",
        prop_effect = sum(direction) / n(),
        n_effect = sum(direction)
    ),
order_test_vel %>%
    dplyr::filter(!is.na(Second)) %>%
    mutate(direction = fifelse(Pre > Second, 1, 0)) %>%
    dplyr::summarise(
        Outcome = "Velocity",
        order = "Second",
        prop_effect = sum(direction) / n(),
        n_effect = sum(direction)
    ),
order_test_acc %>%
    dplyr::filter(!is.na(First)) %>%
    mutate(direction = fifelse(Pre > First, 1, 0)) %>%
    dplyr::summarise(
        Outcome = "Acceleration",
        order = "First",
        prop_effect = sum(direction) / n(),
        n_effect = sum(direction)
    ),
order_test_acc %>%
    dplyr::filter(!is.na(Second)) %>%
    mutate(direction = fifelse(Pre > Second, 1, 0)) %>%
    dplyr::summarise(
        Outcome = "Acceleration",
        order = "Second",
        prop_effect = sum(direction) / n(),
        n_effect = sum(direction)
    ),
order_test_dec %>%
    dplyr::filter(!is.na(First)) %>%
    mutate(direction = fifelse(Pre < First, 1, 0)) %>%
    dplyr::summarise(
        Outcome = "Deceleration",
        order = "First",
        prop_effect = sum(direction) / n(),
        n_effect = sum(direction)
    ),
order_test_dec %>%
    dplyr::filter(!is.na(Second)) %>%
    mutate(direction = fifelse(Pre < Second, 1, 0)) %>%
    dplyr::summarise(
        Outcome = "Deceleration",
        order = "Second",
        prop_effect = sum(direction) / n(),
        n_effect = sum(direction)
    ),
)
```

#### Landmark Biases
```{r}
order_test_lm <- landmark %>% group_by(ppid, order, target) %>% 
dplyr::summarise(error = mean(error_std)) %>% 
as.data.table() %>% 
dcast(ppid+target~order)

order_test_lm %>%
dplyr::filter(!is.na(First)) %>%
mutate(direction = fifelse(Pre < First, "Further", "Closer")) %>%
group_by(target) %>%
dplyr::summarise(prop_further = sum(direction == "Further")/n())

order_test_lm %>%
dplyr::filter(!is.na(Second)) %>%
mutate(direction = fifelse(Pre < Second, "Further", "Closer")) %>%
group_by(target) %>%
dplyr::summarise(prop_further = sum(direction == "Further")/n())
```




## Bell & Macuga (2022) Criticism Follow-ups

The following analyses were not preregistered, but were outlined in @bell2022.

### Does Forearm Length influence baseline kinematic measures?


```{r}
t <- ppt_forearmlength[time == "Pre"][,
  `:=`(forearmlength_std = (forearmlength - mean(forearmlength, na.rm = TRUE)) / sd(forearmlength, na.rm = TRUE),
    vel_m_filt_std = (vel_m_filt - mean(vel_m_filt, na.rm = TRUE)) / sd(vel_m_filt, na.rm = TRUE),
    acc_m_filtfilt_std = (acc_m_filtfilt - mean(acc_m_filtfilt, na.rm = TRUE)) / sd(acc_m_filtfilt, na.rm = TRUE),
    dec_m_filtfilt_std = (dec_m_filtfilt - mean(dec_m_filtfilt, na.rm = TRUE)) / sd(dec_m_filtfilt, na.rm = TRUE),
    vel_lat_filt_std = (vel_lat_filt - mean(vel_lat_filt, na.rm = TRUE)) / sd(vel_lat_filt, na.rm = TRUE),
    acc_lat_filtfilt_std = (acc_lat_filtfilt - mean(acc_lat_filtfilt, na.rm = TRUE)) / sd(acc_lat_filtfilt, na.rm = TRUE),
    dec_lat_filtfilt_std = (dec_lat_filtfilt - mean(dec_lat_filtfilt, na.rm = TRUE)) / sd(dec_lat_filtfilt, na.rm = TRUE),
    ppid = factor(ppid),
    trial_num_in_block = trial_num_in_block),
    by = "study"] %>%
    dplyr::filter(time == "Pre") %>%
    dplyr::select(
        ppid,
        study,
        forearmlength,
        vel_m_filt,
        acc_m_filtfilt,
        dec_m_filtfilt,
        vel_lat_filt,
        acc_lat_filtfilt,
        dec_lat_filtfilt,
        forearmlength_std,
        vel_m_filt_std,
        acc_m_filtfilt_std,
        dec_m_filtfilt_std,
        vel_lat_filt_std,
        acc_lat_filtfilt_std,
        dec_lat_filtfilt_std
    ) %>%
    bind_rows(
        martel_2019_forearm %>%
        dplyr::select(
            ppid,
            study,
            forearmlength,
            vel_m_filt,
            acc_m_filtfilt,
            dec_m_filtfilt,
            vel_lat_filt,
            acc_lat_filtfilt,
            dec_lat_filtfilt,
            forearmlength_std,
            vel_m_filt_std,
            acc_m_filtfilt_std,
            dec_m_filtfilt_std,
            vel_lat_filt_std,
            acc_lat_filtfilt_std,
            dec_lat_filtfilt_std
        ), 
        martel_21 %>%
        dplyr::select(
            ppid,
            study,
            forearmlength,
            vel_m_filt,
            acc_m_filtfilt,
            dec_m_filtfilt,
            vel_lat_filt,
            acc_lat_filtfilt,
            dec_lat_filtfilt,
            forearmlength_std,
            vel_m_filt_std,
            acc_m_filtfilt_std,
            dec_m_filtfilt_std,
            vel_lat_filt_std,
            acc_lat_filtfilt_std,
            dec_lat_filtfilt_std
        )
    )

vel <- t %>% group_by(ppid, study) %>%
dplyr::summarise(forearmlength_std = mean(forearmlength_std, na.rm = TRUE),
          vel_m_filt_std = mean(vel_m_filt_std, na.rm = TRUE)) %>%  
ggplot(aes(x = forearmlength_std, y = vel_m_filt_std)) +
geom_point(aes(color = study)) +
geom_smooth(method = "lm", se = FALSE, color = "black") +
geom_smooth(method = "lm", se = FALSE, aes(color = study), linewidth = 1, linetype = "dashed") +
labs(x = "Forearm Length (Standardized)", y = "Velocity (Standardized)")

acc <- t %>% group_by(ppid, study) %>%
dplyr::summarise(forearmlength_std =mean(forearmlength_std, na.rm = TRUE),
          acc_m_filtfilt_std = mean(acc_m_filtfilt_std, na.rm = TRUE)) %>%  
ggplot(aes(x = forearmlength_std, y = acc_m_filtfilt_std)) +
geom_point(aes(color = study)) +
geom_smooth(method = "lm", se = FALSE, color = "black") +
geom_smooth(method = "lm", se = FALSE, aes(color = study), linewidth = 1, linetype = "dashed") +
labs(x = " ", y = "Acceleration (Standardized)")

dec <- t %>% group_by(ppid, study) %>%
dplyr::summarise(forearmlength_std =mean(forearmlength_std, na.rm = TRUE),
          dec_m_filtfilt_std = mean(dec_m_filtfilt_std, na.rm = TRUE)) %>%  
ggplot(aes(x = forearmlength_std, y = dec_m_filtfilt_std)) +
geom_point(aes(color = study)) +
geom_smooth(method = "lm", se = FALSE, color = "black") +
geom_smooth(method = "lm", se = FALSE, aes(color = study), linewidth = 1, linetype = "dashed") +
labs(x = " ", y = "Deceleration (Standardized)")

vel_lat <- t %>% group_by(ppid, study) %>%
dplyr::summarise(forearmlength_std =mean(forearmlength_std, na.rm = TRUE),
          vel_lat_filt_std = mean(vel_lat_filt_std, na.rm = TRUE)) %>%  
ggplot(aes(x = forearmlength_std, y = vel_lat_filt_std)) +
geom_point(aes(color = study)) +
geom_smooth(method = "lm", se = FALSE, color = "black") +
geom_smooth(method = "lm", se = FALSE, aes(color = study), linewidth = 1, linetype = "dashed") +
labs(x = "Forearm Length (Standardized)", y = "Velocity Latency (Standardized)")

acc_lat <- t %>% group_by(ppid, study) %>%
dplyr::summarise(forearmlength_std =mean(forearmlength_std, na.rm = TRUE),
          acc_lat_filtfilt_std = mean(acc_lat_filtfilt_std, na.rm = TRUE)) %>%  
ggplot(aes(x = forearmlength_std, y = acc_lat_filtfilt_std)) +
geom_point(aes(color = study)) +
geom_smooth(method = "lm", se = FALSE, color = "black") +
geom_smooth(method = "lm", se = FALSE, aes(color = study), linewidth = 1, linetype = "dashed") +
labs(x = " ", y = "Acceleration Latency (Standardized)")

dec_lat <- t %>% group_by(ppid, study) %>%
dplyr::summarise(forearmlength_std =mean(forearmlength_std, na.rm = TRUE),
          dec_lat_filtfilt_std = mean(dec_lat_filtfilt_std, na.rm = TRUE)) %>%  
ggplot(aes(x = forearmlength_std, y = dec_lat_filtfilt_std)) +
geom_point(aes(color = study)) +
geom_smooth(method = "lm", se = FALSE, color = "black") +
geom_smooth(method = "lm", se = FALSE, aes(color = study), linewidth = 1, linetype = "dashed") +
labs(x = " ", y = "Deceleration Latency (Standardized)")

pw_theme <- theme(
    legend.position = "bottom",
    text = element_text(size = 16),
    plot.background = element_rect(fill = "transparent", color = NA),
    panel.background = element_rect(fill = "transparent", color = NA),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA)
)

forearmlength_plots <- (acc + vel + dec) / (acc_lat + vel_lat + dec_lat) + 
patchwork::plot_layout(guides = "collect") & 
labs(color = "Study") &
theme_tidybayes() & pw_theme

ggsave(here::here("scripts", "for_osf", "cumulative_analyses", "figures", "forearm_plots.svg"), forearmlength_plots, width = 10, height = 10, units = "in", dpi = 300, bg = "transparent")
saveRDS(forearmlength_plots, here::here("scripts", "for_osf", "cumulative_analyses", "figures", "forearm_velocity.rds"))

cor <- t %>%
mutate(ppid = factor(ppid),
         study = factor(study)) %>%
dplyr::select(
    vel_m_filt_std,
    acc_m_filtfilt_std,
    dec_m_filtfilt_std,
    vel_lat_filt_std,
    acc_lat_filtfilt_std,
    dec_lat_filtfilt_std,
    forearmlength_std,
    study
) %>% correlation::correlation(
  method = "auto",
  bayesian = TRUE,
  bayesian_prior = "wide",
  multilevel = TRUE,
  include_factors = TRUE,
  partial = TRUE
)
```

### How do kinematic values change by trial?
i.e., is there a transient effect of the tool-use task?

```{r}
ppt_combined <- ppt_forearm_surveys %>% 
  mutate(overall_trial = fcase(time == "Pre", trial_num_in_block,
                               time == "Post", trial_num_in_block + 18),
          study = fcase(ppid %like% "d1-0", "VR (No Avatar)",
                        ppid %like% "d2-0", "Real-world",
                        ppid %like% "d3-0", "VR (Avatar)",
                        default = NA))

ppt_combined %>%
  dplyr::filter(vel_m_filt < 2000, !(time == "tool-use" & vel_m_filt > 1500), !vel_m_filt < 100) %>%
  ggplot(aes(x = overall_trial, y = vel_m_filt,  color = time)) +
  geom_point(size = 2, alpha = .5) +
  geom_smooth(aes(color = time), size = 2, alpha = .5, method = "lm") +
  theme_tidybayes() +
  theme(text = element_text(size = 26)) +
  scale_y_continuous(limits = c(0, 2000)) 

by_trial_velocity <- ppt_combined %>%
  dplyr::filter(vel_m_filt < 2000,
              !(time == "tool-use" & vel_m_filt > 1500)) %>%
  group_by(overall_trial, time, study) %>%
  dplyr::summarise(m_vel = mean(vel_m_filt),
            m_acc = mean(acc_m_filtfilt),
            m_dec = mean(dec_m_filtfilt)) %>%
  ggplot(aes(x = overall_trial, y = m_vel, group = interaction(study, time), color = study, linetype = study)) +
    geom_line(linewidth = 1) +
    geom_point(size = 3) +
    geom_vline(xintercept = 18.5, linetype = "dashed") +
    scale_color_manual(values = c("VR (No Avatar)" = "#E69F00", "Real-world" = "#56B4E9", "VR (Avatar)" = "#009E73")) +
    labs(x = "Trial", y = "Peak Velocity (mm/s)", color = "Study", linetype = "Study") +
    theme_tidybayes()+
    theme(text = element_text(size = 22),
        plot.background = element_rect(fill = "transparent", color = NA),
        panel.background = element_rect(fill = "transparent", color = NA),
        legend.background = element_rect(fill = "transparent", color = NA),
        legend.position = "bottom",
        legend.key = element_rect(fill = "transparent", color = NA))

saveRDS(by_trial_velocity, here::here("scripts", "for_osf", "cumulative_analyses", "figures", "by_trial_velocity.rds"))
ggsave(
    here::here("scripts", "for_osf", "cumulative_analyses", "figures", "by_trial_velocity.svg"), 
    by_trial_velocity + labs(title = "Peak Velocity By Trial"), 
    width = 10, 
    height = 8, 
    units = "in", 
    dpi = 300, 
    bg = "transparent")
```

### Is this influenced by order?
```{r}
order_test_vel <- ppt_m %>% group_by(ppid, trial_num_in_block, order, time, study) %>% 
dplyr::summarise(
    m_vel = mean(vel_m_filt)
    ) %>% 
dplyr::mutate(
    overall_trial = fcase(time == "Pre", trial_num_in_block,
                          time == "Post", trial_num_in_block + 18),
    study = fcase(ppid %like% "d1-0", "VR (No Avatar)",
        ppid %like% "d2-0", "Real-world",
        ppid %like% "d3-0", "VR (Avatar)",
        default = NA
    )
) %>%
as.data.table() %>% 
dcast(ppid+study+trial_num_in_block~order, value.var = "m_vel", fun.aggregate = mean) 

first_participants <- order_test_vel %>%
dplyr::filter(!is.na(First), !is.nan(First)) %>%
group_by(trial_num_in_block, study) %>%
dplyr::summarise(
    m_vel_pre = mean(Pre, na.rm = TRUE),
    m_vel_post = mean(First, na.rm = TRUE)
    )

second_participants <- order_test_vel %>%
    dplyr::filter(!is.na(Second), !is.nan(Second)) %>%
    group_by(trial_num_in_block, study) %>%
    dplyr::summarise(
        m_vel_pre = mean(Pre, na.rm = TRUE),
        m_vel_post = mean(Second, na.rm = TRUE)
    )

order_test_vel %>%
group_by(trial_num_in_block, study) %>% 
dplyr::summarise(m_vel_pre = mean(Pre, na.rm = TRUE), m_vel_first = mean(First, na.rm = TRUE), m_vel_second = mean(Second, na.rm = TRUE)) %>%

ggplot(
    aes(x = trial_num_in_block, color = study, group = study)
    ) +
  geom_line(
    data = first_participants,
    aes(y = m_vel_pre), 
    linetype = "dashed",
    size = 1
    ) +
  geom_line(
    data = first_participants,
    aes(y = m_vel_post, x = trial_num_in_block + 18), 
    linetype = "dashed",
    size = 1
    ) +
    geom_line(
    data = second_participants,
    aes(y = m_vel_pre),
    size = 1
    ) +
    geom_line(
    data = second_participants,
    aes(y = m_vel_post, x = trial_num_in_block + 18),
    size = 1
    )+
    labs(x = "Trial", y = "Peak Velocity (mm/s)", color = "Study", linetype = "Order", title = "Velocity Over Trials By Order And Study") +
    theme_tidybayes()+
    scale_linetype_manual(values = c("dashed", "solid"), labels = c("First", "Second"))+
    theme(text = element_text(size = 22),
        plot.background = element_rect(fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        legend.background = element_rect(fill = "transparent"),
        legend.position = "bottom",
        legend.key = element_rect(fill = "transparent"))
```
Dashed lines are participants who completed the reaching task first, solid lines are participants who completed the reaching task second.

All participants, regardless of order, seemed to show an initial drop in kinematics that quickly recovered.

## Post-experiment Survey Exploratory Analyses

```{r}
ppt_standardized <- ppt_forearm_surveys %>%
    group_by(study) %>%
    dplyr::mutate(
      std_vel = (vel_m_filt - mean(vel_m_filt, na.rm = TRUE)) / sd(vel_m_filt, na.rm = TRUE),
        std_acc = (acc_m_filtfilt - mean(acc_m_filtfilt, na.rm = TRUE)) / sd(acc_m_filtfilt, na.rm = TRUE),
        std_dec = (dec_m_filtfilt - mean(dec_m_filtfilt, na.rm = TRUE)) / sd(dec_m_filtfilt, na.rm = TRUE),
        std_vel_lat = (vel_lat_filt - mean(vel_lat_filt, na.rm = TRUE)) / sd(vel_lat_filt, na.rm = TRUE),
        std_acc_lat = (acc_lat_filtfilt - mean(acc_lat_filtfilt, na.rm = TRUE)) / sd(acc_lat_filtfilt, na.rm = TRUE),
        std_dec_lat = (dec_lat_filtfilt - mean(dec_lat_filtfilt, na.rm = TRUE)) / sd(dec_lat_filtfilt, na.rm = TRUE)
    ) %>% ungroup()

change <- ppt_standardized %>%
    pivot_wider(
        id_cols = c(ppid, trial_num_in_block, study, fatigue),
        names_from = time,
        values_from = c(
            std_vel,
            std_acc,
            std_dec,
            std_vel_lat,
            std_acc_lat,
            std_dec_lat
        ),
        values_fn = list(
            std_vel = ~mean(.x, na.rm = TRUE),
            std_acc = ~mean(.x, na.rm = TRUE),
            std_dec = ~mean(.x, na.rm = TRUE),
            std_vel_lat = ~mean(.x, na.rm = TRUE),
            std_acc_lat = ~mean(.x, na.rm = TRUE),
            std_dec_lat = ~mean(.x, na.rm = TRUE)
        )
    ) 

change_by_study <- change %>%
    dplyr::group_by(ppid, study) %>%
    dplyr::summarise(
        std_vel_change = round(
            mean(std_vel_Post) - mean(std_vel_Pre),
            4
        ),
        std_acc_change = round(
            mean(std_acc_Post) - mean(std_acc_Pre),
            4
        ),
        std_dec_change = round(
            mean(std_dec_Post) - mean(std_dec_Pre),
            4
        ),
        std_vel_lat_change = round(
            mean(std_vel_lat_Post) - mean(std_vel_lat_Pre),
            4
        ),
        std_acc_lat_change = round(
            mean(std_acc_lat_Post) - mean(std_acc_lat_Pre),
            4
        ),
        std_dec_lat_change = round(
            mean(std_dec_lat_Post) - mean(std_dec_lat_Pre),
            4
        )
    ) %>%
    as.data.table()

change_by_study_and_fatigue <- ppt_standardized %>%
    # dplyr::filter(
    #     (time == "Pre" & trial_num_in_block > 12) |
    #     (time == "Post" & trial_num_in_block < 7)
    #     ) %>%
    pivot_wider(
        id_cols = c(ppid, study, fatigue, performance_hypothesis),
        names_from = time,
        values_from = c(
            std_vel,
            std_acc,
            std_dec,
            std_vel_lat,
            std_acc_lat,
            std_dec_lat
        ),
        values_fn = list(
            std_vel = ~mean(.x, na.rm = TRUE),
            std_acc = ~mean(.x, na.rm = TRUE),
            std_dec = ~mean(.x, na.rm = TRUE),
            std_vel_lat = ~mean(.x, na.rm = TRUE),
            std_acc_lat = ~mean(.x, na.rm = TRUE),
            std_dec_lat = ~mean(.x, na.rm = TRUE)
        )
    )  %>%
    dplyr::mutate(
        fatigue = fifelse(fatigue == 1, "Yes", "No"),
        performance_hypothesis = fifelse(performance_hypothesis == 1, "Yes", "No"),
        std_vel_change = std_vel_Post - std_vel_Pre,
        std_acc_change = std_acc_Post - std_acc_Pre,
        std_dec_change = std_dec_Post - std_dec_Pre,
        std_vel_lat_change = std_vel_lat_Post - std_vel_lat_Pre,
        std_acc_lat_change = std_acc_lat_Post - std_acc_lat_Pre,
        std_dec_lat_change = std_dec_lat_Post - std_dec_lat_Pre
    ) %>%
    as.data.table()
```

## Did the results for fatigued participants differ?

Fatigue denoted by a free response item in the post-test, "What was the most difficult part of the experiment?". If the answer noted that the participant felt fatigued, sore, etc. from tool-use, they were coded as fatigued.

### Full block
```{r plotted-change}
change_by_study_and_fatigue %>%
    ggplot(
      aes
      (x = std_vel_change,
      fill = fatigue, 
      color = fatigue)) +
    stat_dotsinterval(
        dotsize = 1,
        alpha = .5,
       position = position_dodge(width = .6),
        point_interval = mean_qi
    ) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
    scale_fill_manual(
        breaks = c("Yes", "No"),
        values = c("firebrick", "steelblue")
    ) +
    scale_color_manual(
        breaks = c("Yes", "No"),
        values = c("firebrick", "steelblue")
    ) +
    scale_y_discrete(
        breaks = c("VR (No Avatar)", "VR (Avatar)", "Real-world"),
    ) +
    theme_tidybayes() +
    theme(text = element_text(size = 26)) +
    labs(
        title = "Change in Kinematics by Self-reported Fatigue", 
        x = "Velocity Change (Standardized)", 
        y = "Study")

```

### 6 Trials before and after tool-use

```{r}
change_fatigue_six_trials <- ppt_standardized %>%
    dplyr::filter(
        (time == "Pre" & trial_num_in_block > 12) |
        (time == "Post" & trial_num_in_block < 7)
        ) %>%
    pivot_wider(
        id_cols = c(ppid, study, fatigue, performance_hypothesis),
        names_from = time,
        values_from = c(
            std_vel,
            std_acc,
            std_dec,
            std_vel_lat,
            std_acc_lat,
            std_dec_lat
        ),
        values_fn = list(
            std_vel = ~ mean(.x, na.rm = TRUE),
            std_acc = ~ mean(.x, na.rm = TRUE),
            std_dec = ~ mean(.x, na.rm = TRUE),
            std_vel_lat = ~ mean(.x, na.rm = TRUE),
            std_acc_lat = ~ mean(.x, na.rm = TRUE),
            std_dec_lat = ~ mean(.x, na.rm = TRUE)
        )
    ) %>%
    dplyr::mutate(
        fatigue = fifelse(fatigue == 1, "Yes", "No"),
        performance_hypothesis = fifelse(performance_hypothesis == 1, "Yes", "No"),
        std_vel_change = std_vel_Post - std_vel_Pre,
        std_acc_change = std_acc_Post - std_acc_Pre,
        std_dec_change = std_dec_Post - std_dec_Pre,
        std_vel_lat_change = std_vel_lat_Post - std_vel_lat_Pre,
        std_acc_lat_change = std_acc_lat_Post - std_acc_lat_Pre,
        std_dec_lat_change = std_dec_lat_Post - std_dec_lat_Pre
    ) %>%
    as.data.table()

change_fatigue_six_trials %>%
    ggplot(
        aes
        (
            x = std_vel_change,
            fill = fatigue,
            color = fatigue
        )
    ) +
    stat_dotsinterval(
        dotsize = 1,
        alpha = .5,
        position = position_dodge(width = .6),
        point_interval = mean_qi
    ) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
    scale_fill_manual(
        breaks = c("Yes", "No"),
        values = c("firebrick", "steelblue")
    ) +
    scale_color_manual(
        breaks = c("Yes", "No"),
        values = c("firebrick", "steelblue")
    ) +
    scale_y_discrete(
        breaks = c("VR (No Avatar)", "VR (Avatar)", "Real-world"),
    ) +
    theme_tidybayes() +
    theme(text = element_text(size = 26)) +
    labs(
        title = "Change in Kinematics by Self-reported Fatigue",
        x = "Velocity Change (Standardized)",
        y = "Study"
    )

by_trial_velocity_fatigue <- ppt_forearm_surveys %>%
    dplyr::filter(
        (time == "Pre" & trial_num_in_block > 12) |
        (time == "Post" & trial_num_in_block < 7)
    ) %>%
    mutate(
        fatigue = fifelse(fatigue == 1, "Yes", "No"),
        overall_trial = ifelse(time == "Pre", trial_num_in_block, trial_num_in_block + 18)
    ) %>%
    group_by(overall_trial, time, study, fatigue) %>%
    dplyr::summarise(
        m_vel = mean(vel_m_filt),
        m_acc = mean(acc_m_filtfilt),
        m_dec = mean(dec_m_filtfilt)
    ) %>%
    ggplot(aes(x = overall_trial, y = m_vel, group = interaction(study, time, fatigue), color = study, linetype = fatigue)) +
    geom_line(linewidth = 1) +
    geom_point(size = 3) +
    geom_vline(xintercept = 18.5, linetype = "dashed") +
    scale_color_manual(values = c("VR (No Avatar)" = "#E69F00", "Real-world" = "#56B4E9", "VR (Avatar)" = "#009E73")) +
    scale_x_continuous(breaks = c(13:24)) +
    labs(x = "Trial", y = "Peak Velocity (mm/s)", color = "Study", linetype = "Fatigue") +
    theme_tidybayes() +
    theme(
        text = element_text(size = 22),
        plot.background = element_rect(fill = "transparent", color = NA),
        panel.background = element_rect(fill = "transparent", color = NA),
        legend.background = element_rect(fill = "transparent", color = NA),
        legend.position = "bottom",
        legend.key = element_rect(fill = "transparent", color = NA)
    )

ggsave(
    here::here("scripts", "for_osf", "cumulative_analyses", "figures", "by_trial_velocity_fatigue.svg"), 
    by_trial_velocity_fatigue + labs(title = "Peak Velocity By Trial and Fatigue Report"), 
    width = 10, 
    height = 8, 
    units = "in", 
    dpi = 300, 
    bg = "transparent")

```


## Did the hypothesis guess matter?

```{r}
change_by_study_and_fatigue %>%
    ggplot(
        aes
        (
            x = std_vel_change,
            fill = performance_hypothesis,
            color = performance_hypothesis
        )
    ) +
    stat_dotsinterval(
        dotsize = 1,
        alpha = .5,
        position = position_dodge(width = .6),
        point_interval = mean_qi
    ) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
    scale_fill_manual(
        breaks = c("Yes", "No"),
        values = c("firebrick", "steelblue")
    ) +
    scale_color_manual(
        breaks = c("Yes", "No"),
        values = c("firebrick", "steelblue")
    ) +
    scale_y_discrete(
        breaks = c("VR (No Avatar)", "VR (Avatar)", "Real-world"),
    ) +
    theme_tidybayes() +
    theme(text = element_text(size = 26)) +
    labs(
        title = "Change in Kinematics by Performance Hypothesis",
        x = "Velocity Change (Standardized)",
        y = "Study"
    )

```

Probably too few who guessed otherwise to tell.

# Comparisons with Past Work

```{r previous-data}
# Cardinali et al. (2009) simulated
# Empirical values, taken (estimated) from Cardinali et al. (2009) figure 1C, corresponding to experiment 2.

# Error bars were 10px (in total), each side corresponding to 26.66 based on the y axis.
se <- 26.66

sample <- 18
sd <- se * sqrt(sample)
cor <- .9055
cov <- matrix(c(
    sd^2, cor * (sd^2),
    cor * (sd^2), sd^2
), nrow = 2)

simdata <- MASS::mvrnorm(sample, mu = c(mupre, mupost), cov, empirical = TRUE) %>%
    as.data.frame() %>%
    pivot_longer(cols = c(V1, V2), names_to = "time", values_to = "velocity") %>%
    mutate(
      std_vel = (velocity - mean(velocity)) / sd(velocity),
      time = factor(time, levels = c("V1", "V2"), labels = c("Pre", "Post")),
      ppid = as.character(rep(1:sample, each = 2))
      ) %>%
    pivot_wider(id_cols = ppid, names_from = time, values_from = std_vel) %>%
    mutate(
      std_vel_pre = Pre,
      std_vel_post = Post,
      std_vel_change = (Post - Pre),
      study = "Cardinali et al. (2009, Simulated)"
    ) 

# Martel et al. (2019) empirical data
martel_2019_wide <- read_csv(here::here("data", "priors", "Martel2019.csv"), col_types = "fddddddddddddddddddfdd")
martel_2019_long <- fread(here::here("data", "priors", "martel_manova_long.csv"))
    
martel_2019_long[,
    `:=`(
        vel_m_filt_std = (VEL - mean(VEL, na.rm = TRUE)) / sd(VEL, na.rm = TRUE),
        acc_m_filtfilt_std = (ACC - mean(ACC, na.rm = TRUE)) / sd(ACC, na.rm = TRUE),
        dec_m_filtfilt_std = (DEC - mean(DEC, na.rm = TRUE)) / sd(DEC, na.rm = TRUE),
        vel_lat_filt_std = (TPVEL - mean(TPVEL, na.rm = TRUE)) / sd(TPVEL, na.rm = TRUE),
        acc_lat_filtfilt_std = (TPACC - mean(TPACC, na.rm = TRUE)) / sd(TPACC, na.rm = TRUE),
        dec_lat_filtfilt_std = (TPDEC - mean(TPDEC, na.rm = TRUE)) / sd(TPDEC, na.rm = TRUE)
    ),
    by = c("GROUP")
][,
time := factor(Time, levels = c("PRE", "POST"), labels = c("Pre", "Post"))
]

martel_2019 <- martel_2019_wide %>%
    pivot_longer(cols = c(VELPRE, VELPOST), names_to = "time", values_to = "velocity") %>%
    mutate(
      std_vel = (velocity - mean(velocity)) / sd(velocity),
      time = factor(time, levels = c("VELPRE", "VELPOST"), labels = c("Pre", "Post")),
      ppid = SUBJECTS
    ) %>%
    pivot_wider(id_cols = c(ppid, FOREARMLENGTH), names_from = time, values_from = std_vel, values_fn = ~mean(.x)) %>%
    mutate(
        std_vel_pre = Pre,
        std_vel_post = Post,
        std_vel_change = (Post - Pre),
        study = "Martel et al. (2019)"
    ) 

martel_2019_forearm <- martel_2019_wide %>%
    group_by(GROUP) %>%
    dplyr::mutate(
        ppid = SUBJECTS,
        vel_m_filt = VELPRE,
        acc_m_filtfilt = ACCPRE,
        dec_m_filtfilt = DECPRE,
        vel_lat_filt = TPVELPRE,
        acc_lat_filtfilt = TPACCPRE,
        dec_lat_filtfilt = TPDECPRE,
        vel_m_filt_std = (vel_m_filt - mean(vel_m_filt, na.rm = TRUE))/sd(vel_m_filt, na.rm = TRUE),
        acc_m_filtfilt_std = (acc_m_filtfilt - mean(acc_m_filtfilt, na.rm = TRUE))/sd(acc_m_filtfilt, na.rm = TRUE),
        dec_m_filtfilt_std = (dec_m_filtfilt - mean(dec_m_filtfilt, na.rm = TRUE))/sd(dec_m_filtfilt, na.rm = TRUE),
        vel_lat_filt_std = (vel_lat_filt - mean(vel_lat_filt, na.rm = TRUE))/sd(vel_lat_filt, na.rm = TRUE),
        acc_lat_filtfilt_std = (acc_lat_filtfilt - mean(acc_lat_filtfilt, na.rm = TRUE))/sd(acc_lat_filtfilt, na.rm = TRUE),
        dec_lat_filtfilt_std = (dec_lat_filtfilt - mean(dec_lat_filtfilt, na.rm = TRUE))/sd(dec_lat_filtfilt, na.rm = TRUE),
        forearmlength = FOREARMLENGTH/10,
        forearmlength_std = (forearmlength - mean(forearmlength, na.rm = TRUE))/sd(forearmlength, na.rm = TRUE),
        study = fifelse(GROUP == 1, "Martel et al. (2019) Ahead", "Martel et al. (2019) Across")
    ) %>% 
    as.data.table()

# Martel et al. (2021) empirical data, 
martel_2021_18plus <- read_csv(here::here("data", "priors", "martel2021_18up_processed.csv")) %>%
mutate(
  std_vel = (VEL - mean(VEL, na.rm = TRUE)) / sd(VEL, na.rm = TRUE),
) %>% dplyr::select(
    subjects, 
    ForearmLength, 
    trials_reaching, 
    std_vel, 
    session,
    VEL,
    ACC,
    DEC,
    TPACC,
    TPDEC,
    TPVEL
    ) %>%
    filter(session != "TOOL") %>%
    mutate(
        vel_m_filt_std = (VEL - mean(VEL, na.rm = TRUE)) / sd(VEL, na.rm = TRUE),
        acc_m_filtfilt_std = (ACC - mean(ACC, na.rm = TRUE)) / sd(ACC, na.rm = TRUE),
        dec_m_filtfilt_std = (DEC - mean(DEC, na.rm = TRUE)) / sd(DEC, na.rm = TRUE),
        vel_lat_filt_std = (TPVEL - mean(TPVEL, na.rm = TRUE)) / sd(TPVEL, na.rm = TRUE),
        acc_lat_filtfilt_std = (TPACC - mean(TPACC, na.rm = TRUE)) / sd(TPACC, na.rm = TRUE),
        dec_lat_filtfilt_std = (TPDEC - mean(TPDEC, na.rm = TRUE)) / sd(TPDEC, na.rm = TRUE),
        study = "Martel et al. (2021) 18+",
        time = fifelse(session == "PRE", "Pre", "Post")
    )


martel_21 <- inner_join(
    martel_2021_18plus %>% filter(session %in% c("PRE")),
    martel_2021_18plus %>% filter(session %in% c("POST")),
    by = c("subjects", "trials_reaching", "ForearmLength"), suffix = c("PRE", "POST")
)

# Join again with tool-use Velocity as a third VEL column.

# Collapse across trials, computing averages.

martel_21 <- martel_21 %>%
    group_by(subjects, trials_reaching) %>%
    dplyr::summarise(
        trial_num_in_block = mean(trials_reaching),
        vel_m_filt = mean(VELPRE),
        acc_m_filtfilt = mean(ACCPRE),
        dec_m_filtfilt = mean(DECPRE),
        vel_lat_filt = mean(TPVELPRE),
        acc_lat_filtfilt = mean(TPACCPRE),
        dec_lat_filtfilt = mean(TPDECPRE),
        std_vel_pre = mean(std_velPRE, na.rm = TRUE),
        std_vel_post = mean(std_velPOST, na.rm = TRUE),
        std_vel_change = std_vel_post - std_vel_pre,
        forearmlength = mean(ForearmLength/10),
        study = "Martel et al. (2021)"
    ) %>%
    ungroup() %>%
    mutate(
      ppid = subjects,
        vel_m_filt_std = (vel_m_filt - mean(vel_m_filt)) / sd(vel_m_filt),
        acc_m_filtfilt_std = (acc_m_filtfilt - mean(acc_m_filtfilt)) / sd(acc_m_filtfilt),
        dec_m_filtfilt_std =  (dec_m_filtfilt - mean(dec_m_filtfilt)) / sd(dec_m_filtfilt),
        vel_lat_filt_std = (vel_lat_filt - mean(vel_lat_filt)) / sd(vel_lat_filt),
        acc_lat_filtfilt_std = (acc_lat_filtfilt - mean(acc_lat_filtfilt)) / sd(acc_lat_filtfilt),
        dec_lat_filtfilt_std = (dec_lat_filtfilt - mean(dec_lat_filtfilt)) / sd(dec_lat_filtfilt),
      forearmlength_std = (forearmlength - mean(forearmlength)) / sd(forearmlength)
    ) %>% as.data.table()
```

```{r}
combined_data <- bind_rows(
    simdata %>% dplyr::select(ppid, study, std_vel_pre, std_vel_post, std_vel_change),
    martel_2019 %>% dplyr::select(ppid, study, std_vel_pre, std_vel_post, std_vel_change),
    martel_21 %>% dplyr::select(ppid, study, std_vel_pre, std_vel_post, std_vel_change, trial_num_in_block),
) 
empirical_plot <- bind_rows(
    combined_data %>% 
    group_by(ppid, study) %>% 
    summarise(std_vel_pre = mean(std_vel_pre), std_vel_post = mean(std_vel_post), std_vel_change = std_vel_post - std_vel_pre), 
    change_by_study) %>% 
    ggplot(aes(x = std_vel_change, y = forcats::fct_reorder(study, std_vel_change, .fun = mean, .desc = TRUE), fill = study, color = study)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "black", linewidth = 1) +
    stat_dotsinterval(
        point_size = 7,
        alpha = .5,
        point_alpha = 1,
        point_interval = mean_qi
    ) +
    theme_tidybayes() +
    theme(
        text = element_text(size = 18, color = "black"),
        legend.position = "none",
        plot.background = element_rect(fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        axis.text.x = element_text(color = "black"),
        axis.text.y = element_text(color = "black"),
        axis.title.y = element_blank(),
    ) +
    scale_fill_manual(
        breaks = c("Real-world", "VR (Avatar)", "VR (No Avatar)", "Martel et al. (2021)", "Martel et al. (2019)", "Cardinali et al. (2009, Simulated)"),
        values = c("#56B4E9", "#009E73", "#E69F00", "#330066", "#660033", "#003566")
    ) +
    scale_color_manual(
        breaks = c("Real-world", "VR (Avatar)", "VR (No Avatar)", "Martel et al. (2021)", "Martel et al. (2019)", "Cardinali et al. (2009, Simulated)"),
        values = c("#56B4E9", "#009E73", "#E69F00", "#330066", "#660033", "#003566")
    ) +
    labs(x = "Change in Standardized Velocity (Post - Pre)", y = "Study")


saveRDS(empirical_plot, here::here("scripts", "for_osf", "cumulative_analyses", "figures", "empirical_plot.rds"))
ggsave(
    here::here("scripts", "for_osf", "cumulative_analyses", "figures", "empirical_plot.svg"), 
    empirical_plot + pw_theme + theme(legend.position = "none"),
    width = 8, 
    height = 8, 
    dpi = 350,
    bg = "transparent"
    )
empirical_plot
```

## Kinematic Meta-Analysis (Velocity)



### Prior Distributions

```{r}
kinematic_meta_analysis_data <- combined_data %>%
    pivot_longer(
        cols = c(std_vel_pre, std_vel_post),
        names_to = "time",
        values_to = "std_vel"
    ) %>%
    dplyr::mutate(
        time = fifelse(time == "std_vel_pre", "Pre", "Post")
    ) %>%
    bind_rows(
      ppt_standardized %>%
        dplyr::select(ppid, study, std_vel, time, trial_num_in_block)
    ) %>%
    dplyr::mutate(
        time = factor(time, levels = c("Pre", "Post")))


kinematic_meta_analysis_priors <- brm(
    std_vel ~ 1 + time + (1 + time | study) + (1 + time | ppid),
    data = kinematic_meta_analysis_data,
    family = gaussian,
    prior = c(
        set_prior(prior = "normal(0, 2)", class = "Intercept"),
        set_prior(prior = "normal(-.2, 1.5)", class = "b", coef = "timePost"),
        set_prior(prior = "exponential(1)", class = "sd"),
        set_prior(prior = "exponential(1)", class = "sigma"),
        set_prior(prior = "lkj(1)", class = "cor", group = "ppid"),
        set_prior(prior = "lkj(1)", class = "cor", group = "study")
    ),
    sample_prior = "only",
    seed = 1337,
    silent = TRUE, refresh = 0,
    save_pars = save_pars(all = TRUE),
    warmup = b, iter = i, chains = ch, cores = co,
    control = control_list
)

plot(kinematic_meta_analysis_priors)
summary(kinematic_meta_analysis_priors)
```

### Posterior

```{r}
kinematic_meta_analysis_posterior <- update(
    kinematic_meta_analysis_priors,
    sample_prior = "no",
    refresh = 0,
    seed = 1337,
    file = here::here("scripts", "for_osf", "cumulative_analyses", "models", "velocity_meta_analysis")
)

summary(kinematic_meta_analysis_posterior)

pp_check(kinematic_meta_analysis_posterior, ndraws = 50) +
    theme_tidybayes() +
    theme(
        axis.text.y = element_blank()
    ) +
    labs(
        title = "Peak Velocity",
        subtitle = "Posterior Draws vs. Empirical Distribution",
        x = "Velocity (mm/s)"
    )

velbf <- bayesfactor_pointnull(
    kinematic_meta_analysis_posterior,
    prior = kinematic_meta_analysis_priors
) %>% as.data.table()

meta_analysis_description <- bayestestR::describe_posterior(
    kinematic_meta_analysis_posterior,
    centrality = "map",
    ci_method = "hdi"
) %>% as.data.table()

meta_analysis_description
saveRDS(meta_analysis_description, here::here("scripts", "for_osf", "cumulative_analyses", "models", "meta_analysis_description.rds"))


velocity_peak_posterior <- kinematic_meta_analysis_data %>%
    distinct(
        time,
        study
    ) %>%
    add_epred_draws(
        kinematic_meta_analysis_posterior,
        re_formula = ~ 1 + time + (1 + time | study),
        seed = 1337,
        allow_new_levels = F,
        ndraws = 5000
    ) %>%
    mutate(
        Outcome = "Peak Velocity (Standardized)"
    ) %>%
    as.data.table() %>%
    pivot_wider(
      id_cols = c(study, .draw),
        names_from = time,
        values_from = .epred
    ) %>%
    mutate(
        Change = Post - Pre
    )

velocity_peak_posterior_overall <- kinematic_meta_analysis_data %>%
    distinct(
        time
    ) %>%
    add_epred_draws(
        kinematic_meta_analysis_posterior,
        re_formula = ~ 1 + time,
        seed = 1337,
        allow_new_levels = F,
        ndraws = 5000
    ) %>%
    mutate(
        Outcome = "Peak Velocity (Standardized)",
        study = "Overall"
    ) %>%
    as.data.table() %>%
    pivot_wider(
        id_cols = c(.draw, study),
        names_from = time,
        values_from = .epred
    ) %>%
    mutate(
        Change = Post - Pre
    )

velocity_posterior <- ggplot(
      velocity_peak_posterior %>%
        bind_rows(velocity_peak_posterior_overall) %>%
        as.data.frame(),
      aes(
          x = Change,
          y = study,
          fill = study,
          color = study
      )
  ) +
    geom_vline(xintercept = 0, alpha = .5, linetype = "dashed", color = "black", size = .5) +
    geom_hline(yintercept = 4, alpha = .5, linetype = "dashed", color = "black", size = .5) +
    geom_density_ridges(
        alpha = .5,
        scale = 1.3,
        color = "black",
        size = .5,
        rel_min_height = .01
    ) +
    ggdist::stat_pointinterval(
        point_size = 5,
        linewidth = 3,
        interval_color = "black",
    )+
    scale_x_continuous(expand = c(0, 0), limits = c(-1, 1)) +
    scale_y_discrete(expand = c(.05, .05)) +
    scale_color_manual(values = c(brewer.pal(n = 8, name = "Dark2"))) +
    scale_fill_manual(values = c(brewer.pal(n = 8, name = "Dark2"))) +
    theme_tidybayes() +
    theme(text = element_text(size = 10)) +
    theme(
        axis.text.y = element_text(size = 18, color = "black"),
        axis.text.x = element_text(size = 14, color = "black"),
        axis.title.x = element_text(size = 18),
        axis.title.y = element_blank(),
        panel.background = element_rect(fill = "transparent", colour = NA),
        legend.background = element_rect(fill = "transparent", colour = NA),
        legend.position = "none",
        plot.background = element_rect(fill = "transparent", colour = NA)
    ) +
    labs(
        x = "Standardized Change in Peak Velocity (Pre - Post)",
        y = "Study"
    )

velocity_posterior
saveRDS(
    velocity_posterior, 
    here::here("scripts", "for_osf", "cumulative_analyses", "figures", "velocity_posterior.rds"))
ggsave(
    here::here("scripts", "for_osf", "cumulative_analyses", "figures", "velocity_posterior_presentation.svg"),
    velocity_posterior + pw_theme + theme(legend.position = "none"), 
    width = 12, 
    height = 6, 
    bg = "transparent",
    dpi = 300)
```

# Session Info

```{r session-info}
sessioninfo::session_info()
```