---
title: "Cumulative Analyses"
author: "Joshua Bell"
date: "11/22/2021"
output: html_document
---

```{r setup, include=FALSE}
pkgs <- c("dplyr", "tidyr", "readr", "data.table", "magrittr", "here", "plotly", "ggplot2", "gghalves", "ggthemes", "patchwork", "BayesFactor", "tidybayes", "correlation", "knitr", "datawizard", "brms", "RColorBrewer", "ggridges")
for(i in pkgs){
  if(!i %in% rownames(installed.packages())){ 
    install.packages(i) 
    library(i, character.only = TRUE)
  }
  else(library(i, character.only = TRUE))
}
# Sets stan backend to cmdstan. You will need to install the cmdstanr package and set up the toolchain.
options("mc.cores" = parallel::detectCores(), "brms.backend" = "cmdstan", tinytex.verbose = T)

b = 2400/parallel::detectCores()
i = 24000/parallel::detectCores()
ch = parallel::detectCores()
co = parallel::detectCores()
control_list <- list(adapt_delta = .99, max_treedepth = 15)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE, fig.width = 12, fig.height = 8)

ppt_m <- read_csv(here::here("data", "study_one", "ppt_manual.csv")) %>%
    bind_rows(
        read_csv(here::here("data", "study_two", "ppt_manual.csv")),
        read_csv(here::here("data", "study_three", "ppt_manual.csv"))
    ) %>%
    as.data.table() %>%
    mutate(
        study = fcase(
            ppid %like% "d1-0", "VR (No Avatar)",
            ppid %like% "d2-0", "Real-world",
            ppid %like% "d3-0", "VR (Avatar)",
            default = NA
        ),
        time = factor(
            x = time,
            levels = c("pre", "post"),
            labels = c("Pre", "Post")
        ),
        order = factor(
            x = order,
            levels = c("pre", "first", "second"),
            labels = c("Pre", "First", "Second")
        )
    )



landmark <- read_csv(here::here("data", "study_one", "landmark.csv")) %>%
    bind_rows(
        read_csv(here::here("data", "study_two", "landmark.csv")),
        read_csv(here::here("data", "study_three", "landmark.csv"))
    ) %>%
    mutate(
        study = fcase(
            ppid %like% "d1-0", "VR (No Avatar)",
            ppid %like% "d2-0", "Real-world",
            ppid %like% "d3-0", "VR (Avatar)",
            default = NA
        ),
        error_std = standardize(lapse_fix_error),
        target = factor(lapse_fix_target,
            levels = c("Elbow", "Forearm", "Wrist")
        ),
        error_cm = lapse_fix_error * 100,
        forearmlength = forearmlength * 100,
        forearmlength_std = standardize(forearmlength),
        time = factor(time,
            levels = c("pre", "post"),
            labels = c("Pre", "Post")
        ),
        order = factor(
            x = order, levels = c("pre", "first", "second"),
            labels = c("Pre", "First", "Second")
        )
    ) %>%
    as.data.table()

participant_info <- bind_rows(
read_csv(
    here::here("data", "1_tooluseinVR", "participant_info.csv"),
),
read_csv(
    here::here("data", "2_toolusenotinVR", "participant_info.csv"),
),
read_csv(
    here::here("data", "3_avatartooluse", "participant_info_coded.csv"),
) %>% mutate(
  fatigue = fifelse(fatigue_yn, 1, 0)
)
) %>%
    mutate(
          study = fcase(ppid %like% "d1-0", "VR (No Avatar)",
                        ppid %like% "d2-0", "Real-world",
                        ppid %like% "d3-0", "VR (Avatar)",
                        default = NA)
    ) %>%
    as.data.table()
    
    



ppt_forearmlength <- landmark[, .(forearmlength = mean(forearmlength)),
                                by = c("ppid")] %>% merge(ppt_m, by = c("ppid")) %>%
                                as.data.table()


ppt_forearm_surveys <- merge(
    ppt_forearmlength,
participant_info[,
        .(
            ppid,
            study,
            age,
            gender,
            fatigue,
            performance_hypothesis
        )
    ],
    by = c("ppid", "study")
)
```




### How many participants displayed the expected effects?
```{r follow-ups-expected-effects}
ppt_m %>%
    group_by(ppid, time) %>%
    dplyr::summarise(m_vel = mean(vel_m_filt)) %>%
    as.data.table() %>%
    dcast(ppid ~ time) %>%
    mutate(direction = fifelse(Pre > Post, 1, 0)) %>%
    dplyr::summarise(num_velocity_effect = sum(direction))

ppt_m %>%
    group_by(ppid, time) %>%
    dplyr::summarise(m_acc = mean(acc_m_filtfilt)) %>%
    as.data.table() %>%
    dcast(ppid ~ time) %>%
    mutate(direction = fifelse(Pre > Post, 1, 0)) %>%
    dplyr::summarise(num_accel_effect = sum(direction))

ppt_m %>%
    group_by(ppid, time) %>%
    dplyr::summarise(m_dec = mean(dec_m_filtfilt)) %>%
    as.data.table() %>%
    dcast(ppid ~ time) %>%
    mutate(direction = fifelse(Pre < Post, 1, 0)) %>%
    dplyr::summarise(num_decel_effect = sum(direction))

landmark %>%
    group_by(ppid, time, target) %>%
    dplyr::summarise(error = mean(error_std)) %>%
    as.data.table() %>%
    dcast(ppid + target ~ time) %>%
    mutate(direction = fifelse(Pre < Post, "Further", "Closer")) %>%
    group_by(target) %>%
    dplyr::summarise(num_further = sum(direction == "Further"))
```

# Exploratory Analyses

The following analyses were not preregistered, but were outlined in @bell2022 as a possible approach to evaluating the validity of kinematics as a measure of embodiment.

### Does Forearm Length influence baseline kinematic measures?

```{r forearm-length-influence}
t <- ppt_forearmlength[
    time == "Pre",
    `:=`(
        forearmlength_std = standardize(forearmlength),
        vel_m_filt_std = standardize(vel_m_filt),
        acc_m_filtfilt_std = standardize(acc_m_filtfilt),
        dec_m_filtfilt_std = standardize(dec_m_filtfilt),
        vel_lat_filt_std = standardize(vel_lat_filt),
        acc_lat_filtfilt_std = standardize(acc_lat_filtfilt),
        dec_lat_filtfilt_std = standardize(dec_lat_filtfilt),
        ppid = factor(ppid),
        trial_num_in_block = trial_num_in_block
    )
]

vel <- t %>%
    group_by(ppid) %>%
    dplyr::summarise(
        forearmlength = mean(forearmlength),
        vel_m_filt = mean(vel_m_filt)
    ) %>%
    ggplot(aes(x = forearmlength, y = vel_m_filt)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)

acc <- t %>%
    group_by(ppid) %>%
    dplyr::summarise(
        forearmlength = mean(forearmlength),
        acc_m_filtfilt = mean(acc_m_filtfilt)
    ) %>%
    ggplot(aes(x = forearmlength, y = acc_m_filtfilt)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)

dec <- t %>%
    group_by(ppid) %>%
    dplyr::summarise(
        forearmlength = mean(forearmlength),
        dec_m_filtfilt = mean(dec_m_filtfilt)
    ) %>%
    ggplot(aes(x = forearmlength, y = dec_m_filtfilt)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)

vel_lat <- t %>%
    group_by(ppid) %>%
    dplyr::summarise(
        forearmlength = mean(forearmlength),
        vel_lat_filt = mean(vel_lat_filt)
    ) %>%
    ggplot(aes(x = forearmlength, y = vel_lat_filt)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)

acc_lat <- t %>%
    group_by(ppid) %>%
    dplyr::summarise(
        forearmlength = mean(forearmlength),
        acc_lat_filtfilt = mean(acc_lat_filtfilt)
    ) %>%
    ggplot(aes(x = forearmlength, y = acc_lat_filtfilt)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)

dec_lat <- t %>%
    group_by(ppid) %>%
    dplyr::summarise(
        forearmlength = mean(forearmlength),
        dec_lat_filtfilt = mean(dec_lat_filtfilt)
    ) %>%
    ggplot(aes(x = forearmlength, y = dec_lat_filtfilt)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)

(vel + acc + dec) / (vel_lat + acc_lat + dec_lat) & theme_tidybayes()

cor <- ppt_forearmlength %>%
    group_by(ppid) %>%
    dplyr::summarise(
        forearmlength = mean(forearmlength),
        vel_m_filt = mean(vel_m_filt),
        acc_m_filtfilt = mean(acc_m_filtfilt),
        acc_lat_filtfilt = mean(acc_lat_filtfilt),
        dec_m_filtfilt = mean(dec_m_filtfilt),
        vel_lat_filt = mean(vel_lat_filt),
        dec_lat_filtfilt = mean(dec_lat_filtfilt,
            acc_lat_filtfilt = mean(acc_lat_filtfilt)
        )
    ) %>%
    correlation::correlation(
        method = "auto",
        bayesian = TRUE,
        bayesian_test = "bf",
        partial = FALSE
    )

forearm_velocity <- brm(
    mvbind(
        vel_m_filt_std, acc_m_filtfilt_std, dec_m_filtfilt_std,
        vel_lat_filt_std, acc_lat_filtfilt_std, dec_lat_filtfilt_std
    ) ~ 1 + forearmlength_std + (1 + forearmlength_std | ppid),
    prior = c(
        prior(normal(0, 2), class = "b")
    ),
    data = t,
    sample_prior = TRUE,
    seed = 1337,
    silent = TRUE,
    save_pars = save_pars(all = TRUE),
    file = here::here("data", "models", "all_studies", "mv_forearm.rds"),
    warmup = b, iter = i, chains = ch, cores = co,
    control = list(adapt_delta = .995, max_treedepth = 15)
)

forearm_velocity %>% bayestestR::bayesfactor_pointnull()
```

### Does Forearm Length affect pre-post change in kinematic measures?

```{r forearm-length-influence-change}
forearmlength_change <- ppt_forearmlength %>%
dcast(
    ppid + forearmlength ~ time,
    value.var = c("vel_m_filt", "acc_m_filtfilt", "dec_m_filtfilt", "vel_lat_filt", "acc_lat_filtfilt", "dec_lat_filtfilt"),
    fun.aggregate = mean
  ) %>%
  mutate(
    # Calculate pre-to-post change as post - pre
    "vel_change" = vel_m_filt_Post - vel_m_filt_Pre,
    "acc_change" = acc_m_filtfilt_Post - acc_m_filtfilt_Pre,
    "dec_change" = dec_m_filtfilt_Post - dec_m_filtfilt_Pre,
    "vel_lat_change" = vel_lat_filt_Post - vel_lat_filt_Pre,
    "acc_lat_change" = acc_lat_filtfilt_Post - acc_lat_filtfilt_Pre,
    "dec_lat_change" = dec_lat_filtfilt_Post - dec_lat_filtfilt_Pre
  ) %>%
  # Select only the change columns
  select(
    ppid,
    forearmlength,,
    ends_with("change")
  )

# Plot the change in peak velocity as a function of forearm length
forearmlength_change %>%
  ggplot(aes(x = forearmlength, y = vel_change)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

forearmlength_change %>%
  ggplot(aes(x = forearmlength, y = acc_change)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

forearmlength_change %>%
  ggplot(aes(x = forearmlength, y = dec_change)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

forearmlength_change %>%
  ggplot(aes(x = forearmlength, y = vel_lat_change)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

forearmlength_change %>%
  ggplot(aes(x = forearmlength, y = acc_lat_change)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

forearmlength_change %>%
  ggplot(aes(x = forearmlength, y = dec_lat_change)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

forearmlength_change %>%
    correlation::correlation(
        method = "auto",
        bayesian = TRUE,
        bayesian_test = "bf",
        partial = FALSE
    )
```



### Does order matter in terms of effect?

#### Kinematics - Velocity
```{r order-influence-kinematics-velocity}
order_test_vel <- ppt_m %>% group_by(ppid, order) %>% 
dplyr::summarise(m_vel = mean(vel_m_filt)) %>% 
as.data.table() %>% 
dcast(ppid~order) 

order_test_vel %>%
dplyr::filter(!is.na(First)) %>% 
mutate(direction = fifelse(Pre > First, 1, 0)) %>% 
dplyr::summarise(prop_velocity_effect = sum(direction)/n())

order_test_vel %>%
dplyr::filter(!is.na(Second)) %>% 
mutate(direction = fifelse(Pre > Second, 1, 0)) %>% 
dplyr::summarise(prop_velocity_effect = sum(direction)/n())

```

#### Kinematics - Acceleration
```{r order-influence-kinematics-acceleration}

order_test_acc <- ppt_m %>% group_by(ppid, order) %>% 
dplyr::summarise(m_acc = mean(acc_m_filtfilt)) %>% 
as.data.table() %>% 
dcast(ppid~order) 

order_test_acc %>% 
dplyr::filter(!is.na(First)) %>% 
mutate(direction = fifelse(Pre > First, 1, 0)) %>% 
dplyr::summarise(prop_accel_effect = sum(direction)/n()) 

order_test_acc %>% 
dplyr::filter(!is.na(Second)) %>% 
mutate(direction = fifelse(Pre > Second, 1, 0)) %>% 
dplyr::summarise(prop_accel_effect = sum(direction)/n()) 

```

#### Kinematics - Deceleration
```{r order-influence-kinematics-deceleration}

order_test_dec <- ppt_m %>% group_by(ppid, order) %>% 
dplyr::summarise(m_dec = mean(dec_m_filtfilt)) %>% 
as.data.table() %>% 
dcast(ppid~order) 

order_test_dec %>% 
dplyr::filter(!is.na(First)) %>% 
mutate(direction = fifelse(Pre < First, 1, 0)) %>% 
dplyr::summarise(prop_decel_effect = sum(direction)/n())

order_test_dec %>% 
dplyr::filter(!is.na(Second)) %>% 
mutate(direction = fifelse(Pre < Second, 1, 0)) %>% 
dplyr::summarise(prop_decel_effect = sum(direction)/n())

```

#### Landmark Biases
```{r order-influence-landmark}
order_test_lm <- landmark %>% group_by(ppid, order, target) %>% 
dplyr::summarise(error = mean(error_std)) %>% 
as.data.table() %>% 
dcast(ppid+target~order)

order_test_lm %>%
dplyr::filter(!is.na(First)) %>%
mutate(direction = fifelse(Pre < First, "Further", "Closer")) %>%
group_by(target) %>%
dplyr::summarise(prop_further = sum(direction == "Further")/n())

order_test_lm %>%
dplyr::filter(!is.na(Second)) %>%
mutate(direction = fifelse(Pre < Second, "Further", "Closer")) %>%
group_by(target) %>%
dplyr::summarise(prop_further = sum(direction == "Further")/n())
```



### How do kinematic values change by trial?

```{r by-trial-kinematics}
ppt_combined <- ppt_forearm_surveys %>% 
  mutate(overall_trial = fcase(time == "Pre", trial_num_in_block,
                               time == "Post", trial_num_in_block + 18),
          study = fcase(ppid %like% "d1-0", "VR (No Avatar)",
                        ppid %like% "d2-0", "Real-world",
                        ppid %like% "d3-0", "VR (Avatar)",
                        default = NA))

ppt_combined %>%
  dplyr::filter(vel_m_filt < 2000, !(time == "tool-use" & vel_m_filt > 1500), !vel_m_filt < 100) %>%
  ggplot(aes(x = overall_trial, y = vel_m_filt,  color = time)) +
  geom_point(size = 2, alpha = .5) +
  geom_smooth(aes(color = time), size = 2, alpha = .5, method = "lm") +
  theme_tidybayes() +
  theme(text = element_text(size = 26)) +
  scale_y_continuous(limits = c(0, 2000)) 

by_trial_velocity <- ppt_combined %>%
  dplyr::filter(vel_m_filt < 2000,
              !(time == "tool-use" & vel_m_filt > 1500)) %>%
  group_by(overall_trial, time, study) %>%
  dplyr::summarise(m_vel = mean(vel_m_filt),
            m_acc = mean(acc_m_filtfilt),
            m_dec = mean(dec_m_filtfilt)) %>%
  ggplot(aes(x = overall_trial, y = m_vel, group = interaction(study, time), color = study, linetype = study)) +
    geom_line(linewidth = 1) +
    geom_point(size = 3) +
    geom_vline(xintercept = 18.5, linetype = "dashed") +
    scale_color_manual(values = c("VR (No Avatar)" = "#E69F00", "Real-world" = "#56B4E9", "VR (Avatar)" = "#009E73")) +
    labs(x = "Trial", y = "Peak Velocity (mm/s)", color = "Study", linetype = "Study") +
    theme_tidybayes()+
    theme(text = element_text(size = 22),
        plot.background = element_rect(fill = "transparent", color = NA),
        panel.background = element_rect(fill = "transparent", color = NA),
        legend.background = element_rect(fill = "transparent", color = NA),
        legend.position = "bottom",
        legend.key = element_rect(fill = "transparent", color = NA))

saveRDS(by_trial_velocity, here::here("scripts", "for_osf", "cumulative_analyses", "figures", "by_trial_velocity.rds"))
ggsave(
    here::here("scripts", "for_osf", "cumulative_analyses", "figures", "by_trial_velocity.svg"), 
    by_trial_velocity + labs(title = "Peak Velocity By Trial"), 
    width = 10, 
    height = 8, 
    units = "in", 
    dpi = 300, 
    bg = "transparent")
```

### Is this influenced by order?
```{r order-influence-by-trial-kinematics-velocity}
ppt_combined %>%
dplyr::filter(overall_trial > 66, order != "Pre") %>%
group_by(overall_trial, order) %>% dplyr::summarise(m_vel = mean(vel_m_filt), m_acc = mean(acc_m_filtfilt), m_dec = mean(dec_m_filtfilt)) %>%
ggplot(aes(x = overall_trial, y = m_vel, color = order)) +
  geom_line(size = 2)
```


```{r performance-hypothesis-and-fatigue-distribution}


# Use ggplot to plot the number of participants who reported a performance hypothesis in each study
participant_info %>%
  ggplot(
    aes(
    fill = performance_hypothesis,
    y = study)
  ) +
  geom_bar(position = position_dodge()) +
  labs(title = "Performance Hypothesis", y = "Study", x = "Number of Participants") +
  theme_tidybayes() +
  theme(text = element_text(size = 26)) +
  scale_fill_manual(
    values = c("#001015", "#09A1D7")
    )

# Use ggplot to plot the number of participants who reported fatigue in each study
participant_info %>%
  ggplot(
    aes(
    fill = fatigue,
    y = study)
  ) +
  geom_bar(position = position_stack()) +
  labs(title = "Fatigue", y = "Study", x = "Number of Participants") +
  theme_tidybayes() +
  theme(text = element_text(size = 26)) +
  scale_fill_manual(
    values = c("#001015", "#09A1D7")
    )
```

### Is the effect influenced by a performance hypothesis?

```{r performance-hypothesis-influence}
participant_info_and_kinematics <- ppt_m %>%
  left_join(participant_info, by = c("ppid", "study")) %>%
  mutate(
    overall_trial = fifelse(
      time == "Post",
      trial_num_in_block + 18,
      trial_num_in_block
    )
  )

participant_info_and_kinematics %>%
group_by(time, performance_hypothesis) %>%
dplyr::summarise(
  m_vel = mean(vel_m_filt, na.rm = TRUE),
  m_acc = mean(acc_m_filtfilt, na.rm = TRUE),
  m_dec = mean(dec_m_filtfilt, na.rm = TRUE), n = n()/18
  )
```

```{r performance-hypothesis-plot}
# Use ggplot to plot a point and line plot of the mean peak velocity on the y axis 
# across each trial on the x axis, grouping by performance hypothesis and using the 
# color aesthetic to differentiate the two groups
performance_hypothesis_plot <- participant_info_and_kinematics %>%
  group_by(overall_trial, time, performance_hypothesis, fatigue) %>%
  dplyr::summarise(
    m_vel = mean(vel_m_filt),
    m_acc = mean(acc_m_filtfilt),
    m_dec = mean(dec_m_filtfilt)
  ) %>%
  ggplot(
    aes(
      x = overall_trial,
      y = m_vel, 
      group = interaction(
        time,
        performance_hypothesis
      ), 
      color = factor(performance_hypothesis)
    )
    ) +
    geom_line(size = 2) +
    labs(
      title = "Peak Velocity By Trial",
      subtitle = "Studies 1 & 2",
      x = "Trial",
      y = "Peak Velocity (mm/s)",
      color = "Performance Hypothesis"
      ) +
    theme_tidybayes()+
    scale_color_manual(
    breaks = c("No", "Yes"),
    values = c("#001015", "#09A1D7"),
    labels = c("No", "Yes")
    ) +
    theme(text = element_text(size = 34))

performance_hypothesis_plot +
facet_wrap(~fatigue, ncol = 1, scales = "free_y")
```

### Is the effect influenced by fatigue?

```{r fatigue-influence}
# Use ggplot to plot a point and line plot of the mean peak velocity on the y axis 
# across each trial on the x axis, grouping by fatigue and using the 
# color aesthetic to differentiate the two groups
participant_info_and_kinematics %>%
  group_by(overall_trial, time, fatigue, study) %>%
  dplyr::summarise(m_vel = mean(vel_m_filt),
            m_acc = mean(acc_m_filtfilt),
            m_dec = mean(dec_m_filtfilt)) %>%
  ggplot(aes(x = overall_trial,
  y = m_vel, 
  group = interaction(
    time,
    fatigue
    ), 
    color = factor(fatigue)
    )
    ) +
    facet_wrap(~study, ncol = 1, scales = "free_y") +
    geom_line(size = 2) +
    labs(
      title = "Peak Velocity By Trial",
      subtitle = "Studies 1 & 2",
      x = "Trial",
      y = "Peak Velocity (mm/s)",
      color = "Fatigue"
      ) +
    theme_tidybayes()+
    scale_color_manual(
    breaks = c("No", "Yes"),
    values = c("#001015", "#09A1D7"),
    labels = c("No", "Yes")
    ) +
    theme(text = element_text(size = 34))
```

```{r fatigue-influence-by-order}
# Recreates the previous plot twice, once for each order in the post-test (one for "First" and one for "Second")
# Then combine the two plots into one using the patchwork package

first_order_participants <- unique(
  participant_info_and_kinematics[
    participant_info_and_kinematics$order == "First", 
    ppid
    ]
  )
second_order_participants <- unique(
  participant_info_and_kinematics[
    participant_info_and_kinematics$order == "Second", 
    ppid
    ]
  )

(
  participant_info_and_kinematics %>%
  dplyr::filter(ppid %in% first_order_participants) %>%
  group_by(overall_trial, time, fatigue, study) %>%
  dplyr::summarise(m_vel = mean(vel_m_filt),
            m_acc = mean(acc_m_filtfilt),
            m_dec = mean(dec_m_filtfilt)) %>%
  ggplot(aes(x = overall_trial,
  y = m_vel, 
  linetype = study,
  group = interaction(
    time,
    fatigue,
    study
    ), 
    color = factor(fatigue)
    )
    ) +
    geom_line(size = 2) +
    labs(
      title = "Reaching First",
      x = "Trial",
      y = "Peak Velocity (mm/s)",
      color = "Fatigue"
      ) +
    theme_tidybayes()+
    scale_color_manual(
    breaks = c("No", "Yes"),
    values = c("#001015", "#09A1D7"),
    labels = c("No", "Yes")
    ) +
    theme(text = element_text(size = 34))
) / (
  participant_info_and_kinematics %>%
  dplyr::filter(ppid %in% second_order_participants) %>%
  group_by(overall_trial, time, fatigue, study) %>%
  dplyr::summarise(m_vel = mean(vel_m_filt),
            m_acc = mean(acc_m_filtfilt),
            m_dec = mean(dec_m_filtfilt)) %>%
  ggplot(aes(x = overall_trial,
  y = m_vel, 
  group = interaction(
    time,
    fatigue,
    study
    ), 
    color = factor(fatigue),
    linetype = study
    )
    ) +
    geom_line(size = 2) +
    labs(
      title = "Reaching Second",
      x = "Trial",
      y = "Peak Velocity (mm/s)",
      color = "Fatigue"
      ) +
    theme_tidybayes()+
    scale_color_manual(
    breaks = c("No", "Yes"),
    values = c("#001015", "#09A1D7"),
    labels = c("No", "Yes")
    ) +
    theme(text = element_text(size = 34))
) +
    patchwork::plot_annotation(
      title = "Peak Velocity By Trial",
      subtitle = "Studies 1 & 2",
      caption = "Figure 1: Peak velocity by trial for each order in the post-test. The line plot shows the mean peak velocity for each trial, with the color representing fatigue and the line representing the order in the post-test. The first order in the post-test is the first time the participant used the tool in the virtual reality environment. The second order in the post-test is the second time the participant used the tool in the virtual reality environment.",
      theme = theme(plot.title = element_text(size = 34), plot.subtitle = element_text(size = 26))
    )
```
Figure S_: Peak velocity by trial for each order in the post-test. The line plot shows the mean peak velocity for each trial, with the color representing fatigue and the line representing the order in the post-test. The first order in the post-test is the first time the participant used the tool in the virtual reality environment. The second order in the post-test is the second time the participant used the tool in the virtual reality environment.


```{r fatigue-influence-by-order-summarise}
participant_info_and_kinematics %>%
  dplyr::filter(
    ppid %in% first_order_participants
    , 
    overall_trial %in% c(1:21)
    ) %>%
  group_by(time, fatigue) %>%
  dplyr::summarise(m_vel = mean(vel_m_filt),
            m_acc = mean(acc_m_filtfilt),
            m_dec = mean(dec_m_filtfilt),
            n = n()/18)

participant_info_and_kinematics %>%
  dplyr::filter(
    ppid %in% unique(
      second_order_participants
    ), 
    overall_trial %in% c(1:21)
    ) %>%
  group_by(time, fatigue) %>%
  dplyr::summarise(m_vel = mean(vel_m_filt),
            m_acc = mean(acc_m_filtfilt),
            m_dec = mean(dec_m_filtfilt),
            n = n()/18)
```


```{r bongers-replication, include=FALSE}
ppt_peaks_bongers <- participant_info_and_kinematics %>%
    dplyr::filter(
        (time == "Post" & 
        trial_num_in_block %in% c(1:3)) 
        | 
        (time == "Pre" & 
        trial_num_in_block %in% c(16:18))
        ) %>%
        group_by(study) %>%
        mutate(
            vel_m_filt_std = (vel_m_filt - mean(vel_m_filt, na.rm = TRUE))/sd(vel_m_filt, na.rm = TRUE),
            acc_m_filtfilt_std = (acc_m_filtfilt - mean(acc_m_filtfilt, na.rm = TRUE))/sd(acc_m_filtfilt, na.rm = TRUE),
            dec_m_filtfilt_std = (dec_m_filtfilt - mean(dec_m_filtfilt, na.rm = TRUE))/sd(dec_m_filtfilt, na.rm = TRUE)
            )

ppt_acceleration_and_latencies_bongers <- ppt_m %>%
  mutate(acc_m_filtfilt_std = standardize(acc_m_filtfilt)) %>%
  dplyr::filter(
      (time == "Post" & 
      trial_num_in_block %in% c(1:6)) 
      | 
      (time == "Pre" & 
      trial_num_in_block %in% c(13:18))
      )

```

As in Bongers, data is filtered such that the analysis only considers the last 6 trials of the first block (Pre) and the first 6 trials of the second block (Post) of manual reaching. 

## Peaks
### Velocity
#### Prior
```{r velocity-peak-prior}
velocity_peak_priors <- brm(
  vel_m_filt_std ~ 1 + time * fatigue + (1 + time + fatigue | ppid), 
  data = ppt_peaks_bongers, 
  family = gaussian,
  prior = c(
    set_prior(prior = "normal(-.2, 2)", class = "b", coef = "timePost"),
    set_prior(prior = "normal(-.2, 2)", class = "b", coef = "fatigue"),
    set_prior(prior = "normal(0, 2)", class = "Intercept"),
    set_prior(prior = "exponential(1)", class = "sd"), 
    set_prior(prior = "exponential(1)", class = "sigma"),
    set_prior(prior = "lkj(1)", class = "cor", group = "ppid")
  ),
  sample_prior = "only",
  seed = 1337,
  silent = TRUE, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(velocity_peak_priors)
summary(velocity_peak_priors)
```

#### Posterior

```{r velocity-peak-posterior}
velocity_peaks <- update(
  velocity_peak_priors,
  sample_prior = "no",
  refresh = 0,
  seed = 1337,
  file = here::here("scripts", "for_osf", "cumulative_analyses", "models", "peakvelocity_ppt_fatigue_bongers")
  )

plot(velocity_peaks)
summary(velocity_peaks)

pp_check(velocity_peaks, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Peak Velocity",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Velocity (mm/s)"
  )

velbf <- bayestestR::bayesfactor_pointnull(
  velocity_peaks,
  direction = "<",
  prior = velocity_peak_priors
  ) %>% as.data.table()

vel_describe <- bayestestR::describe_posterior(
  velocity_peaks,
  centrality = "map",
  ci_method="hdi"
  ) %>% 
  dplyr::filter(Parameter == "b_timePost:fatigueYes") %>% 
  mutate("Outcome" = "Peak Velocity")

(
  vel_describe <- bind_cols(
    vel_describe,
    "BF" = exp(
        velbf[Parameter == "b_timePost:fatigueYes",
        log_BF]
        )
        )
)
```

## Kinematic Meta-Analysis (Velocity)
### Prior Distributions

```{r kinematic-meta-analysis-velocity-prior}
# Cardinali et al. (2009) simulated
# Empirical values, taken (estimated) from Cardinali et al. (2009) figure 1C, corresponding to experiment 2.
mupre <- 1243.2
se <- 25.6
mupost <- 1195.2



# Error bars were 10px (in total), each side corresponding to 26.66 based on the y axis.
se <- 26.66

sample <- 18
sd <- se * sqrt(sample)
cor <- .9055
cov <- matrix(c(
    sd^2, cor * (sd^2),
    cor * (sd^2), sd^2
), nrow = 2)

simdata <- MASS::mvrnorm(sample, mu = c(mupre, mupost), cov, empirical = TRUE) %>%
    as.data.frame() %>%
    pivot_longer(cols = c(V1, V2), names_to = "time", values_to = "velocity") %>%
    mutate(
      std_vel = (velocity - mean(velocity)) / sd(velocity),
      time = factor(time, levels = c("V1", "V2"), labels = c("Pre", "Post")),
      ppid = as.character(rep(1:sample, each = 2))
      ) %>%
    pivot_wider(id_cols = ppid, names_from = time, values_from = std_vel) %>%
    mutate(
      std_vel_pre = Pre,
      std_vel_post = Post,
      std_vel_change = (Post - Pre),
      study = "Cardinali et al. (2009, Simulated)"
    ) 

# Martel et al. (2019) empirical data
martel_2019_wide <- read_csv(here::here("data", "priors", "Martel2019.csv"), col_types = "fddddddddddddddddddfdd")
martel_2019_long <- fread(here::here("data", "priors", "martel_manova_long.csv"))
    
martel_2019_long[,
    `:=`(
        vel_m_filt_std = (VEL - mean(VEL, na.rm = TRUE)) / sd(VEL, na.rm = TRUE),
        acc_m_filtfilt_std = (ACC - mean(ACC, na.rm = TRUE)) / sd(ACC, na.rm = TRUE),
        dec_m_filtfilt_std = (DEC - mean(DEC, na.rm = TRUE)) / sd(DEC, na.rm = TRUE),
        vel_lat_filt_std = (TPVEL - mean(TPVEL, na.rm = TRUE)) / sd(TPVEL, na.rm = TRUE),
        acc_lat_filtfilt_std = (TPACC - mean(TPACC, na.rm = TRUE)) / sd(TPACC, na.rm = TRUE),
        dec_lat_filtfilt_std = (TPDEC - mean(TPDEC, na.rm = TRUE)) / sd(TPDEC, na.rm = TRUE)
    ),
    by = c("GROUP")
][,
time := factor(Time, levels = c("PRE", "POST"), labels = c("Pre", "Post"))
]

martel_2019 <- martel_2019_wide %>%
    pivot_longer(cols = c(VELPRE, VELPOST), names_to = "time", values_to = "velocity") %>%
    mutate(
      std_vel = (velocity - mean(velocity)) / sd(velocity),
      time = factor(time, levels = c("VELPRE", "VELPOST"), labels = c("Pre", "Post")),
      ppid = SUBJECTS
    ) %>%
    pivot_wider(id_cols = c(ppid, FOREARMLENGTH), names_from = time, values_from = std_vel, values_fn = ~mean(.x)) %>%
    mutate(
        std_vel_pre = Pre,
        std_vel_post = Post,
        std_vel_change = (Post - Pre),
        study = "Martel et al. (2019)"
    ) 

martel_2019_forearm <- martel_2019_wide %>%
    group_by(GROUP) %>%
    dplyr::mutate(
        ppid = SUBJECTS,
        vel_m_filt = VELPRE,
        acc_m_filtfilt = ACCPRE,
        dec_m_filtfilt = DECPRE,
        vel_lat_filt = TPVELPRE,
        acc_lat_filtfilt = TPACCPRE,
        dec_lat_filtfilt = TPDECPRE,
        vel_m_filt_std = (vel_m_filt - mean(vel_m_filt, na.rm = TRUE))/sd(vel_m_filt, na.rm = TRUE),
        acc_m_filtfilt_std = (acc_m_filtfilt - mean(acc_m_filtfilt, na.rm = TRUE))/sd(acc_m_filtfilt, na.rm = TRUE),
        dec_m_filtfilt_std = (dec_m_filtfilt - mean(dec_m_filtfilt, na.rm = TRUE))/sd(dec_m_filtfilt, na.rm = TRUE),
        vel_lat_filt_std = (vel_lat_filt - mean(vel_lat_filt, na.rm = TRUE))/sd(vel_lat_filt, na.rm = TRUE),
        acc_lat_filtfilt_std = (acc_lat_filtfilt - mean(acc_lat_filtfilt, na.rm = TRUE))/sd(acc_lat_filtfilt, na.rm = TRUE),
        dec_lat_filtfilt_std = (dec_lat_filtfilt - mean(dec_lat_filtfilt, na.rm = TRUE))/sd(dec_lat_filtfilt, na.rm = TRUE),
        forearmlength = FOREARMLENGTH/10,
        forearmlength_std = (forearmlength - mean(forearmlength, na.rm = TRUE))/sd(forearmlength, na.rm = TRUE),
        study = fifelse(GROUP == 1, "Martel et al. (2019) Ahead", "Martel et al. (2019) Across")
    ) %>% 
    as.data.table()

# Martel et al. (2021) empirical data, 
martel_2021_18plus <- read_csv(here::here("data", "priors", "martel2021_18up_processed.csv")) %>%
mutate(
  std_vel = (VEL - mean(VEL, na.rm = TRUE)) / sd(VEL, na.rm = TRUE),
) %>% dplyr::select(
    subjects, 
    ForearmLength, 
    trials_reaching, 
    std_vel, 
    session,
    VEL,
    ACC,
    DEC,
    TPACC,
    TPDEC,
    TPVEL
    ) %>%
    filter(session != "TOOL") %>%
    mutate(
        vel_m_filt_std = (VEL - mean(VEL, na.rm = TRUE)) / sd(VEL, na.rm = TRUE),
        acc_m_filtfilt_std = (ACC - mean(ACC, na.rm = TRUE)) / sd(ACC, na.rm = TRUE),
        dec_m_filtfilt_std = (DEC - mean(DEC, na.rm = TRUE)) / sd(DEC, na.rm = TRUE),
        vel_lat_filt_std = (TPVEL - mean(TPVEL, na.rm = TRUE)) / sd(TPVEL, na.rm = TRUE),
        acc_lat_filtfilt_std = (TPACC - mean(TPACC, na.rm = TRUE)) / sd(TPACC, na.rm = TRUE),
        dec_lat_filtfilt_std = (TPDEC - mean(TPDEC, na.rm = TRUE)) / sd(TPDEC, na.rm = TRUE),
        study = "Martel et al. (2021) 18+",
        time = fifelse(session == "PRE", "Pre", "Post")
    )


martel_21 <- inner_join(
    martel_2021_18plus %>% filter(session %in% c("PRE")),
    martel_2021_18plus %>% filter(session %in% c("POST")),
    by = c("subjects", "trials_reaching", "ForearmLength"), suffix = c("PRE", "POST")
)

# Join again with tool-use Velocity as a third VEL column.

# Collapse across trials, computing averages.

martel_21 <- martel_21 %>%
    group_by(subjects, trials_reaching) %>%
    dplyr::summarise(
        trial_num_in_block = mean(trials_reaching),
        vel_m_filt = mean(VELPRE),
        acc_m_filtfilt = mean(ACCPRE),
        dec_m_filtfilt = mean(DECPRE),
        vel_lat_filt = mean(TPVELPRE),
        acc_lat_filtfilt = mean(TPACCPRE),
        dec_lat_filtfilt = mean(TPDECPRE),
        std_vel_pre = mean(std_velPRE, na.rm = TRUE),
        std_vel_post = mean(std_velPOST, na.rm = TRUE),
        std_vel_change = std_vel_post - std_vel_pre,
        forearmlength = mean(ForearmLength/10),
        study = "Martel et al. (2021)"
    ) %>%
    ungroup() %>%
    mutate(
      ppid = subjects,
        vel_m_filt_std = (vel_m_filt - mean(vel_m_filt)) / sd(vel_m_filt),
        acc_m_filtfilt_std = (acc_m_filtfilt - mean(acc_m_filtfilt)) / sd(acc_m_filtfilt),
        dec_m_filtfilt_std =  (dec_m_filtfilt - mean(dec_m_filtfilt)) / sd(dec_m_filtfilt),
        vel_lat_filt_std = (vel_lat_filt - mean(vel_lat_filt)) / sd(vel_lat_filt),
        acc_lat_filtfilt_std = (acc_lat_filtfilt - mean(acc_lat_filtfilt)) / sd(acc_lat_filtfilt),
        dec_lat_filtfilt_std = (dec_lat_filtfilt - mean(dec_lat_filtfilt)) / sd(dec_lat_filtfilt),
      forearmlength_std = (forearmlength - mean(forearmlength)) / sd(forearmlength)
    ) %>% as.data.table()

combined_data <- bind_rows(
    simdata %>% dplyr::select(ppid, study, std_vel_pre, std_vel_post, std_vel_change),
    martel_2019 %>% dplyr::select(ppid, study, std_vel_pre, std_vel_post, std_vel_change),
    martel_21 %>% dplyr::select(ppid, study, std_vel_pre, std_vel_post, std_vel_change, trial_num_in_block),
) 
```

```{r kinematic-meta-analysis-velocity-prior-model}
ppt_standardized <- ppt_forearm_surveys %>%
    dplyr::mutate(
      study = fcase(ppid %like% "d1-0", "VR (No Avatar)",
                    ppid %like% "d2-0", "Real-world",
                    ppid %like% "d3-0", "VR (Avatar)",
                    default = NA)
    ) %>%
    group_by(study) %>%
    dplyr::mutate(
      std_vel = (vel_m_filt - mean(vel_m_filt, na.rm = TRUE)) / sd(vel_m_filt, na.rm = TRUE),
        std_acc = (acc_m_filtfilt - mean(acc_m_filtfilt, na.rm = TRUE)) / sd(acc_m_filtfilt, na.rm = TRUE),
        std_dec = (dec_m_filtfilt - mean(dec_m_filtfilt, na.rm = TRUE)) / sd(dec_m_filtfilt, na.rm = TRUE),
        std_vel_lat = (vel_lat_filt - mean(vel_lat_filt, na.rm = TRUE)) / sd(vel_lat_filt, na.rm = TRUE),
        std_acc_lat = (acc_lat_filtfilt - mean(acc_lat_filtfilt, na.rm = TRUE)) / sd(acc_lat_filtfilt, na.rm = TRUE),
        std_dec_lat = (dec_lat_filtfilt - mean(dec_lat_filtfilt, na.rm = TRUE)) / sd(dec_lat_filtfilt, na.rm = TRUE)
    ) %>% ungroup()

kinematic_meta_analysis_data <- combined_data %>%
    pivot_longer(
        cols = c(std_vel_pre, std_vel_post),
        names_to = "time",
        values_to = "std_vel"
    ) %>%
    dplyr::mutate(
        time = fifelse(time == "std_vel_pre", "Pre", "Post")
    ) %>%
    bind_rows(
      ppt_standardized %>%
        dplyr::select(ppid, study, std_vel, time, trial_num_in_block)
    ) %>%
    dplyr::mutate(
        time = factor(time, levels = c("Pre", "Post")))


kinematic_meta_analysis_priors <- brm(
    std_vel ~ 1 + time + (1 + time | study) + (1 + time | ppid),
    data = kinematic_meta_analysis_data,
    family = gaussian,
    prior = c(
        set_prior(prior = "normal(0, 2)", class = "Intercept"),
        set_prior(prior = "normal(-.2, 1.5)", class = "b", coef = "timePost"),
        set_prior(prior = "exponential(1)", class = "sd"),
        set_prior(prior = "exponential(1)", class = "sigma"),
        set_prior(prior = "lkj(1)", class = "cor", group = "ppid"),
        set_prior(prior = "lkj(1)", class = "cor", group = "study")
    ),
    sample_prior = "only",
    seed = 1337,
    silent = TRUE, refresh = 0,
    save_pars = save_pars(all = TRUE),
    warmup = b, iter = i, chains = ch, cores = co,
    control = control_list,
    file = here::here("scripts", "for_osf", "cumulative_analyses", "models", "velocity_meta_analysis_priors")
)

plot(kinematic_meta_analysis_priors)
summary(kinematic_meta_analysis_priors)
```

### Posterior

```{r kinematic-meta-analysis-velocity-posterior}
kinematic_meta_analysis_posterior <- update(
    kinematic_meta_analysis_priors,
    sample_prior = "no",
    refresh = 0,
    seed = 1337,
    file = here::here("scripts", "for_osf", "cumulative_analyses", "models", "velocity_meta_analysis")
)

summary(kinematic_meta_analysis_posterior)

pp_check(kinematic_meta_analysis_posterior, ndraws = 50) +
    theme_tidybayes() +
    theme(
        axis.text.y = element_blank()
    ) +
    labs(
        title = "Peak Velocity",
        subtitle = "Posterior Draws vs. Empirical Distribution",
        x = "Velocity (mm/s)"
    )

velbf <- bayestestR::bayesfactor_pointnull(
    kinematic_meta_analysis_posterior,
    prior = kinematic_meta_analysis_priors
) %>% as.data.table()

meta_analysis_description <- bayestestR::describe_posterior(
    kinematic_meta_analysis_posterior,
    centrality = "map",
    ci_method = "hdi"
) %>% as.data.table()

meta_analysis_description
saveRDS(meta_analysis_description, here::here("scripts", "for_osf", "cumulative_analyses", "models", "meta_analysis_description.rds"))


velocity_peak_posterior <- kinematic_meta_analysis_data %>%
    distinct(
        time,
        study
    ) %>%
    add_epred_draws(
        kinematic_meta_analysis_posterior,
        re_formula = ~ 1 + time + (1 + time | study),
        seed = 1337,
        allow_new_levels = F,
        ndraws = 5000
    ) %>%
    mutate(
        Outcome = "Peak Velocity (Standardized)"
    ) %>%
    as.data.table() %>%
    pivot_wider(
      id_cols = c(study, .draw),
        names_from = time,
        values_from = .epred
    ) %>%
    mutate(
        Change = Post - Pre
    )

velocity_peak_posterior_overall <- kinematic_meta_analysis_data %>%
    distinct(
        time
    ) %>%
    add_epred_draws(
        kinematic_meta_analysis_posterior,
        re_formula = ~ 1 + time,
        seed = 1337,
        allow_new_levels = F,
        ndraws = 5000
    ) %>%
    mutate(
        Outcome = "Peak Velocity (Standardized)",
        study = "Overall"
    ) %>%
    as.data.table() %>%
    pivot_wider(
        id_cols = c(.draw, study),
        names_from = time,
        values_from = .epred
    ) %>%
    mutate(
        Change = Post - Pre
    )

velocity_posterior <- ggplot(
      velocity_peak_posterior %>%
        bind_rows(velocity_peak_posterior_overall) %>%
        as.data.frame(),
      aes(
          x = Change,
          y = study,
          fill = study,
          color = study
      )
  ) +
    geom_vline(xintercept = 0, alpha = .5, linetype = "dashed", color = "black", size = .5) +
    geom_hline(yintercept = 4, alpha = .5, linetype = "dashed", color = "black", size = .5) +
    geom_density_ridges(
        alpha = .5,
        scale = 1.3,
        color = "black",
        size = .5,
        rel_min_height = .01
    ) +
    ggdist::stat_pointinterval(
        point_size = 5,
        linewidth = 3,
        interval_color = "black",
    )+
    scale_x_continuous(expand = c(0, 0), limits = c(-1, 1)) +
    scale_y_discrete(expand = c(.05, .05)) +
    scale_color_manual(values = c(brewer.pal(n = 8, name = "Dark2"))) +
    scale_fill_manual(values = c(brewer.pal(n = 8, name = "Dark2"))) +
    theme_tidybayes() +
    theme(text = element_text(size = 10)) +
    theme(
        axis.text.y = element_text(size = 18, color = "black"),
        axis.text.x = element_text(size = 14, color = "black"),
        axis.title.x = element_text(size = 18),
        axis.title.y = element_blank(),
        panel.background = element_rect(fill = "transparent", colour = NA),
        legend.background = element_rect(fill = "transparent", colour = NA),
        legend.position = "none",
        plot.background = element_rect(fill = "transparent", colour = NA)
    ) +
    labs(
        x = "Standardized Change in Peak Velocity (Pre - Post)",
        y = "Study"
    )

pw_theme <- theme(
    plot.background = element_rect(fill = "transparent", color = "transparent"),
    panel.background = element_rect(fill = "transparent", color = "transparent"),
    legend.background = element_rect(fill = "transparent", color = "transparent"),
    legend.key = element_rect(fill = "transparent", color = "transparent"),
    legend.text = element_text(color = "black", size = 16),
    legend.title = element_text(color = "black", size = 20),
    legend.position = "bottom",
    text = element_text(color = "black"),
    axis.line.x = element_line(colour = "black", linewidth = .5),
    axis.line.y = element_line(colour = "black", linewidth = .5),
)


velocity_posterior
saveRDS(
    velocity_posterior, 
    here::here("scripts", "for_osf", "cumulative_analyses", "figures", "velocity_posterior.rds"))
ggsave(
    here::here("scripts", "for_osf", "cumulative_analyses", "figures", "velocity_posterior_presentation.svg"),
    velocity_posterior + pw_theme + theme(legend.position = "none"), 
    width = 12, 
    height = 6, 
    bg = "transparent",
    dpi = 300)
```