---
title: "Real-world - Trial-level Data - Reaching"
author: "Joshua Bell"
format:
  html:
    toc: true
    toc-depth: 3
    toc-float: true
    toc-placement: left
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(include = TRUE, echo = FALSE, fig.height = 6, fig.width = 12)

pkgs <- c("plyr", "data.table", "dplyr", "Rmisc", "magrittr", "tidyr", "readr", "ggplot2", "here", "tidybayes", "datawizard", "patchwork", "raster")
for(i in pkgs){
  if(!i %in% rownames(installed.packages())){ 
    install.packages(i) 
    library(i, character.only = TRUE)
  }
  else(library(i, character.only = TRUE))
}
# Set max memory to 1gb
rasterOptions(maxmemory = 10e+09)
setDTthreads(percent = 90)

ppt_m_fulltrials <- fread(here::here("data", "study_two", "ppt_m_fulltrials.csv"))

ppt_m_fulltrials <- ppt_m_fulltrials[order(ppid, block_num, trial_num_in_block, time_ms)
  ][,
         `:=`(phase = factor(phase, levels = c("start", "begin", "out", "lift", "replace", "return", "returned")),
         time = factor(time, levels = c("pre", "post")),
         ppid = factor(ppid))
  ]

ppt_m_fulltrials[,
          leadvel := lead(velocity_10hz, 5),
          by = c("ppid", "trial_num_in_block", "time")
          ][,
          dif := abs(velocity_10hz - leadvel),
          by = c("ppid", "trial_num_in_block", "time")
          ][,
            `:=`(movement_start_time = .SD[dif>50]$time_ms[1], 
                 vel_peak_time = .SD[phase %in% c("begin", "out"),][which.max(velocity_10hz),]$time_ms[1]),
          by = c("ppid", "trial_num_in_block", "time")][is.na(time_ms_fix), time_ms_fix := time_ms]

ppt_m <- fread(here::here("data", "study_two", "ppt_manual.csv"))
ppt_m[,
  time := factor(time, levels = c("pre", "post"))
  ]

```

# Overlaid Trials per Participant

## PPT
```{r plotsbyparticipant}
plots_participant <- list()

ppt_m_combined <- merge(ppt_m_fulltrials, ppt_m, by = c("ppid", "time", "block_num", "trial_num_in_block"), all.x = TRUE)

for(p in unique(ppt_m_fulltrials$ppid))
{
  bytrial_velocity <- ppt_m_combined[
      !phase %in% c("start", "lift",
      "replace", "return",
      "returned") 
      & time_ms_fix > 0
      & is.na(dec_lat_filtfilt) | (!is.na(dec_lat_filtfilt)
      & time_ms_fix < dec_lat_filtfilt + 50)
      & ppid == p
    ][
      order(block_num, trial_num_in_block, time_ms_fix)
    ][,
      time_ms_fix := (0:(.N - 1)) * 5,
      by = c("time", "block_num", "trial_num_in_block")
    ][,
      time_ms_norm := datawizard::normalize(time_ms_fix),
      by = c("time", "block_num", "trial_num_in_block")
    ]

    if(p == "d2-006")
    {
      bytrial_velocity <- bytrial_velocity[(trial_num_in_block != 5 | time != "post"),]
    } else if(p == "d2-011")
    {
      bytrial_velocity <- bytrial_velocity[(trial_num_in_block != 8 | time != "pre"),]
    } else if(p == "d2-018")
    {
      bytrial_velocity <- bytrial_velocity[(trial_num_in_block !=17 | time != "pre"),]
    }

  time_normed <- seq(0,1, by = 0.001)
  # Interpolate velocity to the common time scale using spline
  average_velocity <-bytrial_velocity[,
  .(
    velocity_interpolated = spline(time_ms_norm, velocity, xout = time_normed)$y,
    velocity_10hz_interpolated = spline(time_ms_norm, velocity_10hz, xout = time_normed)$y
    ),
    by = c("time", "block_num", "trial_num_in_block")
  ][,
    time_ms_norm := time_normed,
    by = c("time", "block_num", "trial_num_in_block")
  ][,
    .(velocity = mean(velocity_interpolated, na.rm = TRUE),
      velocity_10hz = mean(velocity_10hz_interpolated, na.rm = TRUE)),
    by = c("time_ms_norm", "time", "block_num")
  ][
    order(block_num, time_ms_norm)
    ]

  plots_participant[[p]] <- bytrial_velocity %>%
  ggplot(aes(x = time_ms_norm, 
              y = velocity_10hz, 
              color = time,
              group = interaction(trial_num_in_block, block_num))) +
        geom_line(alpha = .4) +
        geom_line(data = average_velocity,
                  aes(x = time_ms_norm,
                  y = velocity_10hz,
                  group = block_num),
                  size = 1) +
        scale_color_manual(values = c("firebrick", "steelblue")) +
        theme_tidybayes() +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
              text = element_text(size = 22)) +
        labs(x = "Time (normalized)", y = "Velocity (mm/s)", title = p) 
}

plots_participant
```

## Velocity by Participant x Trial

```{r plotcreationloop, include=FALSE, cache = FALSE}
plots <- list()
lats <- data.table()
for(p in unique(ppt_m_fulltrials$ppid))
{
  for(b in unique(ppt_m_fulltrials$time))
  {
    for(t in unique(ppt_m_fulltrials$trial_num_in_block))
    {
      m <- copy(ppt_m[!is.na(vel_m_filt) &
          ppid == p &
          time == b & 
          trial_num_in_block == t])
      d <- copy(
                ppt_m_fulltrials[
                  ppid == p & 
                  time == b & 
                  trial_num_in_block == t & 
                  !phase %in% c("start", "replace", "return", "returned") &
                  between(
                    time_ms_fix,
                    0, 
                    m$dec_lat_filtfilt + 500
                    ) &
                    !is.na(time_ms_fix) &
                    !is.na(velocity_10hz)
                  ]
                )
      
      plot <- d %>%
      ggplot(aes(x = time_ms_fix, 
                 y = velocity_10hz, 
                 color = phase,
                 fill = phase)) +
      geom_vline(xintercept = 0, size=.75, color = "blue")+
      geom_vline(xintercept = m[, vel_lat_filt], size=.75, color = "forestgreen")+
      geom_vline(xintercept = m[, acc_lat_filtfilt], size=.75, color = "steelblue")+
      geom_vline(xintercept = m[, dec_lat_filtfilt], size=.75, color = "gold") +
      geom_line(alpha = .5) +
      geom_area(alpha = .5) +
      scale_color_manual(values = c("steelblue", "forestgreen", "gold", "orange", "firebrick")) +
      scale_fill_manual(values = c("steelblue", "forestgreen", "gold", "orange", "firebrick")) +
      scale_x_continuous(limits = c(min(d[, time_ms_fix]), 
                                    max(d[, time_ms_fix])), 
                         breaks = scales::extended_breaks(as.integer(
                           (max(d[, time_ms_fix])-min(d[, time_ms_fix]))/100))) +
      scale_y_continuous(limits = c(0, max(d[, velocity_10hz]) + sd(d[, velocity_10hz]))) +
      theme_tidybayes() +
      theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
      labs(title = paste("Participant: ", unique(d$ppid), ", Time:", b, ", Trial: ", as.character(t)))
      
      if(length(copy(d[!is.na(start_time), start_time])) > 0)
      {
      plot <- plot +
      annotate(geom = "text",
                x = 50,
                y = m[, vel_m_filt],
                label = copy(d[!is.na(start_time), start_time][[1]]),
                color = "black",
                size = 8)
      }
      plots[[p]][[b]][[t]] <- plot
    }
  }
}

```

# Manual Reaching Trials - PPT
## General Information

- Movement onset calculated as the thick blue vertical line that appears in the timeline
- Acceleration, velocity and deceleration are pale blue, green and gold respectively
- The black text is the time of the movement onset from the start of recording.
- time_ms_fix is the original time_ms with the start time of the trial subtracted from it, making 0 the start of the movement

### Participant 1
#### Pre
```{r participant-1}
print(plots[["d2-001"]]["pre"])
```
#### Post
```{r participant-1-post}
print(plots[["d2-001"]]["post"])
```

### Participant 2
#### Pre
```{r participant-2}
print(plots[["d2-002"]]["pre"])
```
#### Post
```{r participant-2-post}
print(plots[["d2-002"]]["post"])
```


### Participant 3
#### Pre
```{r participant-3}
print(plots[["d2-003"]]["pre"])
```
#### Post
```{r participant-3-post}
print(plots[["d2-003"]]["post"])
```

### Participant 4
#### Pre
```{r participant-4}
print(plots[["d2-004"]]["pre"])
```
#### Post
```{r participant-4-post}
print(plots[["d2-004"]]["post"])
```

### Participant 5
#### Pre
```{r participant-5}
print(plots[["d2-005"]]["pre"])
```
#### Post
```{r participant-5-post}
print(plots[["d2-005"]]["post"])
```

### Participant 6
#### Pre
```{r participant-6}
plots[["d2-006"]]["pre"]
```
#### Post
```{r participant-6-post}
plots[["d2-006"]]["post"]
```



### Participant 7
#### Pre
```{r participant-7}
plots[["d2-007"]]["pre"]
```
#### Post
```{r }
plots[["d2-007"]]["post"]
```


### Participant 8
#### Pre
```{r participant-8}
plots[["d2-008"]]["pre"]
```
#### Post
```{r participant-8-post}
plots[["d2-008"]]["post"]
```



### Participant 9
#### Pre
```{r participant-9}
plots[["d2-009"]]["pre"]
```
#### Post
```{r participant-9-post}
plots[["d2-009"]]["post"]
```



### Participant 10
#### Pre
```{r participant-10}
plots[["d2-010"]]["pre"]
```
#### Post
```{r participant-10-post}
plots[["d2-010"]]["post"]
```



### Participant 11
#### Pre
```{r participant-11}
plots[["d2-011"]]["pre"]
```
#### Post
```{r participant-11-post}
plots[["d2-011"]]["post"]
```



### Participant 12
#### Pre
```{r participant-12}
plots[["d2-012"]]["pre"]
```
#### Post
```{r participant-12-post}
plots[["d2-012"]]["post"]
```



### Participant 13
#### Pre
```{r participant-13}
plots[["d2-013"]]["pre"]
```
#### Post
```{r participant-13-post}
plots[["d2-013"]]["post"]
```



### Participant 14
#### Pre
```{r participant-14}
plots[["d2-014"]]["pre"]
```
#### Post
```{r participant-14-post}
plots[["d2-014"]]["post"]
```



### Participant 15
#### Pre
```{r participant-15}
plots[["d2-015"]]["pre"]
```
#### Post
```{r participant-15-post}
plots[["d2-015"]]["post"]
```



### Participant 16
#### Pre
```{r participant-16}
plots[["d2-016"]]["pre"]
```
#### Post
```{r participant-16-post}
plots[["d2-016"]]["post"]
```



### Participant 17
#### Pre
```{r participant-17}
plots[["d2-017"]]["pre"]
```
#### Post
```{r participant-17-post}
plots[["d2-017"]]["post"]
```



### Participant 18
#### Pre
```{r participant-18}
plots[["d2-018"]]["pre"]
```
#### Post
```{r participant-18-post}
plots[["d2-018"]]["post"]
```



### Participant 19
#### Pre
```{r participant-19}
plots[["d2-019"]]["pre"]
```
#### Post
```{r participant-19-post}
plots[["d2-019"]]["post"]
```



### Participant 20
#### Pre
```{r participant-20}
plots[["d2-020"]]["pre"]
```
#### Post
```{r participant-20-post}
plots[["d2-020"]]["post"]
```



### Participant 21
#### Pre
```{r participant-21}
plots[["d2-021"]]["pre"]
```
#### Post
```{r participant-21-post}
plots[["d2-021"]]["post"]
```



### Participant 22
#### Pre
```{r participant-22}
plots[["d2-022"]]["pre"]
```
#### Post
```{r participant-22-post}
plots[["d2-022"]]["post"]
```



### Participant 23
#### Pre
```{r participant-23}
plots[["d2-023"]]["pre"]
```
#### Post
```{r participant-23-post}
plots[["d2-023"]]["post"]
```



### Participant 24
#### Pre
```{r participant-24}
plots[["d2-024"]]["pre"]
```
#### Post
```{r participant-24-post}
plots[["d2-024"]]["post"]
```

### Participant 25
#### Pre
```{r participant-25}
plots[["d2-025"]]["pre"]
```
#### Post
```{r participant-25-post}
plots[["d2-025"]]["post"]
```