---
title: "Avatar VR - Processing - Reaching"
author: "Joshua Bell"
format:
  html:
    toc: true
    toc-depth: 3
    toc-float: true
    toc-placement: left
---

# Package and Session Info
```{r setup-and-import}
# PPT Reaching Data -------------------------------------------------------


# Load necessary libraries ------------------------------------------------
pkgs <- c("data.table", "dplyr", "readr", "tidyfast", "stringr", "tidyr", "magrittr", "purrr", "signal", "here", "missForest", "simputation")
for (i in pkgs) {
  if (!i %in% rownames(installed.packages())) {
      install.packages(i)
      library(i, character.only = TRUE)
  } else {
      (library(i, character.only = TRUE))
  }
}
data.table::setDTthreads(percent = 90)

# Set-up: Filter specification and .csv import ----------------------------
# 10hz used for analyses
b_10hz <- butter(
  1, # order
  c(.1), # cutoff
  type = "low"
  )

# Parse data from UXF
trial_details <- list.files(
  path = here::here("data", "3_avatartooluse"),
  pattern = "trial_results.csv",
  full.names = TRUE,
  recursive = TRUE
) %>% 
  map_dfr(fread) %>%
  as.data.table()

# Manually-defined latencies
latency_fix <- read_csv(here::here("data", "study_three", "latency_fixes.csv"))
```

# Read Trial Data

```{r filter-and-import-raw}

ppt_m_files <- trial_details %>%
    dplyr::select(ppid, experiment, block_num, trial_num_in_block, manual_reach_vrpn_movement_location_0) %>%
    dplyr::filter(!is.na(manual_reach_vrpn_movement_location_0) & !manual_reach_vrpn_movement_location_0 == "") %>%
    dplyr::mutate(
        manual_reach_vrpn_movement_location_0 = fifelse(
            str_detect(manual_reach_vrpn_movement_location_0, "3_avatartooluse 1"),
            str_replace(manual_reach_vrpn_movement_location_0, "3_avatartooluse 1", "3_avatartooluse"),
            manual_reach_vrpn_movement_location_0
        )
    )

# Read in the csv files using the paths from the trial_results files and unnest those
ppt_trials_nested <- ppt_m_files %>%
    dplyr::mutate(
        manual_movement_ppt = map(
            file.path(here::here("data", manual_reach_vrpn_movement_location_0)),
            fread
        )
    ) %>%
    unnest(cols = c(manual_reach_vrpn_movement_location_0)) %>%
    as.data.table()

# Unnest again, and fix ms values that were recorded with "_"
ppt_trials_unnested <- dt_unnest(ppt_trials_nested[
    ,
    manual_movement_ppt := map(
        manual_movement_ppt,
        ~ dplyr::mutate(.x, time_ms = as.double(gsub("_", "", time_ms)))
    )
], manual_movement_ppt)

ppt_prefilter <- ppt_trials_unnested[,
    `:=`(
        time = if_else(block_num < 3, "pre", "post"),
        time_second = signif(time_ms / 1000, 6),
        time_ms = (0:(.N - 1)) * 5
    ),
    by = c(
        "ppid",
        "block_num",
        "trial_num_in_block",
        "tracked"
    )
]

```




# Position Filter

```{r buffer-and-filter-position}

# Manually impute a time_ms column that increments in steps of 5.
ppt_prefilter <- ppt_trials_unnested[,
    `:=`(
        time = if_else(block_num < 3, "pre", "post"),
        time_second = signif(time_ms / 1000, 6),
        time_ms = (0:(.N - 1)) * 5
    ),
    by = c(
        "ppid",
        "block_num",
        "trial_num_in_block",
        "tracked"
    )
][time_ms > 25]

rm(ppt_trials_unnested)

gc()

leadcols <- c("pos_x_lead", "pos_y_lead", "pos_z_lead", "time_lead")

bytrial <- c(
    "ppid",
    "block_num",
    "trial_num_in_block",
    "time",
    "tracked",
    "phase"
)

buffercols <- colnames(ppt_prefilter)
buffer_samples <- 20

# Create a buffer to reduce the distortion caused by the filtering process
# Mostly relevant for the first few participants,
# others have much more of a buffer built in to the recording.

buffer <- ppt_prefilter[,
    .(
        pos_x = c(
            seq(
                first(pos_x),
                nth(pos_x, buffer_samples - 1),
                length.out = buffer_samples
            ),
            seq(
                nth(pos_x, buffer_samples - 1),
                first(pos_x),
                length.out = buffer_samples
            )
        ),
        pos_y = c(
            seq(
                first(pos_y),
                nth(pos_y, buffer_samples - 1),
                length.out = buffer_samples
            ),
            seq(
                nth(pos_y, buffer_samples - 1),
                first(pos_y),
                length.out = buffer_samples
            )
        ),
        pos_z = c(
            seq(
                first(pos_z),
                nth(pos_z, buffer_samples),
                length.out = buffer_samples
            ),
            seq(
                nth(pos_z, buffer_samples - 1),
                first(pos_z),
                length.out = buffer_samples
            )
        ),
        time_ms = seq(
            25,
            (-5 * buffer_samples * 2) + 25,
            length.out = (buffer_samples * 2)
        ),
        phase = "buffer"
    ),
    by = c(
        "ppid",
        "block_num",
        "trial_num_in_block",
        "tracked",
        "time"
    )
]
ppt_prefilter_buffered <- merge.data.table(
    ppt_prefilter,
    buffer,
    all = TRUE
) %>% dplyr::select(!manual_reach_vrpn_movement_location_0)

# Fix ordering
ppt_prefilter_buffered <- ppt_prefilter_buffered[
    order(
        ppid,
        block_num,
        trial_num_in_block,
        tracked,
        time_ms
    )
]

# Apply Butterworth filter to position values
ppt_position_filtered <- ppt_prefilter_buffered[!(ppid %like% "pilot"), ] %>%
    dplyr::group_by(
        ppid,
        block_num,
        trial_num_in_block,
        time,
        tracked
    ) %>%
    dplyr::mutate(
        dplyr::across(
            pos_x:pos_z,
            ~ filtfilt(b_10hz, .x),
            .names = "{.col}_10hz"
        )
    ) %>%
    as.data.table()

# Pull column names from the position variables
filteredcolnames <- colnames(
    dplyr::select(
        ppt_position_filtered,
        ends_with(
            c("x", "y", "z")
        )
    )
)

cutoffs <- c(
    "raw",
    "10hz"
)

# Filter out buffer and melt the data into long format.
ppt_position_filtered_long <- ppt_position_filtered %>%
    data.table::melt(
        c(
            "ppid",
            "block_num",
            "trial_num_in_block",
            "tracked",
            "time_ms",
            "time_second",
            "time",
            "phase"
        ),
        measure.vars = patterns("^pos_x", "^pos_y", "^pos_z"),
        variable.name = "filter",
        value.name = c("pos_x", "pos_y", "pos_z")
    )

# Establish the different filters as the cutoffs.
levels(ppt_position_filtered_long$filter) <- cutoffs

bytrial_filter <- c(
    "ppid",
    "block_num",
    "trial_num_in_block",
    "time",
    "tracked",
    "filter"
)

# Save position data
fwrite(
    ppt_position_filtered_long,
    here::here(
        "data",
        "study_three",
        "ppt_position_filtered_long.csv"
    )
)
```

# Velocity calculation

```{r velocity}

ppt_velocity <- ppt_position_filtered_long[,
    # create lead columns for position and time
    c(
        "pos_x_lead",
        "pos_y_lead",
        "pos_z_lead",
        "time_ms_lead",
        "time_s_lead"
    ) := lapply(
        .SD,
        data.table::shift,
        1,
        type = "lead"
    ),
    .SDcols = c("pos_x", "pos_y", "pos_z", "time_ms", "time_second"),
    by = bytrial_filter
][,

    # create lag columns for position and time
    c(
        "pos_x_lag",
        "pos_y_lag",
        "pos_z_lag",
        "time_ms_lag",
        "time_s_lag"
    ) := lapply(.SD, data.table::shift, 1, type = "lag"),
    .SDcols = c("pos_x", "pos_y", "pos_z", "time_ms", "time_second"),

    by = bytrial_filter
][,

    `:=`(
        xdiff = (pos_x_lead - pos_x_lag),
        ydiff = (pos_y_lead - pos_y_lag),
        zdiff = (pos_z_lead - pos_z_lag),
        time_diff_ms = (time_ms_lead - time_ms_lag),
        time_diff_s = (time_s_lead - time_s_lag)
    ),
    by = bytrial_filter
][,

    # Calculate velocity in mm/s^2
    `:=`(
        velocity = fifelse(
            !is.na(time_diff_s),
            (sqrt(xdiff^2 + ydiff^2 + zdiff^2) / time_diff_s) * 1000,
            (sqrt(xdiff^2 + ydiff^2 + zdiff^2) / (time_diff_ms / 1000)) * 1000
        ),
        displacement = sqrt(pos_x^2 + pos_y^2 + pos_z^2)
    ),
    by = bytrial_filter
][,

    # Create lead column for velocity
    `:=`(
        velocity_lead = data.table::shift(velocity, 1, type = "lead"),
        velocity_lag = data.table::shift(velocity, 1, type = "lag")
    ),
    by = bytrial_filter
][,

    # Compute differences
    vel_diff := (velocity_lead - velocity_lag),
    by = bytrial_filter
][,

    # Calculate acceleration
    accel := fifelse(
        !is.na(time_diff_s),
        vel_diff / (time_diff_s),
        vel_diff / (time_diff_ms / 1000)
    ),
    by = bytrial_filter
][,

    time_ms_perphase := (
        0:(.N - 1)
    ) * 5,
    by = c(
        "ppid",
        "block_num",
        "trial_num_in_block",
        "time",
        "phase",
        "tracked",
        "filter"
    )
]

```

# Kinematic filtering

```{r kinematic-filtering}

ppt_filt <- ppt_velocity[
    order(ppid, block_num, trial_num_in_block, tracked, filter, time_ms)
][!is.na(velocity) & !is.infinite(velocity),

    # Filter velocity w/ 10hz butterworth
    `:=`(velocity_10hz = filtfilt(b_10hz, velocity)),
    by = c(
        "ppid",
        "block_num",
        "trial_num_in_block",
        "tracked",
        "filter"
    )
][,

    # Create lead column for velocity
    `:=`(
        velocity_10hzlead = data.table::shift(velocity_10hz, 1, type = "lead"),
        velocity_10hzlag = data.table::shift(velocity_10hz, 1, type = "lag")
    ),
    by = bytrial_filter
][,

    # Compute differences
    `:=`(vel_10hzdiff = (velocity_10hzlead - velocity_10hzlag)),
    by = bytrial_filter
][,

    # Compute acceleration
    accel_filtvel := fifelse(
        !is.na(time_diff_s),
        vel_10hzdiff / (time_diff_s),
        vel_10hzdiff / (time_diff_ms / 1000)
    ),
    by = bytrial_filter
][
    order(ppid, block_num, trial_num_in_block, tracked, filter, time_ms)
][
    !is.na(accel) &
        !is.na(accel_filtvel) &
        !is.infinite(accel) &
        !is.infinite(accel_filtvel),

    `:=`(
        accelfilt = filtfilt(b_10hz, accel),
        accel_filtvel_filt = filtfilt(b_10hz, accel_filtvel)
    ),
    by = c(
        "ppid",
        "block_num",
        "trial_num_in_block",
        "tracked",
        "filter"
    )
][order(ppid, block_num, trial_num_in_block, tracked, filter, time_ms)]
```

# Movement Onset

```{r movement-onset}
# Write full data for plotting individual trials/visual quality checks.
ppt_filt_ <- ppt_filt[
    phase != "buffer" &
        filter == "10hz" &
        tracked == "Wrist" &
        # Remove cases that would break analyses-
        # these are at the ends of the movement when the markers are hopping around.
        !is.infinite(velocity_10hz) &
        !is.infinite(accel) &
        !is.infinite(accel_filtvel),
    .(
        ppid,
        time, block_num,
        trial_num_in_block, phase,
        time_ms, time_ms_perphase,
        velocity, velocity_10hz,
        accel, accelfilt, accel_filtvel,
        accel_filtvel_filt
    )
]

ppt_filt_latfix <- merge(
    ppt_filt_,
    latency_fix,
    by = c(
        "ppid",
        "trial_num_in_block",
        "time"
    ),
    all.x = TRUE
) %>%
    dplyr::mutate(
        start_time = fifelse(!is.na(start_time), start_time, 0),
        time_ms_fix = time_ms - start_time
    ) %>%
    arrange(
        ppid,
        time,
        trial_num_in_block,
        time_ms
    ) %>%
    as.data.table()


# Set start time as the first sample where velocity increases
# by 25 over the subsequent 10 samples. When a manual start
# time is specified, use that instead.

ppt_filt_latfix[
    ,
    leadvel := lead(velocity_10hz, 10),
    by = c("ppid", "trial_num_in_block", "time")
][
    ,
    dif := leadvel - velocity_10hz
][,
    `:=`(
        start_time = fifelse(
            start_time != 0, start_time,
            .SD[
                (!phase %in% c("replace", "return", "returned")) &
                    dif > 25
            ]$time_ms[1]
        )
    ),
    by = c(
        "ppid",
        "trial_num_in_block",
        "time"
    )
][
    ,
    `:=`(
        order = fcase(
            block_num < 3, "pre",
            block_num == 4, "first",
            block_num == 5, "second",
            default = "NA"
        )
    )
]

# Merge with manually-identified start points

time_correction <- ppt_filt_latfix[,
    time_ms_fix := time_ms - start_time,
    by = c(
        "ppid",
        "trial_num_in_block",
        "time"
    )
] %>%
    arrange(ppid, time, trial_num_in_block, time_ms)

fwrite(time_correction, here::here("data", "study_three", "ppt_m_fulltrials.csv"))

start_times <- time_correction[, .(start_time = median(start_time)), by = c("ppid", "trial_num_in_block", "time")]

start_times %>%
    fwrite(here::here("data", "study_three", "ppt_start_times.csv"))


# Manual data fixes/filters
ppt_m <- time_correction[
    # Only beginning and out phases, 10hz filter. Remove values that would break an analysis.
    (phase %in% c("start", "begin", "out") |
        (phase == "lift" & time_ms_perphase < 100)) &
        !is.infinite(velocity) &
        !is.infinite(accel) &
        !is.infinite(accel_filtvel) &
        time_ms_fix >= 0
][
    ,
    .(
        ppid, time, phase,
        block_num, trial_num_in_block, order,
        time_ms_perphase, time_ms, time_ms_fix,
        velocity, velocity_10hz,
        accel, accelfilt, accel_filtvel,
        accel_filtvel_filt
    )
]

```

# Individualized Adjustments

The below code lays out the individualized adjustments made to ensure the correct peaks and latencies are chosen for each participant. To see the consequences of these choices, see the individual trial plots in 01a_reaching_trials.qmd.

```{r individual-adjustments}
ppt_m_ <- ppt_m[
    !(ppid == "d3-011" & trial_num_in_block == 8 & time == "pre" & time_ms_fix > 800) &
    !(ppid == "d3-016" & trial_num_in_block == 17 & time == "post" & time_ms_fix > 800) &
    !(ppid == "d3-020" & trial_num_in_block > 4 & time == "post" & time_ms_fix > 750) &
    !(ppid == "d3-022" & trial_num_in_block %in% c(8,10,18) & time == "post" & time_ms_fix > 600)
][,
    # Compute kinematic peaks and latencies
    # Fcase (fast case-when) used to specify individual adjustments
    # When a parameter is not salvageable, it is set to 0 and filtered out after this step
    # due to fcase's constraint that all output values must share type.
    # Kinematic value calculations not used in the final analysis are commented out.
    .(
        # Filtered peaks (10hz butterworth)
        vel_m_filt = max(velocity_10hz, na.rm = TRUE),
        # Filtered latencies
        vel_lat_filt = .SD[
            which.max(velocity_10hz),
            time_ms_fix
        ][1],
        # Peak Accel
        acc_m_filtfilt = max(accel_filtvel_filt, na.rm = TRUE),

        # Peak Decel
        dec_m_filtfilt =
            fcase(
                (ppid == "d3-004" &
                    trial_num_in_block %in% c(1, 2) &
                    time == "post"),
                min(
                    ppt_m[
                        ppid == "d3-004" &
                            trial_num_in_block %in% c(1, 2) &
                            time == "post" &
                            time_ms_fix < 1100,
                        accel_filtvel_filt
                    ],
                    na.rm = TRUE
                ),
                default = min(accel_filtvel_filt, na.rm = TRUE)
            ),

        # Acc/Dec peaks & Latencies when calculated from filtered velocity and filtered again
        # which.max and which.min used to find index of peak and extract the time_ms_fix value
        # Peak Accel Latency
        acc_lat_filtfilt = .SD[which.max(accel_filtvel_filt), time_ms_fix][1],

        # Peak Decel Latency
        dec_lat_filtfilt = fcase(
            (ppid == "d3-004" &
                trial_num_in_block %in% c(1, 2) &
                time == "post"),
            ppt_m[
                ppid == "d3-004" &
                    trial_num_in_block %in% c(1, 2) &
                    time == "post" &
                    time_ms_fix < 1100
            ][
                which.min(accel_filtvel_filt),
                time_ms_fix,
            ][1],
            default = .SD[
                which.min(accel_filtvel_filt),
                time_ms_fix
            ][1]
        )
    ),
    by = c(
        "ppid",
        "trial_num_in_block",
        "order",
        "time"
    )
]

ppt_adjusted <- ppt_m_[
    ,
    `:=`(
        vel_m_filt = ifelse(
            vel_m_filt == 0,
            NA,
            vel_m_filt
        ),
        acc_m_filtfilt = ifelse(
            acc_m_filtfilt == 0,
            NA,
            acc_m_filtfilt
        ),
        dec_m_filtfilt = ifelse(
            dec_m_filtfilt == 0,
            NA,
            dec_m_filtfilt
        ),
        vel_lat_filt = ifelse(
            vel_lat_filt == 0,
            NA,
            vel_lat_filt
        ),
        acc_lat_filtfilt = ifelse(
            acc_lat_filtfilt == 0,
            NA,
            acc_lat_filtfilt
        ),
        dec_lat_filtfilt = ifelse(
            dec_lat_filtfilt == 0,
            NA,
            dec_lat_filtfilt
        )
    )
]


test <- ppt_adjusted[dec_lat_filtfilt < acc_lat_filtfilt |
    dec_lat_filtfilt < vel_lat_filt |
    acc_lat_filtfilt > vel_lat_filt]

test

fwrite(ppt_adjusted, here::here("data", "study_three", "ppt_manual_pre_cleaning.csv"))

```






# Read OpenVR Data
As a backup to PPT

```{r read-openvr}
# openvr_m_files <- trial_details %>%
#     dplyr::select(ppid, experiment, block_num, trial_num_in_block, manual_reach_openvr_movement_steamvr_location_0) %>%
#     dplyr::filter(
#         !is.na(manual_reach_openvr_movement_steamvr_location_0) & !manual_reach_openvr_movement_steamvr_location_0 == ""
#     )

# # Read in the csv files using the paths from the trial_results files and unnest those
# openvr_trials_nested <- openvr_m_files %>%
#     dplyr::mutate(
#         manual_movement_openvr = map(
#             file.path(here::here("data", manual_reach_openvr_movement_steamvr_location_0)),
#             fread
#         )
#     ) %>%
#     unnest(cols = c(manual_reach_openvr_movement_steamvr_location_0)) %>%
#     as.data.table()

# # Unnest again, and fix ms values that were recorded with "_"
# openvr_trials_unnested <- dt_unnest(openvr_trials_nested[
#     ,
#     manual_movement_openvr := map(
#         manual_movement_openvr,
#         ~ dplyr::mutate(.x, time_ms = as.double(gsub("_", "", time_ms)))
#     )
# ], manual_movement_openvr)

# openvr_prefilter <- openvr_trials_unnested[,
#     `:=`(
#         time = if_else(block_num < 3, "pre", "post"),
#         time_second = signif(time_ms / 1000, 6),
#         time_ms = (0:(.N - 1)) * 5
#     ),
#     by = c(
#         "ppid",
#         "block_num",
#         "trial_num_in_block",
#         "tracked"
#     )
#]
```