---
title: "Avatar VR - Descriptive Analyses"
author: "Joshua Bell"
format:
  html:
    toc: true
    toc-depth: 3
    toc-float: true
    toc-placement: left
---
# Imports

```{r packages-import, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.align = "center", fig.width = 12, fig.height = 6)

pkgs <- c("dplyr", "tidyr", "magrittr", "readr", "data.table", "here", "ggplot2", "gghalves", "ggthemes", "tidybayes", "patchwork", "datawizard", "flextable")
for(i in pkgs){
  if(!i %in% rownames(installed.packages())){ 
    install.packages(i) 
    library(i, character.only = TRUE)
  }
  else(library(i, character.only = TRUE))
}

annotate_npc <- function(label, x, y, ...)
{
  ggplot2::annotation_custom(grid::textGrob(
    x = unit(x, "npc"), y = unit(y, "npc"), label = label, gp = grid::gpar(fontsize = 20), ...))
}
# Function to create raincloud plots 8=using ggplot2, ggdist/tidybayes stats
raincloud_plot <- function(dataframe, variable)
{
  plot_data = dataframe
  plot_data %>%
  ggplot() +
  aes(
    x = {{variable}}
  ) +
  stat_slab(
    side = "top",
    fill = "#09A1D7"
  ) +
  stat_dots(
    side = "bottom",
    dotsize = .9,
    fill = "#09A1D7",
    color = "#09A1D7"
  ) +
  stat_pointinterval(
    point_interval = mode_hdi
  ) +
  theme_tidybayes()
}

ppt_m <- read_csv(
  here::here("data", "study_three", "ppt_manual.csv")) %>% 
  as.data.table() %>%
      mutate(time = factor(
          x = time,
          levels = c("pre", "post"),
          labels = c("Pre", "Post")
      ))

# steamvr_participants <- c("d3-006", "d3-007", "d3-012", "d3-024")

# steamvr_m <- fread(here::here("data", "study_three", "steamvr_manual.csv")) %>%
# # Use OpenVR data for participants whose VRPN data is missing
#     dplyr::filter(ppid %in% steamvr_participants) %>%
#     mutate(
#         vel_m_filt = ovr_vel_m_filt,
#         vel_lat_filt = ovr_vel_lat_filt,
#         acc_m_filtfilt = ovr_acc_m_filtfilt,
#         acc_lat_filtfilt = ovr_acc_lat_filtfilt,
#         dec_m_filtfilt = ovr_dec_m_filtfilt,
#         dec_lat_filtfilt = ovr_dec_lat_filtfilt,
#     ) %>%
#     dplyr::select(
#         ppid,
#         time,
#         trial_num_in_block,
#         vel_m_filt,
#         vel_lat_filt,
#         acc_m_filtfilt,
#         acc_lat_filtfilt,
#         dec_m_filtfilt,
#         dec_lat_filtfilt
#     )

# ppt_m <- bind_rows(ppt_m[!ppid %in% steamvr_participants], steamvr_m) %>%
#     mutate(time = factor(
#         x = time,
#         levels = c("pre", "post"),
#         labels = c("Pre", "Post")
#     ))

landmark <- read_csv(
  here::here("data", "study_three", "landmark.csv")) %>%
  select(
    ppid, 
    trial, 
    time, 
    forearmlength, 
    target,
    error,
    lapse_fix_target, 
    lapse_fix_error
  ) %>%
  mutate(
    error_std = standardize(
      error
      ),
    lapse_fix_error_std = standardize(
      lapse_fix_error
      ),
    target = factor(
      target,
      levels = c("Elbow", "Forearm", "Wrist")),
    lapse_fix_target = factor(
      lapse_fix_target,
      levels = c("Elbow", "Forearm", "Wrist")),
    error_cm = error * 100,
    lapse_fix_error = lapse_fix_error * 100,
    time = factor(
      time,
      levels = c("pre", "post"),
      labels= c("Pre", "Post"))) %>%
  as.data.table()

```

# Landmark Task

## Empirical Distributions

### Error (in cm)

#### By Target

```{r}
(landmark_raincloud <- landmark %>% 
  raincloud_plot(variable = error_cm) +
  facet_wrap(~target, ncol = 1))
```

### By Time

```{r}
(landmark_raincloud <- landmark %>% 
  raincloud_plot(variable = error_cm) +
  facet_wrap(~time, ncol = 1))
```

#### Time x Target

```{r landmark-empirical-plot}
lm_empirical <- landmark %>%
ggplot(aes(y = error_cm,
  x = time,
  fill = time,
  color = time)) + 
  stat_pointinterval(data = landmark[time == "Post"],
                     point_interval = mean_qi, 
                     show_slab = FALSE, 
                     position = position_nudge(x = -.45)) +
  stat_pointinterval(data = landmark[time == "Pre"],
                   point_interval = mean_qi, 
                   show_slab = FALSE, 
                   position = position_nudge(x = .45)) +
  geom_half_point(data = landmark[time == "Post"], 
                  side = "r", 
                  range_scale = .5,
                  alpha = .6) +
  geom_half_point(data = landmark[time == "Pre"],
                  side = "l", 
                  range_scale = .5,
                  alpha = .6) +
  stat_slab(data = landmark[time == "Post"],
            alpha = .8, 
            scale = .4,
            side = "left") +  
  stat_slab(data = landmark[time == "Pre"],
            alpha = .8, 
            scale = .4, 
            side = "right") +
  geom_hline(yintercept = 0, linetype = "longdash", color = "black", alpha = .8) +
  facet_wrap(~target)+
  theme_tidybayes() +
  scale_x_discrete(limits = c("Pre", "Post"),
                   expand = c(0, 0),
                   labels = c("Pre", "Post"))+
  scale_y_continuous(limits = c(-35, 35), expand = c(0, 0), breaks = seq(-20, 20, 5)) +
  scale_fill_manual(breaks = c("Pre", "Post"),
    values = c("#001015", "#09A1D7"),
    labels = c("Pre", "Post")) +
  scale_color_manual(breaks = c("Pre", "Post"),
    values = c("#001015", "#09A1D7"),
    labels = c("Pre", "Post")) +
  labs(y = "Error (cm)", x = "Time", fill = "Time", color = "Time", title = "Body Landmark Task Response Distributions") +
  theme(axis.text.y = element_text(hjust = 0),
        title = element_text(size = 14),
        text = element_text(size = 16, color = "black"),
        strip.background = element_blank(),
        strip.placement = "inside",
        strip.switch.pad.wrap = unit(0, "in"),
        panel.background = element_rect(fill = "transparent", colour = NA), 
        legend.background = element_rect(fill = "transparent", colour = NA),  
        plot.background = element_rect(fill = "transparent", colour = NA))

ggsave(lm_empirical, filename = here::here("scripts", "for_osf", "tooluse_avatar",  "figures", "landmark-empirical-plot.svg"), width = 15, height = 8)
saveRDS(lm_empirical, here::here("scripts", "for_osf", "tooluse_avatar",  "figures", "landmark-empirical-plot.rds"))

lm_empirical
```

```{r landmark-empirical-table}
#| tbl-cap: Body landmark task error by time and target

bind_rows(
landmark %>%
  group_by(target, time) %>%
  summarise(mean = mean(error_cm),
            mean_lapse_fix = mean(lapse_fix_error),
            sd = sd(error_cm),
            n = n()),
landmark %>%
  group_by(target) %>%
  summarise(mean = mean(error_cm),
            mean_lapse_fix = mean(lapse_fix_error),
            sd = sd(error_cm),
            n = n()) %>%
  mutate(
    time = "Overall"
  )
) %>%
mutate(
  time = factor(time,
                levels = c("Overall", "Pre", "Post")),
) %>%
arrange(time, target) %>%
  flextable::flextable()

```

# Reaching Task

## Empirical Distributions

### Overall
Intervals are 95% HDI, point estimates are the MAP.

```{r reaching-empirical-plot}



# A raincloud plot for each of the kinematic peaks and latencies, using ggdist's stat_slab and stat_dotplot.
velocity_raincloud <- ppt_m %>% 
  raincloud_plot(vel_m_filt)

acceleration_raincloud <- ppt_m %>% 
  raincloud_plot(acc_m_filtfilt)

deceleration_raincloud <- ppt_m %>% 
  raincloud_plot(dec_m_filtfilt)

velocity_latency_raincloud <- ppt_m %>% 
  raincloud_plot(vel_lat_filt)

acceleration_latency_raincloud <- ppt_m %>% 
  raincloud_plot(acc_lat_filtfilt)

deceleration_latency_raincloud <- ppt_m %>%
  raincloud_plot(dec_lat_filtfilt)

```

##### Velocity

```{r velocity_raincloud, echo = FALSE, fig.cap = "Velocity Raincloud Plot"}
velocity_raincloud
```

##### Acceleration

```{r acceleration_raincloud, echo = FALSE, fig.cap = "Acceleration Raincloud Plot"}
acceleration_raincloud
```

##### Deceleration
 
```{r deceleration_raincloud, echo = FALSE, fig.cap = "Deceleration Raincloud Plot"}
deceleration_raincloud
```

#### Latencies

##### Velocity

```{r velocity_latency_raincloud, echo = FALSE, fig.cap = "Velocity Latency Raincloud Plot"}
velocity_latency_raincloud
```

##### Acceleration

```{r acceleration_latency_raincloud, echo = FALSE, fig.cap = "Acceleration Latency Raincloud Plot"}
acceleration_latency_raincloud
```

##### Deceleration

```{r deceleration_latency_raincloud, echo = FALSE, fig.cap = "Deceleration Latency Raincloud Plot"}
deceleration_latency_raincloud
```


### By Time
```{r kinematics-empirical-plots}
pptvel_dist <- ggplot(ppt_m, 
                      aes(x = vel_m_filt, 
                          fill = time, 
                          color = time)) + 
  stat_dots(alpha = .7) +
  stat_pointinterval(data = ppt_m[time == "Post"], 
                     point_interval = mode_hdi, show_slab = FALSE, 
                     position = position_nudge(y = -.043)) +
  stat_pointinterval(data = ppt_m[time == "Pre"], 
                     point_interval = mode_hdi, 
                     show_slab = FALSE, 
                     position = position_nudge(y = -.01)) +
  labs(x = "Peak Velocity (mm/s)", 
       fill = "Time", 
       color = "Time",
       y = NULL) +
  scale_fill_manual(values = c("#001015", "#09A1D7")) +
  scale_color_manual(values = c("#001015", "#09A1D7")) +
  theme_tidybayes() +
  theme(text = element_text(size = 14)) +
  scale_y_continuous(limits = c(-.05, 1)) +
  scale_x_continuous(breaks = c(450, 900, 1350)) +
  theme(axis.line.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.text.y = element_blank(),
        panel.background = element_rect(fill = "transparent", colour = NA), 
        legend.background = element_rect(fill = "transparent", colour = NA),  
        plot.background = element_rect(fill = "transparent", colour = NA))

pptacc_dist <- ggplot(ppt_m, 
                      aes(x = acc_m_filtfilt, 
                          fill = time, 
                          color = time)) + 
  stat_dots(alpha = .7) +
  stat_pointinterval(data = ppt_m[time == "Post"], 
                     point_interval = mode_hdi, 
                     show_slab = FALSE, 
                     position = position_nudge(y = -.043)) +
  stat_pointinterval(data = ppt_m[time == "Pre"], 
                     point_interval = mode_hdi, 
                     show_slab = FALSE, 
                     position = position_nudge(y = -.01) ) +
  labs(x = expression("Peak Acceleration "(mm/s^2)), 
       fill = "Time", 
       color = "Time",
       y = NULL) +
  scale_fill_manual(values = c("#001015", "#09A1D7")) +
  scale_color_manual(values = c("#001015", "#09A1D7")) +
  theme_tidybayes() +
  theme(text = element_text(size = 14)) +
  scale_y_continuous(limits = c(-.05, 1)) +
  theme(axis.line.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.text.y = element_blank(),
        panel.background = element_rect(fill = "transparent", colour = NA), 
        legend.background = element_rect(fill = "transparent", colour = NA),  
        plot.background = element_rect(fill = "transparent", colour = NA))

pptdec_dist <- ggplot(ppt_m, 
                      aes(x = -dec_m_filtfilt, 
                          fill = time, 
                          color = time)) + 
stat_dots(alpha = .7) +
  stat_pointinterval(data = ppt_m[time == "Post"], 
                     point_interval = mode_hdi, 
                     show_slab = FALSE, 
                     position = position_nudge(y = -.043)) +
  stat_pointinterval(data = ppt_m[time == "Pre"], 
                     point_interval = mode_hdi, 
                     show_slab = FALSE, 
                     position = position_nudge(y = -.01)) +
  labs(x = expression("Peak Deceleration "(mm/s^2)), 
       fill = "Time", 
       color = "Time",
       y = NULL) +
  scale_fill_manual(values = c("#001015", "#09A1D7")) +
  scale_color_manual(values = c("#001015", "#09A1D7")) +
  theme_tidybayes() +
  theme(text = element_text(size = 14)) +
  scale_x_continuous(breaks = c(0, 2500, 5000, 7500, 10000), labels = c("0", "-2500", "-5000", "-7500", "-10000")) +
  scale_y_continuous(limits = c(-.05, 1)) +
  theme(axis.line.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.text.y = element_blank(),
        panel.background = element_rect(fill = "transparent", colour = NA), 
        legend.background = element_rect(fill = "transparent", colour = NA),  
        plot.background = element_rect(fill = "transparent", colour = NA))

pptvel_lat_dist <- ggplot(ppt_m, 
                          aes(x = vel_lat_filt,
                              fill = time, 
                              color = time)) + 
  stat_dots(alpha = .7) +
  stat_pointinterval(data = ppt_m[time == "Post"], 
                     point_interval = mode_hdi, show_slab = FALSE, 
                     position = position_nudge(y = -.043)) +
  stat_pointinterval(data = ppt_m[time == "Pre"], 
                     point_interval = mode_hdi, 
                     show_slab = FALSE, 
                     position = position_nudge(y = -.01) ) +
  labs(x = "Peak Velocity Latency (ms)", 
       fill = "Time", 
       color = "Time",
       y = NULL) +
  scale_fill_manual(values = c("#001015", "#09A1D7")) +
  scale_color_manual(values = c("#001015", "#09A1D7")) +
  theme_tidybayes() +
  theme(text = element_text(size = 14)) +
  scale_y_continuous(limits = c(-.05, 1)) +
  scale_x_continuous(limits = c(0, max(ppt_m[, vel_lat_filt]))) +
  theme(axis.line.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.text.y = element_blank(),
        panel.background = element_rect(fill = "transparent", colour = NA), 
        legend.background = element_rect(fill = "transparent", colour = NA),  
        plot.background = element_rect(fill = "transparent", colour = NA))

pptacc_lat_dist <- ggplot(
  ppt_m,
  aes(
    x = acc_lat_filtfilt, 
    fill = time, 
    color = time
    )
  ) + 
  stat_dots(alpha = .7) +
  stat_pointinterval(data = ppt_m[time == "Post"], 
                     point_interval = mode_hdi, show_slab = FALSE, 
                     position = position_nudge(y = -.043)) +
  stat_pointinterval(data = ppt_m[time == "Pre"], 
                     point_interval = mode_hdi, 
                     show_slab = FALSE, 
                     position = position_nudge(y = -.01) ) +
  labs(x = "Peak Acceleration Latency (ms)", 
       fill = "Time", 
       color = "Time",
       y = NULL) +
  scale_fill_manual(values = c("#001015", "#09A1D7")) +
  scale_color_manual(values = c("#001015", "#09A1D7")) +
  theme_tidybayes() +
  theme(text = element_text(size = 14)) +
  scale_y_continuous(limits = c(-.05, 1)) +
  scale_x_continuous(limits = c(0, max(ppt_m[, acc_lat_filtfilt]))) +
  theme(axis.line.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.text.y = element_blank(),
        panel.background = element_rect(fill = "transparent", colour = NA), 
        legend.background = element_rect(fill = "transparent", colour = NA),  
        plot.background = element_rect(fill = "transparent", colour = NA))

pptdec_lat_dist <- ggplot(
  ppt_m,
  aes(
    x = dec_lat_filtfilt, 
    fill = time, 
    color = time
    )
  ) + 
  stat_dots(alpha = .7) +
  stat_pointinterval(data = ppt_m[time == "Post"], 
                     point_interval = mode_hdi, show_slab = FALSE, 
                     position = position_nudge(y = -.043)) +
  stat_pointinterval(data = ppt_m[time == "Pre"], 
                     point_interval = mode_hdi, 
                     show_slab = FALSE, 
                     position = position_nudge(y = -.01) )+
  labs(x = "Peak Deceleration Latency (ms)", 
       fill = "Time", 
       color = "Time",
       y = NULL) +
  scale_fill_manual(values = c("#001015", "#09A1D7")) +
  scale_color_manual(values = c("#001015", "#09A1D7")) +
  theme_tidybayes() +
  theme(text = element_text(size = 14)) +
  scale_y_continuous(limits = c(-.05, 1)) +
  scale_x_continuous(limits = c(0, max(ppt_m[, dec_lat_filtfilt]))) +
  theme(axis.line.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.text.y = element_blank(),
        panel.background = element_rect(fill = "transparent", colour = NA), 
        legend.background = element_rect(fill = "transparent", colour = NA),  
        plot.background = element_rect(fill = "transparent", colour = NA))

kinematic_empirical_plots <- 
(
  pptacc_dist +  pptvel_dist + pptdec_dist + 
  pptacc_lat_dist + pptvel_lat_dist + pptdec_lat_dist
  ) + plot_layout(
    guides = "collect", 
    nrow = 2, 
    ncol = 3
    ) + patchwork::plot_annotation(
      title = "Kinematic peak and latency empirical distributions"
      ) & theme(
        plot.title = element_text(size = 14),
        panel.background = element_rect(fill = "transparent", colour = NA), 
        legend.background = element_rect(fill = "transparent", colour = NA),  
        plot.background = element_rect(fill = "transparent", colour = NA)
      )

ggsave(kinematic_empirical_plots, filename = here::here("scripts", "for_osf", "tooluse_avatar", "figures", "kinematics-empirical-plot.svg"), width = 18, height = 12, bg = "transparent")
saveRDS(kinematic_empirical_plots, here::here("scripts", "for_osf", "tooluse_avatar", "figures", "kinematics-empirical-plot.rds"))

kinematic_empirical_plots
```

```{r empirical-kinematics-table}

bind_rows(
ppt_m %>%
group_by(time) %>%
summarise(
  acc = mean(acc_m_filtfilt),
  vel = mean(vel_m_filt),
  dec = mean(dec_m_filtfilt),
  acc_lat = mean(acc_lat_filtfilt),
  vel_lat = mean(vel_lat_filt),
  dec_lat = mean(dec_lat_filtfilt)
),
ppt_m %>%
summarise(
  acc = mean(acc_m_filtfilt),
  vel = mean(vel_m_filt),
  dec = mean(dec_m_filtfilt),
  acc_lat = mean(acc_lat_filtfilt),
  vel_lat = mean(vel_lat_filt),
  dec_lat = mean(dec_lat_filtfilt)
) %>%
mutate(
  time = "Overall"
)
) %>%
flextable::flextable()
```

## Over trials

```{r}

average_bytrial <- ppt_m %>% group_by(trial_num_in_block, time) %>%
  dplyr::summarise(vel_m_filt = mean(vel_m_filt))

pptvel_dist <- ggplot(ppt_m, 
                      aes(y = vel_m_filt,
                          x = fifelse(time == "Post", trial_num_in_block + 18, trial_num_in_block), 
                          fill = time, 
                          color = time)) + 
  stat_dots(alpha = .7) +
  geom_line(data = average_bytrial,
    aes(y = vel_m_filt,
                group = time))+
  labs(x = "Trial", 
       fill = "Time", 
       color = "Time",
       y = "Peak Velocity (mm/s)") +
  scale_fill_manual(values = c("#001015", "#09A1D7")) +
  scale_color_manual(values = c("#001015", "#09A1D7")) +
  theme_tidybayes() +
  theme(text = element_text(size = 14)) +
  scale_y_continuous(breaks = c(450, 900, 1350)) +
  theme(axis.line.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.text.y = element_blank(),
        panel.background = element_rect(fill = "transparent", colour = NA), 
        legend.background = element_rect(fill = "transparent", colour = NA),  
        plot.background = element_rect(fill = "transparent", colour = NA))

pptvel_dist
```

# By-participant Kinematic Changes

## Table
```{r }
# Compute change scores by casting ppt_m to wide format and computing the difference between pre and post for each kinematic variable
change <- ppt_m %>%
pivot_wider(
  id_cols = c(ppid, trial_num_in_block),
  names_from = time,
  values_from = c(
    vel_m_filt,
    acc_m_filtfilt,
    dec_m_filtfilt,
    vel_lat_filt,
    acc_lat_filtfilt,
    dec_lat_filtfilt
    )
    ) %>%
  dplyr::group_by(ppid) %>%
  dplyr::summarise(
    vel_change = round(
      mean(vel_m_filt_Post) - mean(vel_m_filt_Pre), 
      2
      ),
    acc_change = round(
      mean(acc_m_filtfilt_Post) - mean(acc_m_filtfilt_Pre),
      2
      ),
    dec_change = round(
      mean(dec_m_filtfilt_Post) - mean(dec_m_filtfilt_Pre),
      2
      ),
    vel_lat_change = round(
      mean(vel_lat_filt_Post) - mean(vel_lat_filt_Pre),
      2
      ),
    acc_lat_change = round(
      mean(acc_lat_filtfilt_Post) - mean(acc_lat_filtfilt_Pre),
      2
      ),
    dec_lat_change = round(
      mean(dec_lat_filtfilt_Post) - mean(dec_lat_filtfilt_Pre),
      2
      )
  ) %>% as.data.table()

change[order(vel_change)]

fwrite(change, here::here("scripts", "for_osf", "tooluse_avatar", "figures", "kinematic_change.csv"), sep = ",", row.names = FALSE)
```

## Plots

```{r}

# Plot change scores
velocity_change <- change %>%
  raincloud_plot(vel_change) +
  geom_vline(xintercept = 0, linetype = "dashed")

acceleration_change <- change %>%
  raincloud_plot(acc_change) +
  geom_vline(xintercept = 0, linetype = "dashed")

deceleration_change <- change %>%
  raincloud_plot(dec_change) +
  geom_vline(xintercept = 0, linetype = "dashed")

velocity_lat_change <- change %>%
  raincloud_plot(vel_lat_change) +
  geom_vline(xintercept = 0, linetype = "dashed")

acceleration_lat_change <- change %>%
  raincloud_plot(acc_lat_change) +
  geom_vline(xintercept = 0, linetype = "dashed")

deceleration_lat_change <- change %>%
  raincloud_plot(dec_lat_change) +
  geom_vline(xintercept = 0, linetype = "dashed")

```

### Peaks
#### Velocity

```{r}
velocity_change
```

#### Acceleration

```{r}
acceleration_change
```

#### Deceleration

```{r}
deceleration_change
```

### Latencies
#### Velocity

```{r}
velocity_lat_change
```

#### Acceleration

```{r}
acceleration_lat_change
```

#### Deceleration

```{r}
deceleration_lat_change
```

# By-participant Landmark Changes

## Table

```{r}

# Compute change scores by casting landmark to wide format and computing the difference between error at pre and post for each target landmark

landmark_change <- landmark %>%
  pivot_wider(
    id_cols = c(ppid, trial, target),
    names_from = time,
    values_from = c(
      error_cm
    )
  ) %>%
  dplyr::group_by(ppid, target) %>%
  dplyr::summarise(
    error_change = round(
      mean(Post, na.rm = TRUE) - mean(Pre, na.rm = TRUE),
      2
    )
  ) %>% as.data.table()

wrist_change <- landmark_change %>%
  filter(target == "Wrist") %>%
  raincloud_plot(error_change)
```

# Session Info

```{r}
sessioninfo::package_info()
```