---
title: "Avatar VR - Supplementary Analyses - Reaching"
author: "Joshua Bell"
date: "10/14/2022"
format:
  html:
    toc: true
    toc-depth: 3
    toc-float: true
    toc-placement: left
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      cache = TRUE, 
                      fig.width = 12, 
                      fig.height = 8)
pkgs <- c("dplyr", "readr", "magrittr", "data.table", "here", "brms", "cmdstanr", "datawizard", "bayestestR", "flextable", "ggplot2", "tidybayes")
for(i in pkgs){
  if(!i %in% rownames(installed.packages())){ 
    install.packages(i) 
    library(i, character.only = TRUE)
  }
  else(library(i, character.only = TRUE))
}

options("mc.cores" = parallel::detectCores(), "brms.backend" = "cmdstan")
control_list = list(adapt_delta = .99, max_treedepth = 15)

b = 4000/parallel::detectCores()
i = 48000/parallel::detectCores()
ch = parallel::detectCores()
co = parallel::detectCores()
```

```{r import-standardize, include=FALSE}

ppt_m <- fread(
  here::here("data", "study_three", "ppt_manual.csv")
)  %>%
      mutate(
          time = factor(
              x = time,
              levels = c("pre", "post"), labels = c("Pre", "Post"),
          ),
      overall_trial = fcase(time == "Pre", trial_num_in_block,
                            time == "Post", as.integer(trial_num_in_block + 18))
            )



ppt_m_std <- ppt_m %>% 
  mutate(vel_m_filt_std = standardize(vel_m_filt),
          dec_m_filtfilt_std = standardize(dec_m_filtfilt),
          acc_m_filtfilt_std = standardize(acc_m_filtfilt),
          vel_lat_filt_std = standardize(vel_lat_filt),
          acc_lat_filtfilt_std = standardize(acc_lat_filtfilt),
          dec_lat_filtfilt_std = standardize(dec_lat_filtfilt)) %>%
  as.data.table()

landmark <- read_csv(here::here("data", "study_three", "landmark.csv")) %>%
    mutate(error_std = standardize(lapse_fix_error),
         target = factor(lapse_fix_target,
            levels = c("Elbow", "Forearm", "Wrist")),
         error_cm = lapse_fix_error * 100,
         forearmlength = forearmlength * 100,
         forearmlength_std = standardize(forearmlength),
         time = factor(time,
            levels = c("pre", "post"),
            labels= c("Pre", "Post")),
         order = factor(x = order, levels = c("pre", "first", "second"),
            labels = c("Pre", "First", "Second"))) %>%
            as.data.table()

participant_info <- fread(here::here("data", "study_three", "participant_info_coded.csv"))

participant_info_and_kinematics <- ppt_m %>%
    left_join(participant_info, by = "ppid")

```

# Supplemental Analyses

## Reaching Task

### Bongers (2010) Replication
In Bongers's (2010) study, no effect of tool-use on kinematics was observed when considering the full block of trials in the post-test. He did, however, observe an effect when comparing a subset of trials: Those immediately after the tool-use block.


#### Is this influenced by order?

```{r}
order_plot_data <- ppt_m %>%
dplyr::filter(
  overall_trial > 18,
  order != "Pre") %>%
mutate(order = factor(
  order,
  levels = c("first", "second"),
  labels = c("First", "Second"))) %>%
group_by(
  overall_trial,
  order) %>% 
dplyr::summarise(
  m_vel = mean(vel_m_filt, na.rm = TRUE), 
  m_acc = mean(acc_m_filtfilt, na.rm = TRUE), 
  m_dec = mean(dec_m_filtfilt, na.rm = TRUE),
  lat_vel = mean(vel_lat_filt, na.rm = TRUE),
  lat_acc = mean(acc_lat_filtfilt, na.rm = TRUE),
  lat_dec = mean(dec_lat_filtfilt, na.rm = TRUE)
  ) 

order_plot_data %>%
ggplot(
  aes(x = overall_trial,
  y = m_vel,
  color = order)) +
  geom_line(size = 2) +
  theme_tidybayes() +
  labs(x = "Trial", y = "Peak Velocity") +
  scale_color_manual(
    breaks = c("First", "Second"),
    values = c("#001015", "#09A1D7"),
    labels = c("First", "Second")
  )

order_plot_data %>%
ggplot(
  aes(x = overall_trial,
  y = m_acc,
  color = order)) +
  geom_line(size = 2) +
  theme_tidybayes() +
  labs(x = "Trial", y = "Peak Acceleration") +
  scale_color_manual(
    breaks = c("First", "Second"),
    values = c("#001015", "#09A1D7"),
    labels = c("First", "Second")
  )

order_plot_data %>%
ggplot(
  aes(x = overall_trial,
  y = m_dec,
  color = order)) +
  geom_line(size = 2) +
  theme_tidybayes() +
  labs(x = "Trial", y = "Peak Deceleration") +
  scale_color_manual(
    breaks = c("First", "Second"),
    values = c("#001015", "#09A1D7"),
    labels = c("First", "Second")
  )

order_plot_data %>%
ggplot(
  aes(x = overall_trial,
  y = lat_vel,
  color = order)) +
  geom_line(size = 2) +
  theme_tidybayes() +
  labs(x = "Trial", y = "Velocity Latency") +
  scale_color_manual(
    breaks = c("First", "Second"),
    values = c("#001015", "#09A1D7"),
    labels = c("First", "Second")
  )

order_plot_data %>%
ggplot(
  aes(x = overall_trial,
  y = lat_acc,
  color = order)) +
  geom_line(size = 2) +
  theme_tidybayes() +
  labs(x = "Trial", y = "Acceleration Latency") +
  scale_color_manual(
    breaks = c("First", "Second"),
    values = c("#001015", "#09A1D7"),
    labels = c("First", "Second")
  )

order_plot_data %>%
ggplot(
  aes(x = overall_trial,
  y = lat_dec,
  color = order)) +
  geom_line(size = 2) +
  theme_tidybayes() +
  labs(x = "Trial", y = "Deceleration Latency") +
  scale_color_manual(
    breaks = c("First", "Second"),
    values = c("#001015", "#09A1D7"),
    labels = c("First", "Second")
  )
```

# Six-trial Models (Bongers 2010)

```{r bongers-replication, include=FALSE}
ppt_peaks_bongers <- ppt_m_std %>%
    dplyr::filter(
        (time == "Post" & 
        trial_num_in_block %in% c(1:3)) 
        | 
        (time == "Pre" & 
        trial_num_in_block %in% c(16:18))
        )

ppt_acceleration_and_latencies_bongers <- ppt_m %>%
  mutate(acc_m_filtfilt_std = standardize(acc_m_filtfilt)) %>%
  dplyr::filter(
      (time == "Post" & 
      trial_num_in_block %in% c(1:6)) 
      | 
      (time == "Pre" & 
      trial_num_in_block %in% c(13:18))
      )

```

As in Bongers, data is filtered such that the analysis only considers the last 6 trials of the first block (Pre) and the first 6 trials of the second block (Post) of manual reaching. 

## Peaks
### Velocity
#### Prior
```{r velocity-peak-prior}
velocity_peak_priors <- brm(
  vel_m_filt_std ~ 1 + time + (1 + time | ppid), 
  data = ppt_peaks_bongers, 
  family = gaussian,
  prior = c(
    set_prior(prior = "normal(-.2, 2)", class = "b", coef = "timePost"),
    set_prior(prior = "normal(0, 2)", class = "Intercept"),
    set_prior(prior = "exponential(1)", class = "sd"), 
    set_prior(prior = "exponential(1)", class = "sigma"),
    set_prior(prior = "lkj(1)", class = "cor", group = "ppid")
  ),
  sample_prior = "only",
  seed = 1337,
  silent = TRUE, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(velocity_peak_priors)
summary(velocity_peak_priors)
```

#### Posterior

```{r velocity-peak-posterior}
velocity_peaks <- update(
  velocity_peak_priors,
  sample_prior = "no",
  refresh = 0,
  seed = 1337,
  file = here::here("scripts", "for_osf", "tooluse_avatar", "models", "supplementary", "peakvelocity_ppt_bongers")
  )

plot(velocity_peaks)
summary(velocity_peaks)

pp_check(velocity_peaks, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Peak Velocity",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Velocity (mm/s)"
  )

velbf <- bayesfactor_pointnull(
  velocity_peaks,
  prior = velocity_peak_priors
  ) %>% as.data.table()

vel_describe <- bayestestR::describe_posterior(
  velocity_peaks,
  centrality = "map",
  ci_method="hdi"
  ) %>% 
  dplyr::filter(Parameter == "b_timePost") %>% 
  mutate("Outcome" = "Peak Velocity")

(
  vel_describe <- bind_cols(
    vel_describe,
    "BF" = exp(
        velbf[Parameter == "b_timePost",
        log_BF]
        )
        )
)
```

### Acceleration
#### Prior
```{r acceleration-peak-prior}
acceleration_peak_priors <- brm(
  acc_m_filtfilt_std ~ 1 + time + (1 + time | ppid), 
  data = ppt_acceleration_and_latencies_bongers, 
  family = gaussian,
  prior = c(
    set_prior(prior = "normal(-.2, 2)", class = "b", coef = "timePost"),
    set_prior(prior = "normal(0, 2)", class = "Intercept"),
    set_prior(prior = "exponential(1)", class = "sd"), 
    set_prior(prior = "exponential(1)", class = "sigma"),
    set_prior(prior = "lkj(1)", class = "cor", group = "ppid")
    ),
  sample_prior = "only",
  seed = 1337,
  silent = TRUE, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(acceleration_peak_priors)
summary(acceleration_peak_priors)
```

#### Posterior

```{r acceleration-peak-posterior}
acceleration_peaks <- update(
  acceleration_peak_priors,
  sample_prior = "no",
  refresh = 0,
  seed = 1337,
  file = here::here("scripts", "for_osf", "tooluse_avatar", "models", "supplementary", "peakacceleration_ppt_bongers")
  )

plot(acceleration_peaks)
summary(acceleration_peaks)

pp_check(acceleration_peaks, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Acceleration Peak",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Acceleration (mm/s^2)"
  )

accbf <- bayesfactor_pointnull(acceleration_peaks) %>% as.data.table()

acc_describe <- bayestestR::describe_posterior(
  acceleration_peaks,
  centrality = "map",
  ci_method="hdi"
  ) %>% dplyr::filter(
    Parameter == "b_timePost"
  ) %>% 
  mutate("Outcome" = "Peak Acceleration")

(
  acc_describe <- bind_cols(
    acc_describe,
    "BF" = exp(
        accbf[Parameter == "b_timePost",
        log_BF]
        )
    )
  )

```

### Deceleration
#### Prior
```{r deceleration-peak-prior}
deceleration_peak_priors <- brm(
  dec_m_filtfilt_std ~ 1 + time + (1 + time | ppid), 
  data = ppt_peaks_bongers, 
  family = gaussian,
  prior = c(
    set_prior(prior = "normal(.2, 2)", class = "b", coef = "timePost"),
    set_prior(prior = "normal(0, 2)", class = "Intercept"),
    set_prior(prior = "exponential(1)", class = "sd"), 
    set_prior(prior = "exponential(1)", class = "sigma"),
    set_prior(prior = "lkj(1)", class = "cor", group = "ppid")
            ),
  sample_prior = "only",
  seed = 1337,
  silent = TRUE, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(deceleration_peak_priors)
summary(deceleration_peak_priors)
```

#### Posterior
```{r deceleration-peak-posterior}

deceleration_peaks <- update(
  deceleration_peak_priors,
  sample_prior = "no",
  seed = 1337,
  refresh = 0,
  file = here::here("scripts", "for_osf", "tooluse_avatar", "models", "supplementary", "peakdeceleration_ppt_bongers")
  )

plot(deceleration_peaks)
summary(deceleration_peaks)

pp_check(deceleration_peaks, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Deceleration Peak",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Deceleration (mm/s^2)"
  )

dec_describe <- bayestestR::describe_posterior(
  deceleration_peaks,
  centrality = "map",
  ci_method="hdi"
  ) %>% dplyr::filter(
    Parameter == "b_timePost"
  ) %>% 
  mutate("Outcome" = "Peak Deceleration")

decbf <- bayesfactor_pointnull(deceleration_peaks) %>% as.data.table()

(
  dec_describe <- bind_cols(
    dec_describe,
    "BF" = exp(
        decbf[Parameter == "b_timePost",
        log_BF]
        )
    )
    )

```

## Peak Latencies
### Preregistration changes
Changes from preregistration:  
- Lognormal distribution over gaussian due to better posterior fit  
- Unstandardized due to lognormal, and negative parameter estimates from standardization  
- Intercepts centered at empirical mean, with an SD equal to empirical SD * 2.5  
- Time effect centered at empirical SD / 5, with spread of empirical SD * 2.5  
- These changes do not change the interpretable results of the models, but do improve the fit of the models  

### Velocity

#### Prior

```{r velocity-latency-prior}

velocity_latency_priors <- brm(
  vel_lat_filt ~ 1 + time + (1 + time | ppid), 
  data = ppt_acceleration_and_latencies_bongers, 
  family = lognormal,
  prior = c(
     prior_string(
       prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(vel_lat_filt)] / 5
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(vel_lat_filt)] * 2.5
         ), 2), ")"
       ),
       class = "b"),
    # Use rstanarm approach to set Intercept prior
    # Use normal with mean of response, and sd of response * 2.5
    prior_string(
      prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_bongers[,mean(vel_lat_filt)]
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(vel_lat_filt)] * 2.5
         ), 2), ")"
       ),
      class = "Intercept"),
    prior(prior = "exponential(1)", class = "sd"),
    prior(prior = "exponential(1)", class = "sigma"),
    prior(prior = "lkj(1)", class = "cor", group = "ppid")
            ),
  sample_prior = "only",
  seed = 1337,
  silent = 2, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(velocity_latency_priors)
summary(velocity_latency_priors)
```

#### Posterior
```{r velocity-latency-posterior}

velocity_latencies <- update(
  velocity_latency_priors,
  sample_prior = "no",
  refresh = 0,
  seed = 1337,
  file = here::here("scripts", "for_osf", "tooluse_avatar", "models", "supplementary", "velocity_latency_ppt_bongers")
  )

plot(velocity_latencies)
summary(velocity_latencies)

pp_check(velocity_latencies, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Velocity Latency",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Time (ms)"
  )

velocity_latencies_describe <- bayestestR::describe_posterior(
  velocity_latencies,
  centrality = "map",
  ci_method="hdi"
  ) %>% 
  dplyr::filter(
  Parameter == "b_timePost"
  ) %>% 
  mutate("Outcome" = "Velocity Latency")

vellatbf <- bayesfactor_pointnull(velocity_latencies) %>% as.data.table()

vel_lat_describe <- bind_cols(
    velocity_latencies_describe,
    "BF" = exp(
        vellatbf[Parameter == "b_timePost",
        log_BF]
        )
    )
```

### Acceleration
#### Prior
```{r acceleration-latency-prior}

# Acceleration Latency -------------

acceleration_latency_priors <- brm(
  acc_lat_filtfilt ~ 1 + time + (1 + time | ppid), 
  data = ppt_acceleration_and_latencies_bongers, 
  family = lognormal(link = "identity"),
  prior = c(
     prior_string(
       prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(acc_lat_filtfilt)] / 5
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(acc_lat_filtfilt)] * 2.5
         ), 2), ")"
       ),
       class = "b"),
    # Use rstanarm approach to set Intercept prior
    # Use normal with mean of response, and sd of response * 2.5
    prior_string(
      prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_bongers[,mean(acc_lat_filtfilt)]
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(acc_lat_filtfilt)] * 2.5
         ), 2), ")"
       ),
      class = "Intercept"),
    prior(prior = "exponential(1)", class = "sd"),
    prior(prior = "exponential(1)", class = "sigma"),
    prior(prior = "lkj(1)", class = "cor", group = "ppid")
            ),
  sample_prior = "only",
  seed = 1337,
  silent = 2, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(acceleration_latency_priors) 

```

#### Posterior
```{r acceleration-latency-posterior}

acceleration_latencies <- update(
  acceleration_latency_priors,
  sample_prior = "no",
  refresh = 0,
  seed = 1337,
  file = here::here("scripts", "for_osf", "tooluse_avatar", "models", "supplementary", "acceleration_latency_ppt_bongers")
  )

plot(acceleration_latencies)
summary(acceleration_latencies)

pp_check(acceleration_latencies, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Acceleration Latency",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Time (ms)"
  )

acc_lat_describe <- bayestestR::describe_posterior(
  acceleration_latencies, centrality = "map",
  ci_method="hdi"
  ) %>% 
  dplyr::filter(
    Parameter == "b_timePost"
  ) %>% 
  mutate("Outcome" = "Acceleration Latency")

acclatbf <- bayesfactor_pointnull(acceleration_latencies) %>% as.data.table()

(
  acc_lat_describe <- bind_cols(
    acc_lat_describe,
    "BF" = exp(
        acclatbf[
          Parameter == "b_timePost",
          log_BF
          ]
        )
    )
    )
```

### Deceleration
#### Prior
```{r deceleration-latency-prior}

deceleration_latency_priors <- brm(dec_lat_filtfilt ~ 1 + time + (1 + time | ppid), 
  data = ppt_acceleration_and_latencies_bongers, 
  family = lognormal(link = "identity"),
  prior = c(
     prior_string(
       prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(dec_lat_filtfilt)] / 5
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(dec_lat_filtfilt)] * 2.5
         ), 2), ")"
       ),
       class = "b"),
    # Use rstanarm approach to set Intercept prior
    # Use normal with mean of response, and sd of response * 2.5
    prior_string(
      prior = paste0("normal(",
         round(log(
          ppt_acceleration_and_latencies_bongers[,mean(dec_lat_filtfilt)]
         ), 2), ",",
         round(log(
          ppt_acceleration_and_latencies_bongers[,sd(dec_lat_filtfilt)] * 2.5
         ), 2), ")"
       ),
      class = "Intercept"),
    prior(prior = "exponential(1)", class = "sd"),
    prior(prior = "exponential(1)", class = "sigma"),
    prior(prior = "lkj(1)", class = "cor", group = "ppid")
            ),
  sample_prior = "only",
  seed = 1337,
  silent = 2, refresh = 0,
  save_pars = save_pars(all = TRUE),
  warmup = b, iter = i, chains = ch, cores = co,
  control = control_list
  )

plot(deceleration_latency_priors)
summary(deceleration_latency_priors)
```

#### Posterior

```{r deceleration-latency-posterior}

deceleration_latencies <- update(
  deceleration_latency_priors,
  sample_prior = "no",
  seed = 1337,
  refresh = 0,
  file = here::here("scripts", "for_osf", "tooluse_avatar", "models", "supplementary", "deceleration_latency_ppt_bongers")
  )

plot(deceleration_latencies)
summary(deceleration_latencies)

pp_check(deceleration_latencies, ndraws = 50) +
  theme_tidybayes() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    title = "Deceleration Latency",
    subtitle = "Posterior Draws vs. Empirical Distribution",
    x = "Time (ms)"
  )

deceleration_latencies_describe <- bayestestR::describe_posterior(
  deceleration_latencies,
  centrality = "map",
  ci_method="hdi"
  ) %>% 
  dplyr::filter(
    Parameter == "b_timePost"
    ) %>% 
  mutate("Outcome" = "Deceleration Latency")

declatbf <- bayesfactor_pointnull(deceleration_latencies) %>% as.data.table()

(
  dec_lat_describe <- bind_cols(
    deceleration_latencies_describe,
    "BF" = exp(
        declatbf[Parameter == "b_timePost",
        log_BF]
        )
    )
    )
```

# Summary Table

```{r table_one, results='asis'}
#| tbl-cap: Bongers Model Summary Table
model_params <- bind_rows(
  vel_describe,
  acc_describe,
  dec_describe,
  vel_lat_describe,
  acc_lat_describe,
  dec_lat_describe
) %>% select(
  Outcome,
  BF,
  MAP,
  CI_low,
  CI_high
) %>% rename("Lower" = CI_low,
             "Upper" = CI_high,
             "Mode" = MAP)

fwrite(model_params, here::here("scripts", "for_osf", "tooluse_in_vr", "tables", "supplementary", "model_params_bongers.csv"))

model_table <- flextable::qflextable(model_params) %>%
  add_header_row(T, 
                 c(" ", "95% Highest Density Interval"), 
                 colwidths = c(3, 2)) %>% 
  add_header_lines("Table 1. Parameters of Kinematic Models") %>%
  border_outer(border = officer::fp_border(style = "none", 
                                           width = 0), 
               part = "header") %>%
  hline(i = 1, 
        border = officer::fp_border(style = "solid", 
                                    width = 1.5), 
        part = "header") %>%
  hline(i = 2, j= c(1:3), 
        border = officer::fp_border(style = "none", 
                                    width = 0), 
        part = "header") %>%
  hline(i = 2, j= c(4, 5), 
        border = officer::fp_border(style = "solid", 
                                    width = 1), 
        part = "header") %>%
  hline(i = 3, 
        border = officer::fp_border(style = "solid", 
                                    width = 1), 
        part = "header") %>%
  hline(i = 6, 
        border = officer::fp_border(style = "solid", 
                                    width = 1.5), 
        part = "body") %>%
  flextable::footnote(i = 3, j=c(1:2),
           value = as_paragraph(
             c(
               "Parameters given as standardized values, and represent the effect of time (tool-use).", 
               "Bayes Factors represent multiplicative evidence in favor of effect (Savage-Dickey Ratios).")
             ), 
           ref_symbols = c("a", "b"),
           part = "header"
          ) %>%
  font(fontname = "Times New Roman",
       part = "all") %>%
  fontsize(size = 9, part = "footer") %>%
  flextable::colformat_double(i=c(1:6), j = 3:5, digits = 3) %>%
  flextable::colformat_double(i=c(1:6), j = 2, digits = 2)
  

model_table

saveRDS(model_table, here::here("scripts", "for_osf", "tooluse_in_vr", "tables", "supplementary", "kinematic_table_bongers.rds"))

```

### Is the effect influenced by a performance hypothesis?

```{r}

participant_info_and_kinematics %>%
    group_by(time, performance_hypothesis, fatigue_yn) %>%
    dplyr::summarise(
        m_vel = mean(vel_m_filt),
        m_acc = mean(acc_m_filtfilt),
        m_dec = mean(dec_m_filtfilt), n = n() / 18
    )
```

```{r}
# Use ggplot to plot a point and line plot of the mean peak velocity on the y axis 
# across each trial on the x axis, grouping by performance hypothesis and using the 
# color aesthetic to differentiate the two groups


performance <- geom_line(
    data = . %>% group_by(
      overall_trial, 
      time, 
      performance_hypothesis
      ) 
      %>% summarise(
        m_vel = mean(vel_m_filt)
      ),
    aes(
      x = overall_trial,
      y = m_vel,
      group = performance_hypothesis, 
      color = performance_hypothesis,
      ), 
    linewidth = 2
)

fatigue <- geom_line(
    data = . %>% group_by(
        overall_trial,
        time,
        fatigue_yn
    )
    %>% summarise(
            m_vel = mean(vel_m_filt)
        ) %>% dplyr::filter(fatigue_yn),
    aes(
        x = overall_trial,
        y = m_vel,
        group = fatigue_yn,
        color = "firebrick",
    ),
    linewidth = 2
)

avatar_embodiment <- geom_line(
    data = . %>% group_by(
        overall_trial,
        time,
        avatar_embodiment_hypothesis
    )
    %>% summarise(
            m_vel = mean(vel_m_filt)
        ) %>% dplyr::filter(avatar_embodiment_hypothesis),
    aes(
        x = overall_trial,
        y = m_vel,
        group = avatar_embodiment_hypothesis,
        color = "darkorange",
    ),
    linewidth = 2
)

tool_embodiment <- geom_line(
    data = . %>% group_by(
        overall_trial,
        time,
        tool_embodiment_hypothesis
    )
    %>% summarise(
            m_vel = mean(vel_m_filt)
        ) %>% dplyr::filter(tool_embodiment_hypothesis),
    aes(
        x = overall_trial,
        y = m_vel,
        group = tool_embodiment_hypothesis,
        color = "darkgreen",
    ),
    linewidth = 2
)

performance_hypothesis_plot <- participant_info_and_kinematics %>%
  ggplot() +
  performance +
    labs(
      title = "Peak Velocity By Trial",
      subtitle = "Avatar VR",
      x = "Trial",
      y = "Peak Velocity (mm/s)",
      color = "Hypothesis"
      ) +
    theme_tidybayes() +
    scale_color_manual(
      values = c(
        "steelblue",
        "firebrick",
        "darkorange",
        "darkgreen"
      ),
      labels = c(
        "Performance Hypothesis",
        "Fatigue",
        "Avatar Embodiment",
        "Tool Embodiment"
      )
    ) +
    theme(text = element_text(size = 34))
```

```{r}
performance_hypothesis_plot 
```


### Is the effect influenced by fatigue?

```{r}
# Use ggplot to plot a point and line plot of the mean peak velocity on the y axis 
# across each trial on the x axis, grouping by fatigue and using the 
# color aesthetic to differentiate the two groups
participant_info_and_kinematics %>%
  group_by(overall_trial, time, fatigue_yn) %>%
  dplyr::summarise(m_vel = mean(vel_m_filt),
            m_acc = mean(acc_m_filtfilt),
            m_dec = mean(dec_m_filtfilt)) %>%
  ggplot(aes(x = overall_trial,
  y = m_vel, 
  group = interaction(
    time,
    fatigue_yn
    ), 
    color = fatigue_yn
    )
    ) +
    geom_line(size = 2) +
    labs(
      title = "Peak Velocity By Trial",
      subtitle = "Studies 1 & 2",
      x = "Trial",
      y = "Peak Velocity (mm/s)",
      color = "Fatigue"
      ) +
    theme_tidybayes()+
    scale_color_manual(
    breaks = c(FALSE, TRUE),
    values = c("#001015", "#09A1D7"),
    labels = c("No", "Yes")
    ) +
    theme(text = element_text(size = 34))
```

```{r}
# Recreates the previous plot twice, once for each order in the post-test (one for "First" and one for "Second")
# Then combine the two plots into one using the patchwork package
(
  participant_info_and_kinematics %>%
  dplyr::filter(order == "first" | order == "pre") %>%
  group_by(overall_trial, time, fatigue_yn) %>%
  dplyr::summarise(m_vel = mean(vel_m_filt),
            m_acc = mean(acc_m_filtfilt),
            m_dec = mean(dec_m_filtfilt)) %>%
  ggplot(aes(x = overall_trial,
  y = m_vel, 
  group = interaction(
    time,
    fatigue_yn
    ), 
    color = fatigue_yn
    )
    ) +
    geom_line(size = 2) +
    labs(
      title = "Reaching First",
      x = "Trial",
      y = "Peak Velocity (mm/s)",
      color = "Fatigue"
      ) +
    theme_tidybayes()+
    scale_color_manual(
    breaks = c(FALSE, TRUE),
    values = c("#001015", "#09A1D7"),
    labels = c("No", "Yes")
    ) +
    theme(text = element_text(size = 34))
) / (
  participant_info_and_kinematics %>%
  dplyr::filter(order == "second" | order == "pre") %>%
  group_by(overall_trial, time, fatigue_yn) %>%
  dplyr::summarise(m_vel = mean(vel_m_filt),
            m_acc = mean(acc_m_filtfilt),
            m_dec = mean(dec_m_filtfilt)) %>%
  ggplot(aes(x = overall_trial,
  y = m_vel, 
  group = interaction(
    time,
    fatigue_yn
    ), 
    color = fatigue_yn
    )
    ) +
    geom_line(size = 2) +
    labs(
      title = "Reaching Second",
      x = "Trial",
      y = "Peak Velocity (mm/s)",
      color = "Fatigue"
      ) +
    theme_tidybayes()+
    scale_color_manual(
    breaks = c(FALSE, TRUE),
    values = c("#001015", "#09A1D7"),
    labels = c("No", "Yes")
    ) +
    theme(text = element_text(size = 34))
) +
    patchwork::plot_annotation(
      title = "Peak Velocity By Trial",
      subtitle = "Studies 1 & 2",
      caption = "Figure 1: Peak velocity by trial for each order in the post-test. The line plot shows the mean peak velocity for each trial, with the color representing fatigue_yn and the line representing the order in the post-test. The first order in the post-test is the first time the participant used the tool in the virtual reality environment. The second order in the post-test is the second time the participant used the tool in the virtual reality environment.",
      theme = theme_tidybayes()
    )
```

```{r}
participant_info_and_kinematics %>%
  dplyr::filter(trial_num_in_block < 6) %>%
  ggplot(
    aes(
      x = fatigue_post_tool,
      y = vel_m_filt
    )
  ) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "Peak Velocity By Fatigue",
    subtitle = "Studies 1 & 2",
    x = "Fatigue",
    y = "Peak Velocity (mm/s)"
  ) +
  theme_tidybayes() +
  theme(text = element_text(size = 34))

participant_info_and_kinematics_wide <- participant_info_and_kinematics %>%
    tidyr::pivot_wider(
        id_cols = c(ppid, trial_num_in_block, fatigue_post_tool, fatigue_yn),
        names_from = time,
        values_from = c(
            vel_m_filt,
            acc_m_filtfilt,
            dec_m_filtfilt,
            vel_lat_filt,
            acc_lat_filtfilt,
            dec_lat_filtfilt
        ),
        values_fn = list(
            vel_m_filt = mean,
            acc_m_filtfilt = mean,
            dec_m_filtfilt = mean,
            vel_lat_filt = mean,
            acc_lat_filtfilt = mean,
            dec_lat_filtfilt = mean
        )
    ) 
    
change_by_fatigue <- participant_info_and_kinematics_wide %>%
    dplyr::group_by(ppid, fatigue_post_tool, fatigue_yn) %>%
    dplyr::summarise(
        vel_change = round(
            mean(vel_m_filt_Post) - mean(vel_m_filt_Pre),
            2
        ),
        acc_change = round(
            mean(acc_m_filtfilt_Post) - mean(acc_m_filtfilt_Pre),
            2
        ),
        dec_change = round(
            mean(dec_m_filtfilt_Post) - mean(dec_m_filtfilt_Pre),
            2
        ),
        vel_lat_change = round(
            mean(vel_lat_filt_Post) - mean(vel_lat_filt_Pre),
            2
        ),
        acc_lat_change = round(
            mean(acc_lat_filtfilt_Post) - mean(acc_lat_filtfilt_Pre),
            2
        ),
        dec_lat_change = round(
            mean(dec_lat_filtfilt_Post) - mean(dec_lat_filtfilt_Pre),
            2
        )
    ) %>%
    as.data.table()

change_by_fatigue %>%
ggplot(
    aes(
        y = vel_change,
        x = fatigue_yn
    )
) +
    stat_dots()
    labs(
        title = "Peak Velocity By Fatigue",
        subtitle = "Studies 1 & 2",
        x = "Fatigue",
        y = "Peak Velocity (mm/s)"
    ) +
    theme_tidybayes() +
    theme(text = element_text(size = 34))
```

```{r}
 participant_info_and_kinematics %>%
  dplyr::filter(overall_trial %in% c(1:36)) %>%
  group_by(time, order, fatigue_yn) %>%
  dplyr::summarise(
    m_vel = mean(vel_m_filt),
    m_acc = mean(acc_m_filtfilt),
    m_dec = mean(dec_m_filtfilt)
    )
```

```{r}
sessioninfo::package_info()
```